\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2013, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, notebook.
Access to any machine inside the ECS 405 lab.
No other electric devices or network links allowed.
All questions 4 points.

\ques
% Project 13
Your wish to begin using NIS for groups, password and shadow on your machine.
Your NIS server is {\ltt{}cougar}, your NIS domain name is {\ltt{}nis3}.
What files do you need to change and what changes do you need to make?
\vskip 1.8in
\ques

ypserver cougar
/bin/domainname nis3
In nsswitch.conf:
passwd: compat
group: compat 
shadow: compat

% Project 25
A user has a hard quota of 1M.
What happens if the user tries to store a 10M file?
\vskip 0.8in
\ques

writing file: disk quota exceeded
failed to extend file: disk quota exceeded

% Project 14
You wish to mount the files from the
{\ltt{}/usr/share} directory on {\ltt{}panter.net.cecs.csulb.edu}
to your file tree as {\ltt{}/auto} (assume panther makes the directory available) read write,
using the automounter.
Give the files and contents you needed to do this.
\vskip 1.8in
\ques

File:
/etc/fstab
Contents:
panther.net.cecs.csulb.edu:/usr/share /auto nfs
bg,soft 0 0
Command:
mount /auto

% Project 21
{\ltt{}sue} wants to make items in her directory
{\ltt{}public_html/friends} available to friends to whom she gives a password.
Give the file name, file location and file contents to do this.
(Just the main file, don't show how to set up the passwords and password file.)
\vskip 2.2in
\vfill\eject
\ques

In public_html/friends:
Create .htaccess file:
AuthName "MyCluster"
AuthType Basic
AuthUserFile /home/sue/public_html/friends/pwd
require valid-user

% Project 16
What two kernels, and one tester, are available to install.
\vskip 0.8in
\ques



% Project 17
In the installation process, describe what a target is.
\vskip 1.0in
\ques

The target fs to install the kernel onto

% Project 18
You wish to log information
from an application
using the {\ltt{}local3} facility and
send that information to log files on panther.
Give the name of the file you need to modify and the line you need to
add to that file.
\vskip 1.0in
\ques

In /etc/syslog.conf:
local3.*   @panther

% Project 18
You want the default (and only) printer for your machine to be the printer
called {\ltt{}hp2300} that is attached to the machine {\ltt{}cougar}.
What file should you modify?
What line do you need in that file?
\vskip 1.0in
\ques

In /etc/printcap:
hp2300|lp:lp=:rm=cougar.cecs.csulb.edu:rp=cougar.net.cecs.csulb.edu:sd=/var/spool/hp2300:

% Project 20
You want to abort any login process where the user
gets the password wrong 4 times.
What file do you need to change?
\vskip 0.6in
\ques

In /etc/login.defs:
LOGIN_RETRIES   4

% Project 19
You want to put all mail with the word {\ltt{}Homework} in its body
into a file called {\ltt{}/home/bob/homework}.
What file do you need to create, in what directory is that file created
and what does that file need to contain?
\vskip 1.6in
\vfill\eject
\ques

File:
.procmailrc (User's home dir)
Lines:
:0:
* ^Body.*Homework
/home/bob/homework

% Project 15
How do you determine what libraries a dynamically linked executable
requires?
\vskip 0.6in
\ques

ldd {{executable file}}

% Project 22
There are two machines for which {\ltt{}n.edu} ({\ltt{}129.1.1.1})
supplies name service:
{\ltt{}o.cs.edu} ({\ltt{}134.139.245.1}) and 
{\ltt{}t.cs.edu} ({\ltt{}134.139.245.2}).
Give the entire forward zone file for {\ltt{}cs.edu}.
\vskip 4.2in
\ques

$TTL 86400
@  IN  SOA  n.edu. root.n.edu. (
                        2011032500 ; Serial
                        28800      ; Refresh
                        14400      ; Retry
                        3600000    ; Expire
                        86400 )    ; Minimum
     IN   NS  cs.edu
  IN   A    129.1.1.1
o IN A 134.139.245.1
t IN A 134.139.245.2
    
% Project 22
Give the {\ltt{}named.conf} entry on {\ltt{}n.edu} for the {\ltt{}cs.edu} zone.
(Do not give the whole file, just the one zone entry.)
\vskip 1.2in
\vfill
\eject
\ques

zone "cs.edu" IN {
     type master;
     file "named.host";
};

% Project 19
What is the difference between a ``mail hub" and a ``smart host"?
\vskip 1.2in
\ques

mail hub:
All mail destined for local machine goes to this machine instead
smart host:
All non-local mail sent here and relayed to destination machine
(use if behind a firewall)

% Project 21
You want no CGIs allowed to {\ltt{}/var/www/thru},
but you do want CGI allowed inside {\ltt{}/var/www/thru/cgi}.
Give the {\ltt{}httpd.conf} entries to do this.
\vskip 1.8in
\ques
% Project 23
Give the steps you would take on {\ltt{}lynx} to install and use
a new {\ltt{}/etc/printcap} file on {\ltt{}lab99}.
You will perform the install from a file called {\ltt{}newprintcap}
located on {\ltt{}lynx}.
To activate the new printcap you will need to issue the command
{\ltt{}lpc restart} on {\ltt{}lab99}.
Include file names, contents and command.
\vskip 2.0in
\ques

In lab99 home, .rhosts:
lynx.net.cecs.csulb.edu csa476t1
Create dist file in lynx:
~/newprintcap -> csa476t1@lab99.net.cecs.csulb.edu
       install /etc/printcap ;
       special "lpc restart" ;
rdist -f distfile

% Project 24
You want to make a directory called {\ltt{}/usr/share} on your
Linux machine available to all machines running Microsoft Windows as
{\ltt{}myshare}.
What file do you need to change?
What lines do you need to add to that file?
\vskip 1.2in
\vfill\eject
\ques

In smb.conf:
[myshare]
  path = /usr/share
  public = yes
  writable = yes
  printable = yes

% Project 15
You want to prohibit the user {\ltt{}sue} from using ftp.
Give the file name and modification to do this.
\vskip 1.0in
\ques

In /etc/ftpusers:
bob

% Project 20
{\ltt{}bob} wants all students to deposit homework in one of his
directories.
Describe how you would set up a {\it program} to allow students to do this.
\vskip 1.3in
\ques

/#!/bash
iptables -A INPUT -p tcp --dport ssh \
       -s 134.139.0.0/16 -j ACCEPT

% Project 14
You want to make your directory
{\ltt{}/load}
available to all unix machines on your subnet (read write).
Give the name of the file you need to modify, the line you need to
add to that file and the command you need to run to activate this.
\vskip 1.0in
\ques

In /etc/exports:
/load(rw)
ls /load will load the directory

% Project 26
When the machine {\ltt{}01:02:03:04:05:06} boots from the network
it is to be assigned the name {\ltt{}lab13} and the IP address
{\ltt{}134.139.248.13} and boot {\ltt{}/tftpboot/pxelinux.0}.
What entries must be in what file on the dhcpd server
for this to happen?
\vskip 2.0in
\vfill\eject

In dhcpd.conf:
filename "/tftpboot/pxelinux.0";
host lab13 {
  hardware ethernet 01:02:03:04:05:06 ;
  fixed-address 134.139.248.13
}

Analysis section. Assume these happen on the machine you administer.
For each of the questions on this page
state what things would you check on the machine you administer
and for each thing you would check give the command you would use to
perform the check. (If you wish to examine the file you may give the
command as {\ltt{}vi}).

\ques
Your {\ltt{}csa476} account receives the message ``no home directory"
when you log in.
\vfill
\ques

The user home was not specified, or not created when adding the user

A web page on your machine gives the message ``internal server
error" back to a browser.
\vfill
\ques

The machine's resolv.conf was not correctly configured,
or the user page has bad permissions on a file,
or htaccess has a syntax error

After a new install (assignment 17):
You can ssh to the machine next to you, but you can't
ssh to panther.
\vfill
\ques

sshd is not running on panther,
your iptables are not set up correctly to interact with panther

You can ftp into your machine using {\ltt{}bob}, but not
using using your {\ltt{}csa476} account.
\bye

Your home account is in /etc/ftpusers
