\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Homework 22 \hfill Fall 2003}}
\footline{Dennis Volper \hfill 19 November 2003 (Week 12 Lecture 2)\hfill 
Due: 24 November 2003 (Week 13, Lab 1)}
\parindent 0pt

This project is about httpd.

If you did not load the http package when you loaded the system you can
extract it separately from
{\ltt{}jaguar:/hdb/disk1/slackware/n/apache.tgz}.
Either use the package tool on the n directory or 
use tar to decompress and extract the stuff.

The web server should be fully configured.
This project is about modifying Web access (security) to
directories.

You can enable the webserver by 
{\ltt{}chmod a+x /etc/rc.d/rc.httpd}
but I would recommand you start it by hand using
the command found in that file.

Setup home pages for both bob and ftp.
A simple home page is available in {\ltt{}~djv/index.html}.
In bob's version of the home page change ``CECS 476" to bob.
In ftp's version of the home page change ``CECS 476" to ftp.
This allows you to distinguish them.
Make sure you can assess the home pages for both ftp and bob.

Now that you have http working,
configure your http security as follows:
\hfill\break
1) The machine home page {\ltt{}http:labxx.net.cecs.csulb.edu}
should be available
\hfill\break
2) The home page for bob {\ltt{}http:labxx.net.cecs.csulb.edu/~bob}
should be available
\hfill\break
3) The home page for ftp {\ltt{}http:labxx.net.cecs.csulb.edu/~ftp}
should NOT be available

That is, even though ftp has a legal home page, you are declaring
through the http security mechanisms that no one is allowed to
access that home page.

To test you will need to start Netscape on some machine. 
If you want, you may configure X on your machine for this project or use 
another machine in the lab whose administrator has X configured.

Note: do the security with the http mechanisms, do NOT do
this by using
{\ltt{}chmod} on the ftp files or directories to make them unreadable.

Submit: 
You had to change several things in the configuration files;
report each of the changes you made.
(Don't report the whole file, only the changes.)

\bye
