\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Homework 2 \hfill Fall 2003}}
\footline{Dennis Volper \hfill 8 September 2003 (Week 2 Lecture 1)\hfill 
Due: 10 September 2003 (Week2 Lab 2)}
\parindent 0pt

Purpose: This assignment is to familiarize you with users and logins.

Submission: You will submit a written document.

Part I) {\it examination of information}

Examine the password and group files on {\ltt{}cheetah}
and answer the following questions:

For the instructors account ({\ltt{}volper}) answer the following
questions:

1) What is the UID (user) number?

2) What is the GID (group) number?

3) What is the home directory?

4) What is the login shell?

5) What is the name of the base group the instructor belongs to?

6) The user {\ltt{}djv} belongs to two additional groups,
what are the names of this group?

7) What is the group numbers for the groups named guest,
cecsu and cecsg?

Examine the shadow file on the {\ltt{}lab66} machine
and answer the following questions:

8) List the local accounts that have (encripted) passwords.
Hint: there are a very small number of such accounts.

9) When (approximately) was the password on the root account changed?

Hint, use bc to help compute the year it was changed (assume
365 days per year), and roughly estimate the month 
(assume 30 days per month).

Examine your {\ltt{}.cshrc} and answer the following questions:

10) How many aliases are setup?

11) How many directories in your path?

\bye
