\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Homework 19 \hfill Fall 2003}}
\footline{Dennis Volper \hfill  10 November 2003 (Week 11 Lecture 1)\hfill 
Due: 12 November 2003 (Week 11, Lab 2)}
\parindent 0pt

This project is about configuring mail.

1) Send mail from your lab machine to your csv account on {\ltt{}cheetah}
using the verbose options ({\ltt{}-v}.
You will notice the conversation between the two machines.

2) On your lab machine send mail from your csv account to bob (on the
local machine) using the verbose option.

You will notice a difference between the lines reported
when the mail goes to another machine and when it is local.

Report: what lines indicate a mail connection to a remote machine
is being made?

3) Suppose you wanted all mail from your lab machine, 
except mail from {\ltt{}root} and {\ltt{}bob}, to be delivered to
{\ltt{}cheetah}.
What changes would you make to {\ltt{}sendmail.cf} to accomplish this?
Make the change, then send mail from {\ltt{}bob} to your account
using the verbose option to make sure that it goes to {\ltt{}cheetah}.
The conversation should be similar to that in (1).
Also send mail from your account on your machine to {\ltt{}bob}
using the verbose option to make sure that it {\it does not} go
to {\ltt{}cheetah}.
The conversation should be similar to that in (2).

Report: the changes you made to {\ltt{}sendmail.cf}

3) Suppose you wish mail coming from your machine to appear as though it
came from cheetah.
You can do this by making a change to the {\ltt{}DM} macro.
Make (and test) this change.

Report: what change did you make.

Somewhere the change you made for (3) causes a change to be made in the return address.
Search the {\ltt{}sendmail.cf} and determine where the return
address is modified.

Report: The ruleset that the rewrite of the address is in (S what).
The rule in that ruleset causes the rewrite (report the entire line).

Cleanup: restore {\ltt{}sendmail.cf} to its original contents.
\bye
