\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Assignment 19 \hfill Spring 2013}}
\footline{Dennis Volper \hfill 28 March 2013 (Week 10 Lecture 2)\hfill 
Due: 9 April 2013 (Week 11, Lab 1)}
\parindent 0pt

This project is about configuring mail.

1) As {\ltt{}bob} modify your incoming mail handling as follows:

a) If the Subject line contains the word ``Late",
place the mail in a file called {\ltt{}latestuff}.

b) If it is from {\ltt{}csa476xx} (use your account here)
place the mail in a file called {\ltt{}importantstuff}

c) If the body of the mail contains the word {\ltt{}Bargin}
place the mail in a file called {\ltt{}junkmail}

If an incoming mail matches multiple actions, the first actions
specified should be taken.
Use lockfiles in all cases.

Report: the contents of bob's {\ltt{}.procmailrc}

For the next question, examine the {\ltt{}sendmail.cf}
file on your machine.
(If you have changed yours, you may examine the one on {\ltt{}panther}.)

2) Report the number of the ruleset that converts header
names to masqueraded form.

For the next question use the manual and possibly some additional commands.

3) Report the name and full path name of the pop3 server.

Make a copy of the standard slackware mc macros.
({\ltt{}/usr/share/sendmail/cf/cf})
Modify the copy of the macros so {\ltt{}jaguar} is setup as
being the ``smart host" for your machine.
Modify the copy of the macros so {\ltt{}jaguar} is setup as
being the ``mail hub" for your machine.
Build the macros into a cf ({\ltt{}Build}), install the cf
as the new mail configuration, restart sendmail.

Modify the new sendmail configuration so that 
mail for {\ltt{}bob} and {\ltt{}root} is to be delivered locally and
not to the mail hub.

Test the mail hub change by (from root) sending mail to your csa account
(should be reabable on jaguar) and to bob (should be readable on your
machine) with no {\ltt{}@} signs.

Test the smart host change by (from root) sending mail to your csa account
{\ltt{}@panther} (should be readable on panther and the log on your machine
should say ``{\ltt{}relay = jaguar.net.cecs.csulb.edu}").

4) Report the changes you made to the macros.

5) Report: the change you made to the {\ltt{}cf} (the special
case stuff for {\ltt{}bob} and {\ltt{}root}).

\bye
