\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Fall 2005, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook. No digital or communitcations devices.
All questions 4 points.

\ques
% Project 14
You want to export the
{\ltt{}/home} directory on your machine to all machines in the lab.
Give the {\ltt{}exportfs} entry to do this.
\vskip 0.8in
\ques
% Project 14
Give the {\ltt{}fstab} entry that would mount
the {\ltt{}/usr/local} directory from {\ltt{}panther.net.cecs.csulb.edu}
on the {\ltt{}/usr/local} directory of your machine.
\vskip 0.7in
\ques
% Project 20
Describe how a SUID program works.
\vskip 2.4in
\ques
% Project 15
Give the {\ltt{}printcap} entry (on {\ltt{}lab99})
for a printer called {\ltt{}laser3}
on {\ltt{}panther}, this printer will use {\ltt{}/var/spool/laser3}
as it's local spool directory.
\vskip 0.8in
\ques
% Project 17
After {\it installing} the system, describe the steps you had to take
to enable NIS.
\vskip 2.4in
\vfill\eject
\ques
% Project 13
You want to add the users in from the NIS server {\ltt{}panther}
to those found in your local groups file.
What files do you need to change and what changes do you need to make?
\vskip 1.7in
\ques
% Project 24
You wish to install the executable file {\ltt{}clogit}
from the {\ltt{}csa476z5} account on {\ltt{}cheetah} as
{\ltt{}/home/bob/sid} on {\ltt{}lab99}.
You wish the file to be owned by {\ltt{}bob} and it should be a SUID
executable. You can use the {\ltt{}bob} account on {\ltt{}lab99}
to do the install.
Give the {\ltt{}distfile}.
\vskip 1.4in
\ques
% Project 19
In {\ltt{}sendmail.cf}:
Define a group {\ltt{}Q} to contain {\ltt{}bob} and {\ltt{}sue}
and a macro {\ltt{}R} to be {\ltt{}panther}.
If you were looking for where the class Q is {\it used} what would you look for?
\vskip 1.6in
\ques
% Project 25
Give the {\ltt{}smb.conf} entries necessary to make
{\ltt{}/home/share} available as a public share to
machines running Windows.
\vskip 1.5in
\vfill\eject
\ques
% Project 19
SWITCHME?
You want mail going to {\ltt{}webmaster} to be delivered locally
and not to the smart host.
What file would you need to change and what change would you need to make.
\vskip 1.0in
\ques
% Project 18
How would you want to find out what libraries are used by
{\ltt{}/usr/sbin/httpd}. Give the exact command to do this.
\vskip 0.7in
\ques
% Project 21
You wish users from {\ltt{}panther} to be able to read and
post news on your machine.
What file will need to be modified
and what modification would be made to that file?
\vskip 2.4in
\ques
% Project 21
You wish your news server to send news to the
{\ltt{}panther} news server.
What files need to be modified and what modifications are done to those files?
\vskip 2.2in
\vfill\eject
\ques
% Project 17
During the configure step of installing the system, name two things you
configured.
\vskip 0.7in
\ques
% Project 18
You want to disallow {\ltt{}bob} from using ftp and
allow NIS accounts to use ftp.
What files do you need to modify and what modifications do you need to make?
\vskip 1.4in
\ques
% Project 23
You have two machines for which you supply name service.
{\ltt{}x.csuf.edu} ({\ltt{}140.111.1.1}) and 
{\ltt{}y.csuf.edu} ({\ltt{}140.111.1.2}).
Give the entire forward zone file for the zone {\ltt{}csuf.edu},
including the SOA, if the DNS server for that zone
is {\ltt{}lab99.csuf.edu} ({\ltt{}140.111.2.3}).
\vskip 4.2in
\ques
% Project 23
Give the zone entry in {\ltt{}named.conf}
for {\ltt{}140.111.1} (reverse lookup) assuming
the name of the file is {\ltt{}named.rev}.
\vfill\eject
\ques
% Project 15
Send all log messages from the 
facility {\ltt{}lpd} that are at level {\ltt{}debug} or higher
to a file called {\ltt{}/var/log/lpd}.
Give the file name and the line you need in that file.
\vskip 0.8in
\ques
% Project 16
What is a boot set?
Name one boot set.
\vskip 1.2in
\ques
% Project 22
Describe the steps you need to take to require passwords to access
a web directory from a browser.
\vskip 1.9in
\ques
% Project 22
Give, in the correct order, the {\ltt{}http.conf} directives that would
disallow web access to all of {\ltt{}/www}, allow access to {\ltt{}/www/public},
and allow {\ltt{}.htaccess} files to operate in {\ltt{}/www/public}.
\vskip 2.3in
\vfill\eject
Analysis section. Assume {\ltt{}lab88} is a machine you administer.
For each of the questions on this page
state what things would you check on {\ltt{}lab88}
and for each thing you would check state how you would perform the check.

\ques
User {\ltt{}csa476z7} receives the message ``no home directory"
when he logs in.
\vfill
\ques
User {\ltt{}bob} tries {\ltt{}telnet cheetah} and receives the
message ``no path to host".
\vfill
\ques
The public html directory ({\ltt{}httpd} is running on {\ltt{}lab88}) for
{\ltt{}bob} can't be seen, the public html directory for {\ltt{}csa476z7}
can be seen.
\vfill
\ques
User {\ltt{}bob} can log in, user {\ltt{}csa476z7} can't.
\bye
