\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Fall 2005, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open book, open notebook. (All question 8 points, 96 total points possible)
\hfill\break
\ques
% Homework 10
Give the exact command to make a compressed backup of {\ltt{}bob}'s home
directory (preserving permissions) to the file {\ltt{}/tmp/bob.tgz}.
\vskip 0.4in
How would you make control-I be the command that a quit signal ({\ltt{}quit})
to a running program?
\vskip 0.4in
\ques
% Homework 5
Give the command to build an Linux ext2 file system on {\ltt{}/dev/hdb2}.
\vskip 0.5in
Give the name of the file and the exact line that needs to be in that file to
have the file system on {\ltt{}/dev/hdb2} attached to the directory trees
as {\ltt{}/homes} automatically at boot time.
\vskip 0.5in
What does the {\ltt{}fsck} command do?
\vskip 0.4in
\ques
% Homework 9
Give the steps to build a kernel.
\vskip 2.0in
You wish to boot Linux from {\ltt{}/dev/hdc1} with no prompt or wait.
The kernel is called {\ltt{}bzImage} and has already been placed into
{\ltt{}/boot}.
Give the exact contents of your {\ltt{}lilo.conf}.
\vskip 1.8in
\vfill\eject
\ques
% Homework 3
The user {\ltt{}sam} has  a home directory of {\ltt{}/home/sam},
a shell of {\ltt{}/bin/tcsh}, a user number of {\ltt{}12123}
and a base group of {\ltt{}113}
Give the {\ltt{}/etc/passwd} entry for {\ltt{}sam}.
\vskip 0.4in
What is {\ltt{}.login}?
\vskip 0.4in
\ques
% Homework 7
You have installed a new login program (called {\ltt{}pgetty}) and you
want to have logins begin using it.
What file do you need to change? Give the exact command to activate this change.
\vskip 0.8in
A system administrator wants to make a backup of the {\ltt{}/homes} directory
{\it every} Tuesday morning at 1AM.
How is this done? Give file name, file contents and command.
\vskip 1.4in
You want to automatically run the {\ltt{}/sbin/reboot} command this evening
at 10:00 pm.
Describe how to do this; give exact file name, file contents and command.
\vskip 1.2in
\ques
% Homework 2
Explain what is in the first three fields of a shadow file entry.
\vskip 1.5in
You want {\ltt{}pf} to be an alias for {\ltt{}ps aux}
What file do you need to modify?
\vskip 0.5in
How are groups given names?
You want joe to be a member of the groups {\ltt{}student}, {\ltt{}cecs472},
and {\ltt{}cecs476}.
What file do you need to modify?
\vskip 0.5in
\vfill\eject
\ques
% Homework 6
Give the exact commands to set up a swap partition on {\ltt{}/dev/hdb1}.
(Assume the disk has already been partitioned.)
\vskip 1.5in
\ques
% Homework 4
Write a script that lists the 3 files in {\ltt{}/var/log} that have changed
most recently.
\vskip 1.5in
\ques
% Homework 11
What dirctory contains the source code for the etherwerks cards?
\vskip 0.4in
At {\ltt{}fullerton.edu} they want to be able to access local machines
without typing the suffix {\ltt{}fullerton.edu}.
Give the file needs to be changed and the exact change.
\vskip 1.0in
A machine with a netmask of {\ltt{}255.255.255.192}
knows about two gateways, one ({\ltt{}192.168.5.2} to cable
{\ltt{}192.168.2.0} with a netmask of {\ltt{}255.255.255.192}, the other 
{\ltt{}192.168.5.1} to the rest of the network.
Give the entire routing table for this machine.
\vskip 2.0in
\vfill\eject
\ques
% Homework 12
How would you allow telnets to your machine only from machines
in the lab. Hint these machines are the only ones with
DNS domain names ending in {\ltt{}net.cecs.csulb.edu}.
Give file name(s) and contents.
\vskip 0.9in
How would you allow rlogins to your machine from accounts
on {\ltt{}cheetah} that use have the same user name.
\vskip 0.9in
Your IP number is 192.168.5.2 and netmask is 255.255.255.192;
give the exact {\ltt{}ifconfig} command you need.
\vskip 0.4in
Your default (and only) gateway is 192.168.5.1;
give the exact {\ltt{}route} command you need.
\vskip 0.4in
\ques
% Homework 1
Give a {\it command} that allow you to access the password file entry
from section 5 of the manual.
\vskip 0.4in
How would you find a command that would allow you to eject the CDROM?
\vskip 0.4in
In what {\it directory} would you most likely find
the following files:
\hfill\break
A) Log files:
\vskip 0.2in
B) Information about the CPU:
\vskip 0.2in
C) Interfaces to device drivers:
\vskip 0.2in
D) Configuration files:
\vskip 0.2in
\ques
% Homework 8
You install a serial mouse. You must change one file and one symbolic
link. Give the name of that file and that symbolic link.
\vskip 1.0in
How would you make the X11 window system rotate through the available
resolutions?
\vskip 0.7in
\bye
