\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Fall 2006, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook. No digital or communications devices.
All questions 4 points.

\ques
% Project 15
Send all messages from the printer
({\ltt{}lpr}) that are at level {\ltt{}crit} or higher
to {\ltt{}cheetah.cecs.csulb.edu}.
Give the file name and the line you need in that file.
\vskip 0.8in
\ques
% Project 16
What are the two uses of {\ltt{}pkgtool}?
\vskip 1.2in
\ques
% Project 22
You wish to provide password only access to the documents in
{\ltt{}/var/www/htdocs}.
Give the directive you need to add to {\ltt{}httpd.conf}
\vskip 2.8in
\ques
% Project 22
You wish to provide password only access to the documents in
{\ltt{}/var/www/htdocs}.
Where do you place the {\ltt{}.htaccess} file and
what do you place in it.
\vskip 2.3in
\vfill\eject
\ques
% Project 13
For looking up host names you want to use (in the order given)
(1) the local hosts file, (2) the NIS database, (3) dns.
What file do you need to change and what change do you need to make?
\vskip 1.2in
\ques
% Project 24
Give the steps to install a new {\ltt{}/etc/exports} file on 
{\ltt{}panther}, {\ltt{}lynx} and {\ltt{}cougar} from {\ltt{}cheetah}.
Assume the appropriate permissions have been set up on the
target machines.
(Don't forget to activate it.)
\vskip 2.4in
\ques
% Project 17
You want to run a web server on your machine.
What disk set needs to be installed?
\vskip 0.8in
\ques
% Project 19
How do you send all mail from {\ltt{}support-cecs} to
the file {\ltt{}support_mail}?
\vskip 1.6in
\vfill\eject
\ques
% Project 19
You want to the return address of your mail messages to be {\ltt{}cheetah}
(instead of your lab machine).
What file would you need to change?
\vskip 0.7in
\ques
% Project 18
What is in a statically linked executable that is not in a dynamically
linked executable?
\vskip 0.7in
\ques
% Project 23
There are two machines for {\ltt{}ns.myspace.com} ({\ltt{}190.14.1.1})
supplies name service:
{\ltt{}x.myspace.com} ({\ltt{}190.14.3.1}) and 
{\ltt{}y.myspace.com} ({\ltt{}190.14.3.2}).
Give the entire zone file for the zone {\ltt{}myspace.com}.
\vskip 4.3in
\ques
% Project 23
Give the reverse zone entry in {\ltt{}named.conf}
for {\ltt{}190.14}  assuming
the name of the zone file is {\ltt{}n190.rev}.
\vfill\eject
\ques
% Project 20
Describe how {\ltt{}bob} allow {\ltt{}csa472z1} (and only
{\ltt{}csa472z1}) to modify the file {\ltt{}~bob/msg_from_z1}.
Briefly describe the source code involved (do not write the source code)
and the command you need to allow that code work.
\vskip 1.8in
\ques
% Project 14
You wish to access the files in the
{\ltt{}/local/public} directory on {\ltt{}lynx.net.cecs.csulb.edu}.
What file do you need to change and what change do you need to make?
\vskip 0.9in
\ques
% Project 14
You want to make your directory 
{\ltt{}/local/public}
available to
{\ltt{}cougar.net.cecs.csulb.edu}.
What file do you need to change?
What change do you need to make?
What command do you need to run?
\vskip 1.2in
\ques
% Project 25
You want to make your directory 
{\ltt{}/local/public}
available to
{\ltt{}windows.net.cecs.csulb.edu}.
What file do you need to change?
What change do you need to make?
What command do you need to run?
\vskip 1.5in
\vfill\eject
\ques
% Project 17
When you reinstalled Linux you ran two commands
before your rebooted.
What were those commands?
\vskip 0.9in
\ques
% Project 18
When a user accesses anonymous ftp you want the
contents of the file {\ltt{}~ftp/hello.txt}
to be displayed.
What file do you change? What change do you make?
\vskip 1.0in
\ques
% Project 15
Assuming you are running {\ltt{}lpd}, how do you set up printing
to the printer named {\ltt{}lp} on {\ltt{}cheetah.}
Give file name and contents.
\vskip 1.2in
\ques
% Project 21
You wish to receive the news group ``general.476a".
What directory specific to this group should exist on your server?
\vskip 1.0in
\ques
% Project 21
You are exchanging news with {\ltt{}grok.csulb.edu}.
Give the names of the files and lines in them that
will contain {\ltt{}grok}.
\vskip 2.2in
\vfill\eject
Analysis section. Assume {\ltt{}lab88} is a machine you administer.
For each of the questions on this page
state what things would you check on {\ltt{}lab88}
and for each thing you would check give the command you would use to
perform the check.

\ques
As {\ltt{}csa476z1}, the command 
{\ltt{}ls -l} gives
``{\ltt{}-rw-r--r-- 1 csa476z1 40 1342 Dec 6 2006 demo}".
\vfill
\ques
Telnet from {\ltt{}cougar} gives ``connection refused".
\vfill
\ques
News is working locally and arriving from jaguar,
but {\ltt{}nntpsend} doesn't get it to jaguar.
\vfill
\ques
Your {\ltt{}named} doesn't start.
\bye
