\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Fall 2006, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open book, open notebook. (All question 8 points, 96 total points possible)
\hfill\break
\ques
% Homework 1
How would you find a command to convert a text file to postscript?
\vskip 0.4in
How would you find out which directory the {\ltt{}test} program is in.
\vskip 0.4in
In what {\it directory} would you most likely find
the following files:
\hfill\break
A) Information about your DMA channels:
\vskip 0.3in
B) The configuration file for your printer:
\vskip 0.3in
C) The {\ltt{}ifconfig} command:
\vskip 0.3in
D) Log files:
\vskip 0.3in
\ques
% Homework 4
Write a script that counts how many {\ltt{}tty} devices are listed in 
 the ({\ltt{}/dev}) directory.
\vskip 2.0in
\ques
% Homework 3
The user {\ltt{}fay} has  a home directory of {\ltt{}/d2/u3/fay},
a shell of {\ltt{}/bin/tcsh}, a user number of {\ltt{}32101}
and a base group of {\ltt{}119}.
Give the {\ltt{}/etc/passwd} entry for {\ltt{}fay}.
\vskip 0.4in
Give the {\ltt{}/etc/shadow} entry for {\ltt{}fay}.
\vskip 0.4in
Give the steps to set up the user {\ltt{}fay}?
\vskip 1.2in
\vfill\eject
\ques
% Homework 7
You wish to change your system so that it uses a graphic screen for the login
process instead of the text screen. 
What file do you need to change?
\vskip 0.4in
You wish to update the locate database (i.e., run {\ltt{}/usr/bin/updatedp}) once
every day.
How can you do this? Give file name, file contents and command.
\vskip 1.4in
You want to see how many people are logged in at midnight.
You need to save this information to a file since you won't be here at midnight.
Describe how to do this; give exact name of your script file, the file contents
and command.
\vskip 1.6in
\ques
% Homework 2
You wish to add {\ltt{}bob} to the {\ltt{}guest} group;
what file do you need to modifiy?
\vskip 0.4in
As root you want to be able to type {\ltt{}a.out} instead of
always typing {\ltt{}./a.out}
What modification do you need to make and to what file?
\vskip 0.4in
What is an alias and what can you use it for?
\vskip 0.8in
\ques
% Homework 8
The control-alt-plus to switch screen resolutions can be disabled.
Which file would you have to modify to do this?
\vskip 0.4in
What command would you run to find out what your current screen resolution is.
\vskip 0.4in
Give the command you would use to find out what device is designated as the mouse?
\vskip 0.4in
\vfill\eject
\ques
% Homework 10
How do you make control-Y interrupt a program ({\ltt{}intr})?
\vskip 0.4in
Give the exact tar command to make a compressed backup of {\ltt{}/home}
to the file {\ltt{}/tmp/bkup.tgz}.
\vskip 0.4in
\ques
% Homework 5
How would you modify partition {\ltt{}/dev/hdd1} from being
a Linux partition to being a swap partition.
(Just modify the partition table, not the contents of the partition.)
\vskip 1.0in
Give the exact command to set up an {\ltt{}ext2} file system in the partition
{\ltt{}/dev/hdd2}. (Assume the partition already exists.)
\vskip 0.4in
\ques
% Homework 9
You have just added a 3Com905 ethernet card to your machine.
How do you modify the kernel to use this card?
\vskip 1.5in
Name one thing you deleted from the configuration when building the kernel.
\vskip 0.4in
You wish to boot Linux from {\ltt{}/dev/hdc2} with no wait.
The kernel is called {\ltt{}vmlinuz} and has already been placed into
{\ltt{}/boot}.
Give the exact contents of your {\ltt{}lilo.conf}.
\vskip 1.8in
\vfill\eject
\ques
% Homework 6
What command would you use to find out what percentage of the CPU the
operating system was spending in user mode.
\vskip 0.4in
{\ltt{}/dev/hdb3} is a swap partition.
Give the corresponding {\ltt{}fstab} entry.
\vskip 0.6in
\ques
% Homework 12
Your IP number is {\ltt{}128.74.2.151} and netmask is {\ltt{}255.255.255.240};
give the exact {\ltt{}ifconfig} command you need.
\vskip 0.4in
Your default (and only) gateway is {\ltt{}128.74.2.149};
give the exact {\ltt{}route} command you need.
\vskip 0.4in
You wish to completely disable the use of the {\ltt{}ftp} command to
access your machine.
Give file name and modification to do this.
\vskip 0.8in
You wish do allow {\ltt{}ftp} only from machines ending in
{\ltt{}cecs.csulb.edu}.
Give the file names and the lines you would add to each file.
\vskip 1.6in
\ques
% Homework 11
A machine has internet number {\ltt{}128.74.2.151} and
netmask {\ltt{}255.255.255.240};
give it's cable number and broadcast address.
\vskip 1.0in
How do you find out your broadcast address?
(Give a command.)
\vskip 0.4in
How do you find out your gateways?
(Give a command.)
\vskip 0.4in
What file determines your DNS server?
\vskip 0.4in
\bye
