\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2006, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook. No digital or communitcations devices.
All questions 4 points.

\ques
% Project 13
You want to use the passwords ({\ltt{}shadow}) from the NIS server
{\ltt{}cougar} ({\ltt{}134.139.248.20})
before those found in your local shadow file.
What files do you need to change and what changes do you need to make?
\vskip 1.7in
\ques
% Project 24
Give the steps to install a new {\ltt{}smb.conf} file on 
{\ltt{}lab97}, {\ltt{}lab98} and {\ltt{}lab99} from {\ltt{}jaguar}.
Assume the appropriate permissions have been set up on the
target machines.
Don't forget you need to have samba reload or restart.
\vskip 2.4in
\ques
% Project 19
In {\ltt{}sendmail.cf}:
Define a group {\ltt{}H} to contain {\ltt{}panther} and {\ltt{}puma}
and a macro {\ltt{}J} to be {\ltt{}sue}.
If you were looking for where the macro J is used what would you look for?
\vskip 1.6in
\ques
% Project 17
Describe what ``select target" does.
\vskip 1.5in
\vfill\eject
\ques
% Project 19
You want mail going to {\ltt{}bob} to be delivered locally
and not to the smart host.
What file would you need to change and what change would you need to make.
\vskip 1.0in
\ques
% Project 18
How would you want to find out what libraries are used by the ftp server
({\ltt{}/usr/sbin/proftpd}).
\vskip 0.7in
\ques
% Project 23
You have two machines for which you supply name service.
{\ltt{}a.bell.com} ({\ltt{}131.42.1.1}) and 
{\ltt{}b.bell.com} ({\ltt{}131.42.1.2}).
Give the entire reverse zone file for the zone {\ltt{}131.42},
including the SOA, if the DNS server for that zone
is {\ltt{}ns1.level3.net} ({\ltt{}144.45.1.2}).
\vskip 4.2in
\ques
% Project 23
Give the zone entry in {\ltt{}named.conf}
for {\ltt{}bell.com}  assuming
the name of the zone file is {\ltt{}named.bell}.
\vfill\eject
\ques
% Project 14
You want to export your
{\ltt{}/usr/share} directory on your machine to {\ltt{}cougar}
({\ltt{}134.139.248.20}).
What file do you need to change and what change do you need to make?
\vskip 0.8in
\ques
% Project 14
You want users on your machine to have access to the files in the
{\ltt{}/home/share} directory on {\ltt{}lynx} ({\ltt{}134.139.248.22}).
What file do you need to change and what change do you need to make?
\vskip 0.9in
\ques
% Project 20
Explain how the instructor's {\ltt{}getscore} let's you see you
grade, but no one else's.
\vskip 1.8in
\ques
% Project 15
Assuming you are running {\ltt{}CUPS}, how do you set up printing
to the printer named {\ltt{}laser2} on {\ltt{}panther}
({\ltt{}134.139.248.21}).
\vskip 1.2in
\ques
% Project 25
Give the {\ltt{}smb.conf} entries necessary to make
{\ltt{}/usr/share} available as a public share to
machines running Windows.
\vskip 1.5in
\vfill\eject
\ques
% Project 17
When you reinstalled Linux you temporarily disabled the web server.
Describe how you did this.
\vskip 0.9in
\ques
% Project 18
You want anonymous ftp to display a special welcome message.
What file do you put it in? (Give full path.)
\vskip 0.8in
\ques
% Project 21
You wish to send the news group ``general.476a" from your machine
to the {\ltt{}panther} ({\ltt{}134.139.248.21)}) news server.
What files will need to be modified
and what modification would be made to that files?
\vskip 2.6in
\ques
% Project 21
You wish your news server to receive the news group ``general.476b"
from the {\ltt{}cougar} ({\ltt{}134.139.248.20)}) news server.
What files need to be modified and what modifications are done to those files?
\vskip 2.2in
\vfill\eject
\ques
% Project 15
Send all log messages from the new server
({\ltt{}news}) that are at level {\ltt{}notice} or higher
to a file called {\ltt{}/var/log/news}.
Give the file name and the line you need in that file.
\vskip 0.8in
\ques
% Project 16
How do you list the components that are installed on your machine?
\vskip 1.2in
\ques
% Project 22
You want all users except {\ltt{}sue} to be able to make their
own web pages.
What file do you need to change and what changes do you need to make?
(Assume all home directories are in {\ltt{}/home}.)
\vskip 2.0in
\ques
% Project 22
You wish your friend from {\ltt{}UCLA} to be able to use his browser
to access a couple files you wish to keep private from everyone else.
Describe how you would do this.
\vskip 2.3in
\vfill\eject
Analysis section. Assume {\ltt{}lab88} is a machine you administer.
For each of the questions on this page
state what things would you check on {\ltt{}lab88}
and for each thing you would check state how you would perform the check.

\ques
{\ltt{}telnet cheetah} returns the message ``no path to
{\ltt{}cheetah.ics.uci.edu}".
\vfill
\ques
The home directories on {\ltt{}cheetah} are not visible.
\vfill
\ques
The instructor informs that {\ltt{}telnet} into you machine isn't working.
\vfill
\ques
{\ltt{}bob} can get his files off your machine using ftp,
but {\ltt{}csa476z7} can't.
\bye
