\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2006, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open book, open notebook. (All question 8 points, 96 total points possible)
\hfill\break
\ques
% Homework 6
Give the exact commands to set up a 2 megabyte swap file
called {\ltt{}/var/swap3}.
\vskip 0.8in
Give the command to turn swapping on on that file.
\vskip 0.4in
\ques
% Homework 12
Your IP number is {\ltt{}140.74.3.148} and netmask is {\ltt{}255.255.255.192};
give the exact {\ltt{}ifconfig} command you need.
\vskip 0.4in
Your default (and only) gateway is {\ltt{}140.74.3.149}
give the exact {\ltt{}route} command you need.
\vskip 0.4in
You wish to completely disable the use of the {\ltt{}rlogin} command to
access your machine.
Give file name and modification to do this.
\vskip 0.8in
You wish do allow {\ltt{}telnet} from any machine ending in
{\ltt{}.net.cecs.csulb.edu}, but disallow all others.
Give the file names and the lines you would add to each file.
\vskip 1.6in
\ques
% Homework 8
You want to know what ``Driver" is being used by your video card.
Give the commands you would use to do this.
\vskip 1.0in
What file would you need to change to make a {\ltt{}1280x1024} screen resolution
available.
\vskip 0.4in
\vfill\eject
\ques
% Homework 1
How would you find the meaning of the termcap entry ``mb"?
\vskip 0.4in
How would you find out which directory the {\ltt{}shutdown} is in.
\vskip 0.4in
In what {\it directory} would you most likely find
the following files:
\hfill\break
A) The configuration file for your sound card.:
\vskip 0.3in
B) Log files:
\vskip 0.3in
C) Information about which file systems your kernel is supporting:
\vskip 0.3in
D) The {\ltt{}reboot} command:
\vskip 0.3in
\ques
% Homework 4
Write a script that counts the number of compiles ({\ltt{}gcc}) that
are running.
\vskip 2.0in
\ques
% Homework 3
The user {\ltt{}joe} has  a home directory of {\ltt{}/u3/joe},
a shell of {\ltt{}/bin/bash}, a user number of {\ltt{}10101}
and a base group of {\ltt{}141}.
Give the {\ltt{}/etc/passwd} entry for {\ltt{}sam}.
\vskip 0.4in
Give the steps to set up the user {\ltt{}joe}?
\vskip 1.2in
\vfill\eject
\ques
% Homework 7
You have want {\ltt{}<alt-F7>} to be a seventh virtual screen.
What file do you need to change? Give the exact command to activate this change.
\vskip 0.8in
You wish to reboot the Linux systems to clean out stuck student programs
every morning at 2AM.
How can you do this automatically? Give file name, file contents and command.
\vskip 1.4in
You want to build a new {\ltt{}bzImage} after all the employees are out
of the office and not using the system (6PM).
Describe how to do this; give exact name of your script file, the file contents
and command.
\vskip 1.6in
\ques
% Homework 2
What does an {\ltt{}x} in the second field of the password file mean?
\vskip 0.4in
You wish to run {\ltt{}/usr/lib/news/bin/ctlinnd} without always
having to {\ltt{}cd} or type the {\ltt{}/usr/lib/news/bin}.
What modification do you need to make and to what file?
\vskip 0.8in
What goes into the second field of the {\ltt{}shadow} file?
\vskip 0.4in
\ques
% Homework 11
A machine has an internet number {\ltt{}140.74.3.148}
and a a netmask of {\ltt{}255.255.255.192};
give it's cable number and broadcast address.
\vskip 0.8in
How do your find out the fully qualified hostname of {\ltt{}jaguar}.
Give a command.
\vskip 0.4in
What does the {\ltt{}arp} command do?
\vskip 0.8in
\vfill\eject
\ques
% Homework 10
Give the exact tar command to make a compressed backup of {\ltt{}/etc}
to a floppy disk.
\vskip 0.4in
In what {\it file} would you look to find out what sequence is sent to the
screen to cause letters to blink. 
\vskip 0.4in
\ques
% Homework 5
Explain how you would create two partitions on {\ltt{}hdd} and
set one of them up to contain a Linux file system.
\vskip 1.6in
Give the exact line that needs to be in the {\ltt{}fstab} to
have the file system you just created on {\ltt{}hdd} attached to the directory
trees as {\ltt{}/mystuff} automatically at boot time.
\vskip 0.5in
\ques
% Homework 9
Give the three {\ltt{}make} commands you used to build the kernel.
\vskip 1.5in
Name one thing you deleted from the configuration when building the kernel.
\vskip 0.5in
You wish to boot Linux from {\ltt{}/dev/hda2} with a 5 second wait.
The kernel is called {\ltt{}bzImage} and has already been placed into
{\ltt{}/boot}.
Give the exact contents of your {\ltt{}lilo.conf}.
\vskip 1.8in
\bye
