\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Fall 2007, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook. No digital or communications devices.
All questions 4 points.

\ques
% Project 17
Give 2 disk sets and state briefly what they contain.
\vskip 1.0in
\ques
% Project 18
You want to use the file {\ltt{}~ftp/HiThere} as the
welcome message for anonymous ftp service.
What file do you change? What change do you make?
\vskip 1.0in
\ques
% Project 15
You want print to {\ltt{}puma} to the printer puma calls {\ltt{}ecs1}.
What file do you need to modify?
What do you need to add to that file?
\vskip 1.2in
\ques
% Project 21
You want users on {\ltt{}lynx} to use {\ltt{}jaguar} as their news server.
What file do you need to change and what change to you need to make?
\vskip 1.0in
\ques
% Project 21
On your lab machine, you wish to exchange news with {\ltt{}cougar}
(in addition to {\ltt{}jaguar}).
Give the names of the files you will need to change and lines you
will have to add to each of those files.
\vskip 2.2in
\vfill\eject
\ques
% Project 15
You wish to record what user printed what
(level {\ltt{}info}, facility {\ltt{}lpr}) in
the file {\ltt{}/var/log/printjobs}.
Give the name of the file you need to modify and the line you need to
add to that file.
\vskip 0.8in
\ques
% Project 16
You installed Linux using the NFS option, give two other options
you could have used.
\vskip 0.8in
\ques
% Project 22
You move your system web pages are to the directory {\ltt{}/home/apache}.
What file do you need to change and what do you need to change in that file.
\vskip 1.0in
\ques
% Project 22
You want to require logins for access to the directory
{\ltt{}/home/apache/confidential}.
Describe how you would do this (give file names and contents).
\vskip 2.8in
\vfill\eject
\ques
% Project 13
You wish to modify your system so that it uses only the local list of
groups and not those from NIS.
What file do you need to change and what change do you need to make?
\vskip 0.8in
\ques
% Project 20
Describe what capability a setuid program provides. (Short answer, English.)
\vskip 2.0in
\ques
% Project 18
You need to block the ability to access your machine using ftp into the
{\ltt{}bob} account.
What file do you need to change and what change do you need to make?
\vskip 0.8in
\ques
% Project 19
You want to place all your mail with the word {\ltt{}cecs476} in the
body into the file {\ltt{}cecs476_mail}.
What file do you need to create and what does that file need to contain?
\vskip 1.6in
\vfill\eject
\ques
% Project 19
You want to rewrite the return address on all mail from your machine
to be from {\ltt{}cecs.csulb.edu}
What file would you need to change?
\vskip 0.5in
\ques
% Project 20
You want only {\ltt{}bob} to be able to {\ltt{}su} to {\ltt{}root}.
What files do you to change and what changes to you need to make?
\vskip 1.2in
\ques
% Project 23
There are two machines for which {\ltt{}ns.q.com} ({\ltt{}135.22.1.1})
supplies name service:
{\ltt{}a.q.com} ({\ltt{}135.22.2.2}) and 
{\ltt{}b.q.com} ({\ltt{}135.22.2.3}).
Give the forward and reverse sone entries for the  {\ltt{}named.conf} file.
\vskip 1.5in
\ques
% Project 23
Give the entire reverse zone file for the zone {\ltt{}135.22.2}.
\vskip 3.5in
\vfill\eject
\ques
% Project 24
Give the steps you would take on {\ltt{}puma} to install and use
a new {\ltt{}/etc/printcap} file on {\ltt{}panther}.
You will perform the install from a file called {\ltt{}printcap}
located on {\ltt{}puma}.
To activate the change you will need to issue the command
{\ltt{}/etc/rd.d/rc.lprng restart} on panther.
\vskip 2.4in
\ques
% Project 14
You wish to attach the files the
{\ltt{}/hdb/disk2} directory on {\ltt{}jaguar.net.cecs.csulb.edu}
to your file tree as {\ltt{}/mnt}.
Give the {\ltt{}fstab} entry to do this.
\vskip 0.6in
\ques
% Project 14
You want to make your directory 
{\ltt{}/homes}
available (read write) to {\ltt{}panther} and {\ltt{}puma}
What file do you need to change?
What change do you need to make?
What command do you need to run?
\vskip 1.6in
\ques
% Project 25
You want to make a directory on your
Linux machine available to all machines running Microsoft Windows. 
What file do you need to change?
What do you need to add to that file?
\vskip 1.2in
\vfill\eject
Analysis section. Assume {\ltt{}lab88} is a machine you administer.
For each of the questions on this page
state what things would you check on {\ltt{}lab88}
and for each thing you would check give the command you would use to
perform the check.

\ques
Ping to {\ltt{}lab87} works, but ping to {\ltt{}panther} doesn't.
\vfill
\ques
Ftp into {\ltt{}bob} works, but ftp into {\ltt{}csa476z6} doesn't.
\vfill
\ques
The command {\ltt{}telnet panther} gets the message,
no  machine {\ltt{}panther.net.cect.csulb.edu}.
\vfill
\ques
You are trying to debug your news server configuration
and you aren't getting any news server messages in the log files.
\bye
