\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Fall 2007, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open book, open notebook. (All question 8 points, 96 total points possible)
\hfill\break
\ques
% Homework 8
How do you switch video resolutions?
\vskip 0.4in
How do you find out the current resolution of your X-windows display?
\vskip 0.4in
What program would you run if you got a new monitor with new scan rates?
\vskip 0.4in
\ques
% Homework 5
Give the exact command to build a Linux file ext2 system on the
{\ltt{}/dev/hdb1}.
\vskip 0.4in
Give the {\ltt{}fstab} entry to attach the file system
on {\ltt{}/dev/hdb1} at {\ltt{}/u1}.
\vskip 0.4in
Give the exact command to mount the file system on {\ltt{}/dev/hdb1}
to {\ltt{}/u1} by hand (i.e., not using {\ltt{}fstab}).
\vskip 0.4in
\ques
% Homework 7
You want to boot to the graphical X-windows login interface (run level 6).
What file do you need to change?
\vskip 0.4in
You want to begin building the kernel on your machine at 1:30am.
Describe how to do this; give exact name of your script file, the file contents
and command.
\vskip 1.7in
You wish to terminate ({\ltt{}killall -9}) all {\ltt{}a.out} programs
running on your machine once a night.
How can you do this? Give file name, file contents and command.
\vskip 1.4in
\vfill\eject
\ques
% Homework 4
Write a script that prints the names of the 3 files in {\ltt{}/var/log}
that have changed most recently.
\vskip 1.5in
\ques
% Homework 3
The user {\ltt{}bill} has  a home directory of {\ltt{}/home/bill},
a shell of {\ltt{}/bin/ksh}, a user number of {\ltt{}5432}
and a base group of {\ltt{}234}.
Give the password and shadow entries for {\ltt{}bill}.
\vskip 1.4in
\ques
% Homework 2
How do you make {\ltt{}t} a short-hand for {\ltt{}telnet cheetah}.
What modification do you need to make and to what file?
\vskip 1.0in
If you wish the user {\ltt{}sue} to belong to groups {\ltt{}src} (GID 201)
in addition to her base group;
what modification do you need to make and to what file?
\vskip 1.0in
What does the user PATH do?
\vskip 1.2in
\vfill\eject
\ques
% Homework 1
How would you find out what directory the manual entries for {\ltt{}lilo}
are in?
\vskip 0.4in
How would you find out what devices contain the letters {\ltt{}tty}?
\vskip 0.4in
In what {\it directory} would you most likely find
the following:
\hfill\break
A) The configuration file for the web server:
\vskip 0.3in
B) Error messages about networking:
\vskip 0.3in
C) The {\ltt{}mke2fs} command:
\vskip 0.3in
D) Whether forwarding of network packets is allowed by your kernel:
\vskip 0.3in
\ques
% Homework 6
Give a command that would list all the processes that are running that
contain the word ``browser"?
\vskip 0.4in
Give the exact command you would use to turn swapping on on
{\ltt{}/dev/hda2}.
\vskip 0.4in
\ques
% Homework 9
You install a new flash card reader.
Describe how you would modify your machine to use this card?
\vskip 1.5in
You wish to add a boot boot option to your machine.
The boot drive will be {\ltt{}/dev/hdb2}, the kernel will
be called {\ltt{}vmlinuzb}.
Give the lines you need to add to your {\ltt{}lilo.conf}.
\vskip 1.8in
\vfill\eject
\ques
% Homework 10
You want the delete key ({\ltt{}control-?}) to terminate (interrupt)
a program. Give the exact command to set this up.
\vskip 0.4in
Give the exact command to back up {\ltt{}/etc} to {\ltt{}/dev/usb0}
(assume the device is enabled).
\vskip 0.4in
\ques
% Homework 11
A machine has internet number {\ltt{}189.102.7.87} and
netmask {\ltt{}255.255.255.240}; give it's cable number and broadcast address.
\vskip 1.0in
How do you find out the ethernet card addresses of the machines your computer 
has been communicating with?  (Give a command.)
\vskip 0.4in
What file determines your DNS name server?
\vskip 0.4in
How do you find out your default route?
(Give a command.)
\vskip 0.4in
\ques
% Homework 12
Your IP number is {\ltt{}189.102.7.87} and netmask is {\ltt{}255.255.255.240};
give the exact {\ltt{}ifconfig} command you need.
\vskip 0.4in
Your default (and only) gateway is {\ltt{}189.102.7.89};
give the exact {\ltt{}route} command you need.
\vskip 0.4in
You wish to completely disable the use of the {\ltt{}ftp} command to
access your machine.
Give file name and modification to do this.
\vskip 0.8in
You wish do allow {\ltt{}telnet} only from {\ltt{}cheetah.net.csulb.edu}.
Give file names and modifications to do this.
\vskip 1.4in
\bye
