\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2007, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook. No digital or communications devices.
All questions 4 points.

\ques
% Project 15
You wish to send all error messages (level {\ltt{}err})
from the {\ltt{}crond}(facility {\ltt{}cron})
to the file {\ltt{}/var/log/cronerr}.
Give the file name and the line you need in that file.
\vskip 1.0in
\ques
% Project 16
What utility is used install or inspect packages?
\vskip 0.8in
\ques
% Project 22
You wish to allow sam (and only sam) to use an {\ltt{}.htaccess} file to
control access to the {\ltt{}private} subdirectory of his web directory.
What file do you need to change and show the entry you need to make in that
file.
\vskip 2.8in
\ques
% Project 22
You wish to block all web access to all home directories that are located
inside the {\ltt{}/u4/students} directory.
What file do you need to change and what do you need to add to that file.
\vskip 2.3in
\vfill\eject
\ques
% Project 13
Your ypserver is {\ltt{}panther} ({\ltt{}134.139.248.21}).
What file do you need to change and what change do you need to make?
\vskip 1.0in
\ques
% Project 20
How do you set up a setuid program?
\vskip 1.5in
\ques
% Project 18
Give the steps to enable anonymous ftp.
\vskip 1.3in
\ques
% Project 19
How do you send all mail on the subject {\ltt{}backups} to
the file {\ltt{}backup.folder}?
Give the file and the contents.
\vskip 1.6in
\vfill\eject
\ques
% Project 19
You want all mail from you machine to go to {\ltt{}cheetah}
before it goes to it's final destination.
What file would you need to change?
\vskip 0.6in
\ques
% Project 20
You want to allow users to login even if their home directory
is not available.
What file do you need an entry in?
\vskip 0.6in
\ques
% Project 23
There are two machines for {\ltt{}dns.mytube.com} ({\ltt{}182.33.1.1})
supplies name service:
{\ltt{}a.mytube.com} ({\ltt{}182.33.2.6}) and 
{\ltt{}b.mytube.com} ({\ltt{}182.33.2.7}).
Give the entire zone file for the zone {\ltt{}mytube.com}.
\vskip 4.3in
\ques
% Project 23
Give the zone entry in {\ltt{}named.conf}
for {\ltt{}mytube.com} assuming
the name of the zone file is {\ltt{}mytube.list}.
\vfill\eject
\ques
% Project 24
Give the steps you would take on {\ltt{}lynx} to install and use
a new {\ltt{}/etc/smb.conf} file on {\ltt{}panther}.
You will perform the install from a file called {\ltt{}newsmb}
located on {\ltt{}lynx}.
Remember to you will need to restart samba.
\vskip 2.4in
\ques
% Project 14
You wish to attach the files the
{\ltt{}/u7} directory on {\ltt{}d1.cecs.csulb.edu}
to your file tree as {\ltt{}/net/d1/u7}.
Give the {\ltt{}fstab} entry to do this.
\vskip 0.9in
\ques
% Project 14
You want to make your directory 
{\ltt{}/public}
available (read only) to all machines with numbers starting with 134.139.248.
What file do you need to change?
What change do you need to make?
What command do you need to run?
\vskip 1.6in
\ques
% Project 25
You want to make a printer on your
Linux machine available to another machine running Microsoft Windows. 
What file do you need to change?
What service do you need to run?
\vskip 1.2in
\vfill\eject
\ques
% Project 17
You want to run a java compiles on your machine.
What disk set needs to be installed?
\vskip 0.6in
\ques
% Project 18
How do you allow the accounts whose passwords are delivered
using NIS to use the ftp service?
What file do you change? What change do you make?
\vskip 1.4in
\ques
% Project 15
You want to enable printing, it should automatically start at boot.
What file do you need to modify?
What change to you need to make in the {\ltt{}rc.d} directory?
What server should you see running (if you do a ps)?
\vskip 1.6in
\ques
% Project 21
You wish to allow {\ltt{}panther.net.cecs.csulb.edu} to read
and post news on your machine.
What file do you need to change?
What change to you need to make?
\vskip 1.4in
\ques
% Project 21
You {\ltt{}innd} is sending news to and receiving news from
{\ltt{}cougar.net.csulb.edu}.
Give the names of the files and lines in them that
will contain {\ltt{}cougar}.
\vskip 2.2in
\vfill\eject
Analysis section. Assume {\ltt{}lab88} is a machine you administer.
For each of the questions on this page
state what things would you check on {\ltt{}lab88}
and for each thing you would check give the command you would use to
perform the check.

\ques
When {\ltt{}csa476z1} logs in he gets the
message ``No home directory". 
\vfill
\ques
Telnet from {\ltt{}cougar} doesn't work.
Telnet from {\ltt{}lab87} does.
\vfill
\ques
{\ltt{}nslookup test01.net88.csulb.edu lab88}
give the message ``{\ltt{}SERVER FAILED}".
\vfill
\ques
Your {\ltt{}httpd} doesn't start.
\bye
