\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2007, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open book, open notebook. (All question 8 points, 96 total points possible)
\hfill\break
\ques
% Homework 10
You want a program to use boldface for its prompts.
What manual entry do you need to read?
\vskip 0.8in
Give the exact commands to extract the file {\ltt{}hwk4.tgz}
into bob's home directory.
\vskip 0.4in
\ques
% Homework 3
The user {\ltt{}joe} has  a home directory of {\ltt{}/home/joe},
a shell of {\ltt{}/bin/bash}, a user number of {\ltt{}4321}
and a base group of {\ltt{}123}.
Give the steps to set up the user {\ltt{}joe}?
\vskip 1.4in
\ques
% Homework 2
How do you make {\ltt{}cdl} a short-hand for {\ltt{}cd /usr/src/linux}.
What modification do you need to make and to what file?
\vskip 0.8in
How do you enable the execution of {\ltt{}ypxfr} and all other files
in the same directory as it without always typing {\ltt{}/usr/lib/yp/}
in front of the command.
What modification do you need to make and to what file?
\vskip 0.8in
How do you find out the date on which bob's password was changed?
Give file, contents and math.
\vskip 1.4in
\vfill\eject
\ques
% Homework 1
How would you find the option to make the {\ltt{}ls} command sort by file size?
\vskip 0.4in
How would you find out wat files in the {\ltt{}/etc} directory end in
{\ltt{}.conf}?
\vskip 0.4in
In what {\it directory} would you most likely find
the following:
\hfill\break
A) Log files:
\vskip 0.3in
B) The configuration file for your DSL modem card:
\vskip 0.3in
C) Whether your CPU is from Intel or AMD:
\vskip 0.3in
D) The {\ltt{}ls} command:
\vskip 0.3in
\ques
% Homework 6
What command would you use to find out how much swap space you have?
\vskip 0.4in
Give the exact command you would use to set up a swap structure on
{\ltt{}/dev/hdb1}.
\vskip 0.4in
\ques
% Homework 9
You get a USB storage device.
Describe how you would modify your machine to use this card?
\vskip 1.5in
How can you find out what version of the kernel your are running?
Give the exact command.
\vskip 0.4in
You wish to add a second boot option to your machine.
The boot drive will be {\ltt{}/dev/hdb3}, the kernel will
be called {\ltt{}bzImage}.
Give the lines you need to add to your {\ltt{}lilo.conf}.
\vskip 1.8in
\vfill\eject
\ques
% Homework 7
You want alt-F7 to allow a seventh virtual console.
What file do you need to change?
\vskip 0.4in
You might have a problem with the Linux partition on {\ltt{}/dev/hdb3},
so you want to run a {\ltt{}fsck} on that partition at 23:30 this
evening.
Describe how to do this; give exact name of your script file, the file contents
and command.
\vskip 1.6in
You wish to clean the tmp directory ({\ltt{}rm /tmp/*}) every morning
at 2am.
How can you do this? Give file name, file contents and command.
\vskip 1.4in
\ques
% Homework 8
You are switching to a Radeon Video card.
Which file has to be modified to make X recognize this card?
\vskip 0.4in
You run a probe of your video system.
How do you know where to look for for the probe informations?
\vskip 0.4in
Name {\it one} mouse protocol.
\vskip 0.4in
\ques
% Homework 5
Give the exact command to build a Linux file ext2 system on the
{\ltt{}/dev/hdb3}.
\vskip 0.4in
Give the {\ltt{}fstab} entry to attach the file system
on {\ltt{}/dev/hdb3} at {\ltt{}/d3}.
\vskip 0.4in
Give the exact command to mount the file system on {\ltt{}/dev/hdb3}
to {\ltt{}/d3} by hand (i.e., not using {\ltt{}fstab}).
\vskip 0.4in
\vfill\eject
\ques
% Homework 4
Write a script that prints the last 3 lines in the messages file that
contain the word ``automount".
\vskip 2.0in
\ques
% Homework 11
A machine has internet number {\ltt{}192.214.4.151} and
netmask {\ltt{}255.255.255.248}; give it's cable number and broadcast address.
\vskip 1.0in
How do you test if you can get to another machine on the network
(Give a command.)
\vskip 0.4in
What file determines if you use DNS for host names?
\vskip 0.4in
How do you find out your ethernet address?
(Give a command.)
\vskip 0.4in
\ques
% Homework 12
Your IP number is {\ltt{}192.214.4.151} and netmask is {\ltt{}255.255.255.248};
give the exact {\ltt{}ifconfig} command you need.
\vskip 0.4in
Your default (and only) gateway is {\ltt{}192.214.4.153};
give the exact {\ltt{}route} command you need.
\vskip 0.4in
You wish to completely disable the use of the {\ltt{}rlogin} command to
access your machine.
Give file name and modification to do this.
\vskip 0.8in
You wish do allow {\ltt{}rlogin} only from machines on your local cable
(see IP number and netmask above).
Give file name and modification to do this.
\vskip 0.8in
\bye
