\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2008, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook. No digital or communications devices.
All questions 4 points.

\ques
% Project 24
Give the steps you would take on {\ltt{}puma} to install and use
a new {\ltt{}/etc/exports} file on {\ltt{}panther}.
You will perform the install from a file called {\ltt{}exports}
located on {\ltt{}puma}.
To activate the change you will need to issue the command
{\ltt{}exportfs -a} on {\ltt{}panther}.
\vskip 2.4in
\ques
% Project 14
You wish to attach the files the
{\ltt{}/u3} directory on {\ltt{}cheetah.cecs.csulb.edu}
to your file tree as {\ltt{}/mnt}.
Give the {\ltt{}fstab} entry to do this.
\vskip 0.6in
\ques
% Project 14
You want to make your directory 
{\ltt{}/homes}
available (read write) to {\ltt{}cougar}.
What file do you need to change?
What change do you need to make?
\vskip 1.2in
\ques
% Project 25
You want to make a directory called {\ltt{}/myshare} on your
Linux machine available to all machines running Microsoft Windows as
{\ltt{}LinuxShare}.
What file do you need to change?
What do you need to add to that file?
\vskip 1.2in
\vfill\eject
\ques
% Project 17
What is the install step between setting up swap space and selecting source?
\vskip 0.8in
\ques
% Project 18
You want only users with local accounts (not network accounts) to
be able to use the ftp service.
What file do you change? What change do you make?
\vskip 1.0in
\ques
% Project 15
You want print to {\ltt{}cougar} to the printer puma calls {\ltt{}lp}.
What file do you need to modify?
What do you need to add to that file?
\vskip 1.2in
\ques
% Project 21
You wish to block (not receive) all messages from news groups starting
with {\ltt{}alt.}
What file do you need to change and what change to you need to make?
\vskip 1.2in
\ques
% Project 21
On your lab machine, you wish to exchange news with {\ltt{}panther}
(in addition to {\ltt{}jaguar}).
Give the names of the files you will need to change and lines you
will have to add to each of those files.
\vskip 2.2in
\vfill\eject
\ques
% Project 15
You wish to record debug messages from {\ltt{}innd}
(level {\ltt{}debug}, facility {\ltt{}news}) in
the file {\ltt{}/var/log/news/debug}.
Give the name of the file you need to modify and the line you need to
add to that file.
\vskip 1.0in
\ques
% Project 16
What are the two uses of the package tool?
\vskip 1.2in
\ques
% Project 22
How would you block web access to all directories under {\ltt{}/home/students}?
What file do you need to change and what do you need to add to that file.
\vskip 2.2in
\ques
% Project 22
Given the {\ltt{}.htaccess} file that would be needed to require an
account name and password for the directory it is place in.
\vskip 2.8in
\vfill\eject
\ques
% Project 13
After you install, you wish to use accounts and groups from the NIS
server on {\ltt{}cougar} (NIS domain name: {\ltt{}FinalExam}).
What files do you need to change and what changes do you need to make?
\vskip 1.4in
\ques
% Project 20
How do you make an executable into a setuid program?
\vskip 1.0in
\ques
% Project 18
You want to present a message when a users who is using ftp enters a directory.
Where do you look to find out the name the message file should have?
\vskip 0.8in
\ques
% Project 19
You want to send all your mail with the word {\ltt{}forged} in the
``{\ltt{}Received}" header to {\ltt{}/dev/null}.
What file do you need to create and what does that file need to contain?
\vskip 1.6in
\vfill\eject
\ques
% Project 26
When you boot from the network, how does the server decide which internet
address to give you?
\vskip 1.6in
\ques
% Project 20
If a user's home directory is not available you don't want that user to be
able to login.
What file do you to change?
\vskip 0.8in
\ques
% Project 23
There are two machines for which {\ltt{}lab88.ns.com} ({\ltt{}129.41.1.1})
supplies name service:
{\ltt{}a.xyzzy.com} ({\ltt{}129.41.2.1}) and 
{\ltt{}b.xyzzy.com} ({\ltt{}129.41.2.2}).
Give the forward entries for the  {\ltt{}named.conf} file.
\vskip 1.7in
\ques
% Project 23
Give the entire forward zone file for the zone {\ltt{}xyzzy.com}.
\vskip 3.5in
\vfill\eject
Analysis section. Assume {\ltt{}lab88} is a machine you administer.
For each of the questions on this page
state what things would you check on {\ltt{}lab88}
and for each thing you would check give the command you would use to
perform the check. (If you wish to examine the file you may give the
command as {\ltt{}vi}).

\ques
Ping to {\ltt{}lab87} works, but ping to {\ltt{}panther} times out.
\vfill
\ques
{\ltt{}bob} can login, but {\ltt{}csa476z6} can't.
\vfill
\ques
You can view web pages on posted by lab87, but you when you try to
view web pages posted on panther you get ``{\ltt{}host not found}".
\vfill
\ques
Telnet's into your machine work, but rlogin's don't.
\bye
