\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2008, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open book, open notebook. (All question 8 points, 96 total points possible)
\hfill\break
\ques
% Homework 1
How would you find out what directory the {\ltt{}ls} is in?
\vskip 0.4in
How would you find out what files in {\ltt{}etc} contain the letters
{\ltt{}xorg}?
\vskip 0.4in
In what {\it directory} would you most likely find
the following:
\hfill\break
A) What devices are connected to the PCI bus?
\vskip 0.3in
B) The configuration file for the ftp service:
\vskip 0.3in
C) Information about ftp transfers:
\vskip 0.3in
D) The {\ltt{}ls} command:
\vskip 0.3in
\ques
% Homework 6
Give a command that would list all the processes that are running that
contain the word ``rpc"?
\vskip 0.4in
Give the exact command to set up a swap structure in
{\ltt{}/dev/hdd1}.
\vskip 0.4in
\ques
% Homework 9
What are the steps to rebuild a kernel?
\vskip 1.5in
You wish to add a boot boot option to your machine.
The boot drive will be {\ltt{}/dev/hdd2}, the kernel will
be called {\ltt{}bzImage}.
Give the lines you need to add to your {\ltt{}lilo.conf}.
\vskip 1.8in
\vfill\eject
\ques
% Homework 4
Write a script that prints the number of additional groups to which
{\ltt{}sue} belongs.
\vskip 1.5in
\ques
% Homework 5
Give the exact command to build a Linux file ext2 system on the
{\ltt{}/dev/hdd2}.
\vskip 0.4in
Give the {\ltt{}fstab} entry to attach the file system
on {\ltt{}/dev/hdd2} at {\ltt{}/disk}.
\vskip 0.4in
What command would you use to set up swap and Linux partitions on
{\ltt{}/dev/hdd}?
\vskip 0.4in
\ques
% Homework 7
You want alt-F7 to be a seventh screen.
What file do you need to change?
\vskip 0.4in
You want to find out what users on your machine at 1:30am.
Describe how to do this; give exact name of your script file, the file contents
and command.
\vskip 1.7in
You wish to reboot your machine every morning at 2:00am. 
How can you do this? Give file name, file contents and command.
\vskip 1.4in
\vfill\eject
\ques
% Homework 8
What command do you run to find out which video card driver got loaded?
\vskip 0.4in
How do you find out the current resolution of your X-windows display?
\vskip 0.4in
What program would you run if you got a new video card?
\vskip 0.4in
\ques
% Homework 3
The user {\ltt{}sue} has  a home directory of {\ltt{}/u1/sue},
a shell of {\ltt{}/bin/bash}, a user number of {\ltt{}1234}
and a base group of {\ltt{}123}.
Give the password entry for {\ltt{}sue}.
\vskip 1.4in
\ques
% Homework 2
How do you make {\ltt{}cdv} a short-hand for {\ltt{}cd ~djv}.
What modification do you need to make and to what file?
\vskip 1.0in
What is in the shadow file?
\vskip 1.0in
There are several commands in {\ltt{}/usr/lib/news/bin}.
How do you make them available so you won't always have to type the full path.
\vskip 1.2in
\vfill\eject
\ques
% Homework 10
You want the ({\ltt{}control-Y}) key to pause/suspend (susp)
a program. Give the exact command to set this up.
\vskip 0.4in
Give the exact command to back up {\ltt{}/etc} to {\ltt{}/dev/fd0}
(assume the device is enabled).
\vskip 0.4in
\ques
% Homework 11
A machine has internet number {\ltt{}134.132.6.34} and
netmask {\ltt{}255.255.255.248}; give it's cable number and broadcast address.
\vskip 1.0in
How do you find out the gateway your machine is using?  (Give a command.)
\vskip 0.4in
What file determines the order (dns files nis) your machine uses for
looking up host names?
\vskip 0.4in
How do you find out the address of your ethernet card?
(Give a command.)
\vskip 0.4in
\ques
% Homework 12
Your IP number is {\ltt{}134.132.6.34} and netmask is {\ltt{}255.255.255.248};
give the exact {\ltt{}ifconfig} command you need.
\vskip 0.4in
Your default (and only) gateway is {\ltt{}134.132.6.36};
give the exact {\ltt{}route} command you need.
\vskip 0.4in
You wish to completely disable the use of the {\ltt{}rlogin} ({\ltt{}login})
command to access your machine.
Give file name and modification to do this.
\vskip 0.8in
You wish do allow {\ltt{}ftp} only from {\ltt{}puma.net.cecs.csulb.edu}.
Give file names and modifications to do this.
\vskip 1.4in
\bye
