\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2009, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook. No digital or communications devices.
All questions 4 points.

\ques
% Project 24
Give the steps you would take on {\ltt{}puma} to install and use
a new {\ltt{}/etc/http/httpd.conf} file on {\ltt{}lab88}.
You will perform the install from a file called {\ltt{}newhttpconf}
located on {\ltt{}puma}.
To activate the change you will need to issue the command
{\ltt{}/etc/rc.d/rc.httpd restart} on {\ltt{}lab88}.
Include file names and contents.
\vskip 2.4in
\ques
% Project 15
You wish to record information about ftp transfers
(level {\ltt{}notice} and above, facility {\ltt{}ftp}) in
the file {\ltt{}/var/log/xferlog}.
Give the name of the file you need to modify and the line you need to
add to that file.
\vskip 1.0in
\ques
% Project 14
You want to make your directory 
{\ltt{}/newdisk}
available (read write) to {\ltt{}jaguar}.
What file do you need to change?
What addition do you need to make?
\vskip 1.2in
\ques
% Project 25
You want to make a directory called {\ltt{}/newdisk} on your
Linux machine available to all machines running Microsoft Windows as
{\ltt{}NewDiskShare}.
What file do you need to change?
What do you need to add to that file?
\vskip 1.2in
\vfill\eject
\ques
% Project 17
When you ran the setup script to do the install,
what were the major steps it performed?
(Hint: they were on the top level menu.)
\vskip 1.8in
\ques
% Project 18
What is the purpose of the {\ltt{}ftpusers} file?
\vskip 1.0in
\ques
% Project 15
You want print to {\ltt{}cheetah} to the printer cheetah calls {\ltt{}cecs1}.
What file do you need to modify?
What do you need to add to that file?
\vskip 1.2in
\ques
% Project 21
You wish to allow {\ltt{}panther} to use the {\ltt{}innd} on your machine
to post news.
What file do you need to change and what change to you need to make?
\vskip 1.2in
\ques
% Project 21
On your lab machine, you wish to exchange news with {\ltt{}cougar}
(in addition to {\ltt{}jaguar}).
Give the names of the files you will need to change and lines you
will have to add to each of those files.
\vskip 2.2in
\vfill\eject
\ques
% Project 14
You wish to attach the files the
{\ltt{}/hdb/disk1} directory on {\ltt{}jaguar.net.cecs.csulb.edu}
to your file tree as {\ltt{}/mnt}.
Give the {\ltt{}fstab} entry to do this.
\vskip 0.5in
\ques
% Project 26
When the machine {\ltt{}00:01:AC:B2:34:22} boots from the network
it is to be assigned the name {\ltt{}lab88} and the IP address
{\ltt{}134.139.248.88}.
What entry must be in what file for this to happen?
\vskip 1.8in
\ques
% Project 22
You wish to allow the use of {\ltt{}.htaccess} files in all directories
in {\ltt{}/home} except for {\ltt{}/home/students}?
What file do you need to change and what do you need to add to that file.
\vskip 2.8in
\ques
% Project 22
Given the {\ltt{}.htaccess} file that would be needed to require an
account name and password for the directory {\ltt{}/home/sue/public_html}.
The password file should be in the same directory.
\vskip 2.4in
\vfill\eject
\ques
% Project 13
You wish to begin using NIS for groups, password and shadow.
Your NIS server is {\ltt{}panther}, your NIS domain name is {\ltt{}net88}.
What files do you need to change and what changes do you need to make?
\vskip 1.8in
\ques
% Project 20
Describe how an suid program works.
\vskip 1.2in
\ques
% Project 18
You want to present the message found in the {\ltt{}message.txt} file
when a users who is using anonymous ftp logs in.
What file do you need to modify?
\vskip 0.8in
\ques
% Project 19
You want to put all your mail with the word {\ltt{}sale} in the
body into a file called {\ltt{}junk} in your home directory.
What file do you need to create and what does that file need to contain?
\vskip 1.6in
\vfill\eject
\ques
% Project 16
What tool would you use to find out what has been installed on your machine?
\vskip 0.7in
\ques
% Project 20
You want {\ltt{}bob} and {\ltt{}sue} (and no one else) to be able to {\ltt{}su}
to {\ltt{}root}.
What files do you need to change?
What changes to you need to make?
\vskip 1.6in
\ques
% Project 23
There are two machines for which {\ltt{}lab88.net} ({\ltt{}134.139.248.88})
supplies name service:
{\ltt{}a.soup.org} ({\ltt{}129.88.1.1}) and 
{\ltt{}b.soup.org} ({\ltt{}129.88.1.2}).
Give the entire reverse zone file for the zone {\ltt{}1.41.129.in-addr.arpa}.
\vskip 3.5in
\ques
% Project 23
Give the just the forward entries from the forward zone file for
{\ltt{}soup.org}.
\vskip 1.2in
\vfill\eject
Analysis section. Assume {\ltt{}lab88} is a machine you administer.
For each of the questions on this page
state what things would you check on {\ltt{}lab88}
and for each thing you would check give the command you would use to
perform the check. (If you wish to examine the file you may give the
command as {\ltt{}vi}).

\ques
Ping to {\ltt{}134.139.248.87} works, but ping to {\ltt{}lab87} doesn't.
\vfill
\ques
Anonymous ftp to your machine doesn't work.
Other ftp's do.
\vfill
\ques
When {\ltt{}csa476z1} logs in his files aren't there.
\vfill
\ques
Telnet to {\ltt{}lab87} works, telnet to {\ltt{}lab34} doesn't.
\bye
