\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2009, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open book, open notebook. (All question 8 points, 96 total points possible)
\hfill\break
\ques
% Homework 1
Give a command that will count the number of entries in the {\ltt{}/etc/group}
file.
\vskip 0.4in
How would you find a command that allows you to probe the BIOS?
\vskip 0.4in
Give a command that will print the names of the last 3 files changed in
the {\ltt{}/etc} directory.
\vskip 0.4in
In what {\it directory} would you most likely find
the following:
\hfill\break
A) Information about a server failure:
\vskip 0.3in
B) Information about your CPU:
\vskip 0.3in
\ques
% Homework 10
You want the ({\ltt{}control-B}) key to interrupt ({\ltt{}intr})
a program. Give the exact command to set this up.
\vskip 0.4in
Give the exact command (or commands) to extract
{\ltt{}/mntpysqlite-2.3.3.tgz} into {\ltt{}/usr/local/src}.
\vskip 1.0in
\ques
% Homework 9
What are the steps to {\it install} a new kernel?
Assume it has already been built and this is your third try at a new
kernel ({\ltt{}bzImage}) that works. (The other two tries booted, but
were bigger than you wanted.)
\vskip 1.5in
You  want your machine to wait (forever) until you select which kernel
you want to boot. Give the file name and
change to that file you will need to make.
\vskip 0.8in
\vfill\eject
\ques
% Homework 6
Give a command that would find the amount of swap space currently in use.
\vskip 0.4in
Give the exact command to set up a swap structure in
{\ltt{}/dev/hdc1}.
\vskip 0.4in
\ques
% Homework 11
A machine has internet number {\ltt{}129.195.7.99} and
netmask {\ltt{}255.255.255.240}; give it's cable number and broadcast address.
\vskip 1.0in
You want to use DNS (which has never been set up on your machine before).
Your DNS server will be {\ltt{}129.195.7.1} and you wish to do the DNS
look up after any lookups in local files.
Give the two files you will need to change and the new lines for each file.
\vskip 0.8in
How do you find out the address of your ethernet card?
(Give a command.)
\vskip 0.4in
\ques
% Homework 12
Your IP number is {\ltt{}129.195.7.99} and netmask is {\ltt{}255.255.255.240};
give the exact {\ltt{}ifconfig} command you need.
\vskip 0.4in
Your default (and only) gateway is {\ltt{}129.195.7.81};
give the exact {\ltt{}route} command you need.
\vskip 0.4in
You wish to completely disable the ability of other machines to 
access the {\ltt{}daytime} capability of your machine.
Give file name and modification to do this.
\vskip 0.8in
You wish do allow {\ltt{}comsat} to be accessed only from
{\ltt{}panther.net.cecs.csulb.edu}.
Give file names and modifications to do this.
\vskip 1.4in
\vfill\eject
\ques
% Homework 4
Write a script that prints information about all {\ltt{}a.out} processes
running in the system.
\vskip 1.5in
\ques
% Homework 5
What command would you use to run a file system check on
{\ltt{}/dev/hdc2}?
\vskip 0.4in
Give the exact command to build a Linux file ext2 system on the
{\ltt{}/dev/hdc2}.
\vskip 0.4in
Give the mount command to attach the file system
on {\ltt{}/dev/hdc2} at {\ltt{}/mnt}.
\vskip 0.4in
\ques
% Homework 7
You want everyone to use the GUI to login (run level 6).
What file do you need to change?
\vskip 0.4in
You want to shut down your web service ({\ltt{}killall -TERM httpd})
at 1:30am.
Describe how to do this; give exact name of your script file, the file contents
and command.
\vskip 1.7in
You wish to backup your {\ltt{}/u3} directory to {\ltt{}/bkup/u3.tgz}
every morning at 1:00am. 
\vskip 1.4in
\vfill\eject
\ques
% Homework 8
What command do you run to find out how much video RAM is available?
\vskip 0.4in
How do you find out the current resolution of your X-windows display?
\vskip 0.4in
What program would you run if you got a new higher resolution monitor?
\vskip 0.4in
\ques
% Homework 3
The user {\ltt{}sue} has  a home directory of {\ltt{}/u3/joe},
a shell of {\ltt{}/bin/tcsh}, a user number of {\ltt{}10101}
and a base group of {\ltt{}111}.
Give the password entry for {\ltt{}joe}.
\vskip 1.0in
\ques
% Homework 2
You want to make {\ltt{}gp} a short-hand for {\ltt{}g++ -lpthreads}.
What modification do you need to make and to what file?
\vskip 1.2in
{\ltt{}joe} needs to be added to both the {\ltt{}faculty} and {\ltt{}users}
groups.
How do you do this?
\vskip 1.2in
Have your shell ({\ltt{}csh}) search {\ltt{}/bin}, {\ltt{}/sbin},
{\ltt{}/usr/bin} and finally {\ltt{}.} for executables.
Give the file name and entry to do this.
\vskip 1.2in
\bye
