\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2010, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, notebook, on-line manual and files.
No communications devices or communication linkes.
All questions 4 points.

\ques
% Project 8
You wish to automatically launch {\ltt{}firefox} whenever you start the
X windows system.
What file needs to exist and what entry needs to be in that file?
\vskip 1.8in
\ques
% Project 20
You wish to write a program called {\ltt{}submit.out} that allows students
to deposit a copy of their homework into your {\ltt{}submitted} directory.
Give the {\ltt{}chmod} command (protections) necessary for both the
program and the directory.
\vskip 1.4in
\ques
% Project 18
You want to present a message found in the {\ltt{}dir_info.txt} file
when a user using anonymous ftp changes into a directory.
What file do you need to modify and what entry do you need to make?
\vskip 1.4in
\ques
% Project 19
You want to put all your mail from any {\ltt{}.biz} site 
into a file called {\ltt{}/dev/null} (i.e., throw it out).
What file do you need to create and what does that file need to contain?
\vskip 1.6in
\vfill\eject
\ques
% Project 24
Give the steps you would take on {\ltt{}cougar} to install and use
a new {\ltt{}/etc/ntp.conf} file on {\ltt{}lab91} using ssl/ssh.
You will perform the install from a file called {\ltt{}newntpconf}
located on {\ltt{}cougar}.
To activate the change you will need to issue the command
{\ltt{}/etc/rc.d/rc.ntpd restart} on {\ltt{}lab91}.
Include file names, contents and command.
\vskip 2.6in
\ques
% Project 15
You wish to record information about cron activities
(level {\ltt{}info} and above, facility {\ltt{}cron}) in
the file {\ltt{}/var/log/cronlog}.
Give the name of the file you need to modify and the line you need to
add to that file.
\vskip 1.0in
\ques
% Project 14
You want to make your directory 
{\ltt{}/mysharedisk}
available (read write) to {\ltt{}puma}.
Give the name of the file you need to modify and the line you need to
add to that file.
\vskip 1.0in
\ques
% Project 25
You want to make a directory called {\ltt{}/myshare} on your
Linux machine available to all machines running Microsoft Windows as
{\ltt{}myshare}.
What file do you need to change?
What lines do you need to add to that file?
\vskip 1.2in
\vfill\eject
\ques
% Project 17
When you ran the setup script to do the install,
you selected several disk sets (themes).
Give the names of {\it two} of these and for each of them
describe their contents in 8 words or less.
\vskip 1.4in
\ques
% Project 18
How do you enable anonymous ftp?
\vskip 0.8in
\ques
% Project 15
You want print to {\ltt{}panther} to the printer panther calls 
{\ltt{}colorlaser}.
What file do you need to modify?
What do you need to add to that file?
\vskip 0.8in
\ques
% Project 21
You wish to add a news group to you news system.
Give the steps, including modifications files, commands and directories.
\vskip 2.0in
\ques
% Project 21
On your lab machine, you wish to exchange news with {\ltt{}panther}
(in addition to {\ltt{}jaguar}).
Give the names of the files you will need to change and lines you
will have to add to each of those files.
\vskip 2.2in
\vfill\eject
\ques
% Project 14
You wish to attach the files the
{\ltt{}/hdb/disk1/slackware} directory on {\ltt{}jaguar.net.cecs.csulb.edu}
to your file tree as {\ltt{}/mnt}.
Give the {\ltt{}fstab} entry to do this.
\vskip 0.5in
\ques
% Project 26
When the machine {\ltt{}00:01:AC:B2:34:22} boots from the network
it is to be assigned the name {\ltt{}lab91} and the IP address
{\ltt{}134.139.248.91} and boot {\ltt{}/tftpboot/pxelinux.0}.
What entries must be in what file for this to happen?
\vskip 1.8in
\ques
% Project 22
Given the {\ltt{}.htaccess} file that would be needed to require an
account name and password for the directory
{\ltt{}/home/sue/public_html/private}.
The password file should be in the same directory and called {\ltt{}.htpasswd}.
\vskip 2.4in
\ques
% Project 22
You have already allowed the use of {\ltt{}.htaccess} files in all directories
in {\ltt{}/home}, however you realize that you have a security problem
and files called {\ltt{}.htpasswd} should not be readable by web browsers.
What file do you need to change and what do you need to add to that file?
\vskip 2.2in
\vfill\eject
\ques
% Project 16
You need to know what packages have been installed on your machine.
What command do you need to run?
\vskip 0.5in
\ques
% Project 20
You want log all {\ltt{}su} activity.
What file do you need to change?
What change to you need to make?
\vskip 1.0in
\ques
% Project 23
There are two machines for which {\ltt{}lab91.net} ({\ltt{}134.139.248.91})
supplies name service:
{\ltt{}a.gnu.org} ({\ltt{}129.91.1.1}) and 
{\ltt{}b.gnu.org} ({\ltt{}129.91.1.2}).
\hfill\break
Give the entire reverse zone file for the zone {\ltt{}1.91.129.in-addr.arpa}.
\vfill
\ques
% Project 23
Give the just the {\ltt{}A} record entries from the forward zone file for
{\ltt{}gnu.org}.
\vskip 1.2in
\eject
Analysis section. Assume {\ltt{}lab91} is a machine you administer.
For each of the questions on this page
state what things would you check on {\ltt{}lab91}
and for each thing you would check give the command you would use to
perform the check. (If you wish to examine the file you may give the
command as {\ltt{}vi}).

\ques
Telnet into your machine isn't working, but other services are.
\vfill
\ques
You've just finished the install and rebooted.
You discover you are off the net, but your net cable is plugged in
and working (link lights are on).
\vfill
\ques
Joe reports his web pages have suddenly disappeared
and you know that {\it you} haven't change any web configurations.
\vfill
\ques
Some student attempts to hack the system at 10:42.
You want to identify the student.
\bye
