\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2010, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open book, open notebook. (All question 8 points, 96 total points possible)
\hfill\break
\ques
% Homework 4
Give a command that will tell you how much disk space is available on
the partition that contains bob's home directory.
\vskip 0.4in
Write a script that tells you which log file was changed last.
\vskip 1.1in
\ques
% Homework 5
What command would you use to run a file system check on
{\ltt{}/dev/hdd1}?
\vskip 0.4in
Give the exact command to build a Linux file ext2 system on the
{\ltt{}/dev/hdd1}.
\vskip 0.4in
Give the {\ltt{}fstab} entry to attach the file system
on {\ltt{}/dev/hdd1} at {\ltt{}/slackware}.
\vskip 0.4in
\ques
% Homework 7
On the printserver in ECS 416 we want the students to be able to
abort a print job by typing {\ltt{}ctl-alt-del}.
What file does the administrator need to change?
\vskip 0.4in
You wish to run {\ltt{}ypxfr} every 15 minutes between 9:00am and
10:00PM (2200).
Give the command and exact file contents used to do this.
\vskip 1.4in
You want to upgrade your {\ltt{}C++} compiler at 3:30am.
You will need to extract {\ltt{}/root/g++.4.2.1.tgz} into
{\ltt{}/usr/local/src}, {\ltt{}cd} into that directory and
run the command {\ltt{}make install}.
Describe how to do this; give exact name of your script file, the file contents
and the command.
\vskip 1.7in
\vfill\eject
\ques
% Homework 1
Give a command that will count the number of mounts.
\vskip 0.4in
How would you find a command that allows you to process a {\ltt{}pic} file?
\vskip 0.4in
Give a command that will print the last 10 lines of the {\ltt{}syslog} file.
\vskip 0.4in
In what {\it directory} would you most likely find
the following:
\hfill\break
A) The addresses being used by the vrious I/O ports:
\vskip 0.3in
B) Configuration file for you {\ltt{}xyzzy} server:
\vskip 0.3in
\ques
% Homework 10
You want the ({\ltt{}control-L}) key to redraw the current line ({\ltt{}rprnt}).
Give the exact command to set this up.
\vskip 0.4in
Give the command to backup {\ltt{}~sue} to {\ltt{}/var/backups/sue.txz}.
\vskip 1.0in
Give the command to encrypt the {\ltt{}Scores} file that is in your
current directory.
\vskip 1.0in
\ques
% Homework 9
Your new kernel doesn't boot. The message says, ``Doesn't have ext4 file
system support".
How do you modify and rebuild the kernel.
(Don't do the boot stuff, just modify and rebuild.)
\vskip 1.5in
You wish to make {\ltt{}bzImage} your default boot.
What file do you need to change and what change do you need to make?
\vskip 0.8in
\vfill\eject
\ques
% Homework 6
Give the exact command to set up a swap structure in {\ltt{}/dev/hdd2}.
\vskip 0.4in
You want to use {\ltt{}/dev/hdd2} as swap space and you want this to
happen everytime you boot.
What file do you need to change and what line needs to be there?
\vskip 0.6in
\ques
% Homework 11
A machine has internet number {\ltt{}144.102.99.171} and
netmask {\ltt{}255.255.255.224}; give it's cable number and broadcast address.
\vskip 1.0in
You want to use DNS (which has never been set up on your machine before).
Your DNS server will be {\ltt{}144.102.99.101} and you wish to do the DNS
look up after any lookups in local files.
Give the two files you will need to change and the new lines for each file.
\vskip 0.8in
How do you find out the address of your ethernet card?
(Give a command.)
\vskip 0.4in
\ques
% Homework 12
Your IP number is {\ltt{}144.102.99.171} and netmask is {\ltt{}255.255.255.240};
give the exact {\ltt{}ifconfig} command you need.
\vskip 0.4in
Your default (and only) gateway is {\ltt{}144.102.99.161};
give the exact {\ltt{}route} command you need.
\vskip 0.4in
You wish do allow {\ltt{}proftp} to be accessed only from
{\ltt{}lynx.net.cecs.csulb.edu}.
Give file names and modifications to do this.
\vskip 1.4in
You wish to completely disable the ability of other machines to 
access the {\ltt{}comsat} capability of your machine.
Give file name and modification to do this.
\vskip 0.8in
\vfill\eject
\ques
% Homework 13
You want to use NIS for password and shadow, but use only the
local file for groups.
Give the file name and lines in that file that would do this.
\vskip 0.6in
You want to use {\ltt{}panther} ({\ltt{}134.139.248.21}) as your
NIS (yp) server.
Give the file name and contents to do this.
\vskip 0.6in
How would you check to see if the information for the {\ltt{}joe} account
was being deliver to your machine by NIS.
\vskip 0.4in
\ques
% Homework 3
The user {\ltt{}george} has  a home directory of {\ltt{}/u3/george},
a shell of {\ltt{}/bin/bash}, a user number of {\ltt{}4321}
and a base group of {\ltt{}321}.
Give the password entry for {\ltt{}george}.
\vskip 0.4in
What other steps to you need to do if you are setting up the
account for {\ltt{}george}?
\vskip 1.2in
\ques
% Homework 2
You want to make {\ltt{}delbin} a short-hand for {\ltt{}rm *.out}.
What modification do you need to make and to what file?
\vskip 0.9in
You wish to create the group called {\ltt{}micromouse} as group
number {\ltt{}234}.
What modification do you need to make and to what file?
\vskip 0.9in
As the administrator you are frequently using the commands found
in the directory {\ltt{}/usr/lib/yp}.
You are tired having to {\ltt{}cd} to that directory everytime
you want to run a command.
What modification do you need to make and to what file?
\vskip 1.0in
\bye
