\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2011, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, notebook, on-line manual and files.
No communications devices or communication linkes.
All questions 4 points.

\ques
% Project 17
Give the principal steps (i.e. no more than 5)
in installing a new Linux system.
\vskip 1.8in
\ques
% Project 15
You want the default printer for your machine to be the printer
called {\ltt{}x1} that is attached to the machine {\ltt{}puma}.
What file do you need to modify?
What do you need to add to that file?
\vskip 1.0in
\ques
% Project 21
You wish to set quotas on {\ltt{}/dev/sdb1} (which you mounted
as {\ltt{}/newdisk} in an ancient homework.)
Give the steps.
\vskip 2.3in
\ques
% Project 21
If qoutas are set up, how would you set a quota for {\ltt{}bob}.
Give the exact command and describe what you when you ran that command.
\vskip 1.8in
\vfill\eject
\ques
% Project 8
You wish to automatically launch {\ltt{}/usr/bin/thunderbird} at the lower left
of the screen whenever you start the X windows system.
What file needs to exist and what entry needs to be in that file?
\vskip 1.0in
\ques
% Project 18
What does the {\ltt{}ftpusers} file do?
\vskip 0.7in
\ques
% Project 20
How do you cause a program to be SUID?
\vskip 1.6in
\ques
% Project 18
How would you find out what libraries gcc depends on?
Give the exact command.
\vskip 0.8in
\ques
% Project 25
You want to make a directory called {\ltt{}/apps} on your
Linux machine available to all machines running Microsoft Windows as
{\ltt{}myshare}.
What file do you need to change?
What lines do you need to add to that file?
\vskip 1.2in
\vfill\eject
\ques
% Project 24
Give the steps you would take on {\ltt{}puma} to install and use
a new {\ltt{}/etc/dhcpd.conf} file on {\ltt{}lab90}.
You will perform the install from a file called {\ltt{}newdhcp}
located on {\ltt{}puma}.
To activate the change you will need to issue the command
{\ltt{}/etc/rc.d/rc.inet1 restart} on {\ltt{}lab90}.
Include file names, contents and command.
\vskip 2.6in
\ques
% Project 15
You wish to record information
from one of your an application
in the file {\ltt{}/var/log/our_app}.
The application logs to facility {\ltt{}local3}).
You should record all levels.
Give the name of the file you need to modify and the line you need to
add to that file.
\vskip 1.4in
\ques
% Project 14
You want to make your a 
{\ltt{}/d1}
available to all machines on the
{\ltt{}134.139.248.0/255.255.255.0} subnets.
Give the name of the file you need to modify and the line you need to
add to that file.
\vskip 1.2in
\ques
% Project 19
You want to put all your mail containing the word ``Homework" (in the body)
to go into a file called {\ltt{}/home/instructor/homework}.
What file do you need to create and what does that file need to contain?
\vskip 1.6in
\vfill\eject
\ques
% Project 14
You wish to mount the files from the
{\ltt{}/sdb/slack13.1} directory on {\ltt{}jaguar.net.cecs.csulb.edu}
to your file tree as {\ltt{}/mnt}.
Give the {\ltt{}fstab} entry to do this.
\vskip 0.5in
\ques
% Project 26
When the machine {\ltt{}00:01:02:CE:03:62} boots from the network
it is to be assigned the name {\ltt{}lab90} and the IP address
{\ltt{}134.139.248.19} and boot {\ltt{}/tftpboot/pxelinux.0}.
What entries must be in what file for this to happen?
\vskip 2.0in
\ques
% Project 22
How would you require a password for web access to files in
{\ltt{}/var/www/private}.
\vskip 2.0in
\ques
% Project 22
Assume you have enabled {\ltt{}cgi} (added the handler).
You want to allow {\ltt{}cgi} files to be run in the directories
{\ltt{}/d1/u2/*}.
What file do you need to change and what do you need to add to that file?
\vskip 2.2in
\vfill\eject
\ques
% Project 16
What is PXE?
\vskip 0.8in
\ques
% Project 20
You want to activate an inactivity timeout.
What file do you need to change?
\vskip 0.7in
\ques
% Project 23
There are two machines for which {\ltt{}dns99.net} ({\ltt{}134.139.248.99})
supplies name service:
{\ltt{}acme.com} ({\ltt{}10.10.1.14}) and 
{\ltt{}acme.com} ({\ltt{}10.10.1.15}).
Give the entire forward zone file for the zone.
\vfill
\ques
% Project 23
Give the just the {\ltt{}PTR} record entries from the reverse zone file for
{\ltt{}134.139.248}.
\vskip 1.2in
\eject
Analysis section. Assume {\ltt{}lab90} is a machine you administer.
For each of the questions on this page
state what things would you check on {\ltt{}lab90}
and for each thing you would check give the command you would use to
perform the check. (If you wish to examine the file you may give the
command as {\ltt{}vi}).

\ques
Sam complains that halfway through programming his homework
he began getting the message ``unable to save file" from the editor.
\vfill
\ques
You've just installed a new version of Linux and
Sam complains that his home directory isn't there.
\vfill
\ques
Someone rebooted your machine last night.
How would you identify the person you would most likely
need to talk to?
\vfill
\ques
Sam complains he can't {\ltt{}telnet} into his account
but he can {\ltt{}ssh}.
\bye
