\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2011, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open book, open notebook. (All question 8 points, 96 total points possible)
\hfill\break
\ques
% Homework 4
Give a command that will reveal the file system types of
the partitions containing directories in use.
\vskip 0.4in
Write a script that tells how many {\ltt{}httpd} processes are running.
\vskip 1.1in
\ques
% Homework 10
You want the ({\ltt{}control-Y}) key to send a quit signal
the currently running process line ({\ltt{}quit}).
Give the exact command to set this up.
\vskip 0.4in
Give the command to backup {\ltt{}/u1} into {\ltt{}/u1bu/u1.txz}.
\vskip 0.4in
Give the command to decrypt the {\ltt{}demo.cr} file.
\vskip 0.4in
\ques
% Homework 7
You wish to use the GUI to login. To do this you must have the
machine go to runlevel 4 when it boots.
What file does the administrator need to change?
\vskip 0.4in
You wish to run {\ltt{}reboot} every Saturday morning at 1:00am.
Give the exact crontab entry to do this.
\vskip 1.4in
You want to upgrade your web server at 3:30am.
You will need to run the untar {\ltt{}/root/httpd.tgz} into
{\ltt{}/}, then {\ltt{}cd} into the {\ltt{}/install} directory and
run the command {\ltt{}source doinst.sh}.
Describe how to do this; give exact name of your script file, the file contents
and the command to activate the script at the specified time.
\vskip 1.7in
\vfill\eject
\ques
% Homework 5
Give the exact command to build a Linux file ext2 system on the
{\ltt{}/dev/sdd2}.
\vskip 0.4in
What command would you use to run a file system check on
{\ltt{}/dev/sdd2}?
\vskip 0.4in
Give the {\ltt{}fstab} entry to attach the file system
on {\ltt{}/dev/sdd2} at {\ltt{}/mnt}.
\vskip 0.4in
\ques
% Homework 1
How would you find a command that allows you to compile a fortran program?
\vskip 0.4in
Give a command that will tell you how many groups are listed in the local
{\ltt{}group} file.
\vskip 0.4in
Give a command that will print the last 5 files changed in the {\ltt{}/etc}
directory.
\vskip 0.4in
In what {\it directory} would you most likely find
the following:
\hfill\break
A) Configuration file(s) for the web server:
\vskip 0.3in
B) Information about interrupts:
\vskip 0.3in
\ques
% Homework 9
Give the steps to modify and rebuild the kernel.
(Don't do the boot stuff, just modify and rebuild.)
\vskip 1.5in
You wish create a full dual boot system.
The second boot will be to {\ltt{}/dev/sdb2}. That drive will contain a 
full copy of the operating system and a kernel called {\ltt{}/boot/vmlinuz}.
What file do you need to modify and what addition do you need to make?
\vskip 0.8in
\vfill\eject
\ques
% Homework 6
Give the exact command to set up a swap structure in {\ltt{}/dev/sdd1}.
\vskip 0.4in
Give the fstab entry to activate {\ltt{}/dev/sdd1} as swap space on boot.
\vskip 0.6in
\ques
% Homework 11
A machine has internet number {\ltt{}137.99.22.219} and
netmask {\ltt{}255.255.255.192}; give it's cable number and broadcast address.
\vskip 1.0in
You want to use DNS (which has never been set up on your machine before).
Your DNS server will be {\ltt{}137.99.22.101} and you wish to do the DNS
look up after any lookups in local files.
Give the two files you will need to change and the new lines for each file.
\vskip 0.8in
Give a command that would allow you to find out how many subnets your
computer is connected to.
\vskip 0.4in
\ques
% Homework 12
Your IP number is {\ltt{}137.99.22.78} and netmask is {\ltt{}255.255.255.224};
give the exact {\ltt{}ifconfig} command you need.
\vskip 0.4in
Your default (and only) gateway is {\ltt{}137.99.22.71};
give the exact {\ltt{}route} command you need.
\vskip 0.4in
You wish do allow {\ltt{}imapd} to be accessed only from
{\ltt{}cougar.net.cecs.csulb.edu}.
Give file names and modifications to do this.
\vskip 1.4in
You wish to completely disable the ability of other machines to 
access the {\ltt{}ftp} capability of your machine.
Give file name and modification to do this.
\vskip 0.8in
\vfill\eject
\ques
% Homework 13
You want to use NIS for groups, but use only the
local file for password and shadow.
Give the file name and lines in that file that would do this.
\vskip 0.6in
You want to use {\ltt{}lynx} ({\ltt{}134.139.248.22}) as your
NIS (yp) server.
Give the file name and contents to do this.
\vskip 0.6in
How would you check to see if the information for the {\ltt{}group} file
was being deliver to your machine by NIS.
\vskip 0.4in
\ques
% Homework 3
The user {\ltt{}sam} has  a home directory of {\ltt{}/net/d1/u3/sam},
a shell of {\ltt{}/bin/tcsh}, a user number of {\ltt{}5678}
and a base group of {\ltt{}42}.
Give the password entry for {\ltt{}sam}.
\vskip 0.4in
What other steps to you need to do if you are setting up the
account for {\ltt{}sam}?
\vskip 1.2in
\ques
% Homework 2
You want to make {\ltt{}ph} a short-hand for {\ltt{}ps aux | grep http}.
What modification do you need to make and to what file?
\vskip 0.9in
Why does the administrator ({\ltt{}root}) need to type {\ltt{}./a.out}
to run a program, while {\ltt{}bob} only has to type {\ltt{}a.out}?
\vskip 1.0in
You need to know the group number for the group called {\ltt{}audio}.
Give a command that pulls the (correct single) line out of the correct file
to give you that information.
\vskip 0.9in
\bye
