\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2012, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, notebook, on-line manual and files.
No communications devices or communication linkes.
All questions 4 points.

\ques
% Project 13
Your wish to begin using NIS for groups, password and shadow.
Your NIS server is {\ltt{}puma}, your NIS domain name is {\ltt{}t476}.
What files do you need to change and what changes do you need to make?
\vskip 1.8in
\ques
% Project 14
You want to make your directory
{\ltt{}/home}
available to panther (read only) and lynx (read write).
Give the name of the file you need to modify and the line you need to
add to that file.
\vskip 1.2in
\ques
% Project 14
You wish to mount the files from the
{\ltt{}/home} directory on {\ltt{}jaguar.net.cecs.csulb.edu}
to your file tree as {\ltt{}/auto} (assume the directory exists) read write,
using the automounter.
Give the {\ltt{}auto.master} line and the indirect file (indicate the file name)
needed to do this.
\vskip 1.2in
\ques
% Project 21
You want to disable access to the personal web page of the
user {\ltt{}sue}.
What file do you need to change and what do you need to add to that file?
\vskip 2.2in
\vfill\eject
\ques
% Project 16
What is {\ltt{}pkgtool}?
\vskip 0.9in
\ques
% Project 17
What is a package series and which ones did you select?
\vskip 1.2in
\ques
% Project 18
You wish to record information
from an application
in the file {\ltt{}/var/log/printer_errors}.
The application logs to facility {\ltt{}lpr}.
You should record log level {\ltt{}err} and above.
Give the name of the file you need to modify and the line you need to
add to that file.
\vskip 1.4in
\ques
% Project 18
You want the default (and only) printer for your machine to be the printer
called {\ltt{}laser} that is attached to the machine {\ltt{}lynx}.
What should that file contain?
What do you need to add to that file?
\vskip 1.0in
\ques
% Project 19
You want to put all mail to {\ltt{}bob} from {\ltt{}volper}
into a file called {\ltt{}/home/bob/teacher_msgs}.
What file do you need to create and what does that file need to contain?
\vskip 1.8in
\vfill\eject
\ques
% Project 19
You wish to configure mail to use an antivirus filter.
What file do you need to modify?
What commands do you need to run to install and activate that change?
(Do not give the modification.)
\vskip 1.2in
\ques
% Project 20
How is special about an SUID program?
\vskip 1.5in
\ques
% Project 22
There are two machines for which {\ltt{}dns1.intenet.com} ({\ltt{}216.209.44.1})
supplies name service:
{\ltt{}b.syr.com} ({\ltt{}216.184.1.14}) and 
{\ltt{}s.syr.com} ({\ltt{}216.184.1.15}).
Give the entire reverse zone file for {\ltt{}216.184.1}.
\vskip 2.2in
\vfill
\ques
% Project 22
Give the just the {\ltt{}A} entries for the zone file for {\ltt{}syrup.com}.
\vskip 1.2in
\eject
\ques
% Project 20
You limit the times at which users can login.
What file do you need to change?
\vskip 0.6in
\ques
% Project 21
How would you require a password for web access to files in
{\ltt{}/var/www/private}?
\vskip 2.0in
\ques
% Project 23
Give the steps you would take on {\ltt{}jaguar} to install and use
a new {\ltt{}/etc/httpd/httpd.conf} file on {\ltt{}lab13}.
You will perform the install from a file called {\ltt{}newhttpd}
located on {\ltt{}jaguar}.
To activate the change you will need to issue the command
{\ltt{}/etc/rc.d/rc.httpd restart} on {\ltt{}lab13}.
Include file names, contents and command.
\vskip 2.6in
\ques
% Project 24
You want to make a directory called {\ltt{}/etc} on your
Linux machine available to all machines running Microsoft Windows as
{\ltt{}etcstuff}.
What file do you need to change?
What lines do you need to add to that file?
\vskip 1.2in
\vfill\eject
\ques
% Project 15
How does anonymous ftp restrict what can be seen?
\vskip 1.0in
\ques
% Project 15
What is static vs dynamic linking?
\vskip 1.0in
\ques
% Project 25
You wish to set user quotas on {\ltt{}/dev/sdb2} (which you mounted
as {\ltt{}/newdisk} in an ancient homework).
Set a quota for {\ltt{}sam} (1 MB).
Give the steps.
\vskip 3.0in
\ques
% Project 26
When the machine {\ltt{}01:02:03:04:05:06} boots from the network
it is to be assigned the name {\ltt{}lab13} and the IP address
{\ltt{}134.139.248.13} and boot {\ltt{}/tftpboot/pxelinux.0}.
What entries must be in what file for this to happen?
\vskip 2.0in
\vfill\eject
Analysis section. Assume {\ltt{}lab90} is a machine you administer.
For each of the questions on this page
state what things would you check on {\ltt{}lab90}
and for each thing you would check give the command you would use to
perform the check. (If you wish to examine the file you may give the
command as {\ltt{}vi}).

\ques
Ping to 134.139.248.13 works, but ping go lab13 doesn't.
\vfill
\ques
Some student attempted to hack the system at 2:13AM.
You want to identify the student.
\vfill
\ques
After a new install (assignment 17)
the user {\ltt{}csa476z1} reports he can't log in.
\vfill
\ques
After a new install (assignment 17)
the user {\ltt{}sam} complains he can't {\ltt{}rlogin} into his account
but he can {\ltt{}ssh}.
\bye
