\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2013, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open book, open notes, access to your the machine you administer.
(All question 8 points, 96 total points possible)
\hfill\break
\ques
% Homework 9
The user {\ltt{}sue} wishes to set her background to {\ltt{}solid blue}
regardless of which window manager she chooses to use.
Give the file and the line she needs to add to that file.
\vskip 0.6in
When any user chooses the {\ltt{}twm} window 
manager you wish modify the default configuration for that window manager
to use {\ltt{}Shift-left-click} to change the background color.
What file would you need to change? (Give the full path.)
(Just give the file name, you don't need to give the change.)
\vskip 0.4in
What link controls the selection of a default window manager for
all users on the system? (Of course users can override this.)
\vskip 0.4in
\ques
% Homework 1
Give the names of two stream editors that are available on your machine.
Also give the command(s) you used to find out this information.
\vskip 0.8in
Give the full command (with arguments) that will tell you which libraries have
been {\it recently} installed on your system.
\vskip 0.4in
In what {\it directory} would you {\it most likely} find
the following:
\hfill\break
A) What IO ports on your system were found by the kernel:
\vskip 0.3in
B) Log file for the mysql database:
\vskip 0.3in
\ques
% Homework 8
What command would you use to build a new kernel (assuming you have
already modified the configuration file).
\vskip 0.4in
In the main labs we boot the {\ltt{}/boot/vmlinuz} kernel with
from the boot sector on {\ltt{}/dev/sda} with {\ltt{}/dev/sda1}
as the root partition.
Give a minimal {\ltt{}lilo.conf} file to do this.
(Note: you are not allowed to access those machines to answer this question.
\vskip 1.4in
\vfill\eject
\ques
% Homework 6
You have an {\ltt{}/dev/sdc1} swap partion you wish to use. to
Give the commands to place the swap structure into parttion and to activate
the swapping on the partition by hand (don't use {\ltt{}fstab}).
\vskip 1.0in
Give the exact command (with options) to list all processes being run from
{\ltt{}/dev/tty1}. (You are expected to do a manual lookup for the options.)
\vskip 0.4in
\ques
% Homework 11
A machine has internet number {\ltt{}128.139.35.122} and
netmask {\ltt{}255.255.255.252}; give it's subnet/cable number and subnet
broadcast address.
\vskip 1.0in
For looking up host names/numbers you wish to use your the information
in you {\ltt{}/etc/hosts} before you attempt to use DNS.
Give the name of the file you need to modify and the new value of the
entry that you need to change in that file.
\vskip 0.6in
You want your DNS server to be {\ltt{}142.15.22.99}.
Give the file name and the entry to do this.
\vskip 0.4in
\ques
% Homework 12
Your IP number is {\ltt{}128.139.35.122} and netmask is {\ltt{}255.255.255.252};
give the exact command to configure your (only) network interface.
\vskip 0.4in
Your default (and only) gateway is {\ltt{}128.139.35.121};
give the exact command to configure your machine to use this gateway.
\vskip 0.4in
You wish to enable {\ltt{}finger}.
Give name of the file and the exact line that needs to be uncommented.
(Hint: look in the file on your machine and find the line.)
\vskip 0.4in
You wish do allow {\ltt{}finger} to be accessed only from
{\ltt{}panther.net.cecs.csulb.edu}.
Give file names and modifications to do this.
\vskip 1.4in
\vfill\eject
\ques
% Homework 5
You have an {\ltt{}/dev/sdc2} Linux native partion you wish to add to
your machine as the {\ltt{}/disk2}. 
Give the exact command to build a Linux file ext2 system on that partition,
the command to make the mount point available and the
{\ltt{}fstab} entry to that partition automatically mount at boot time.
\vskip 1.3in
\ques
% Homework 7
You wish permanently run the X11 window system, even for login's.
This means you need to start X11 at boot time.
To do this you will need to modify the default runlevel.
Give the name of the file you need to modify and the modification (one line)
you will need to make to that file
(Hint: Look at that file on your machine to find the line.)
\vskip 0.6in
You need to reboot one of your servers to use a new Linux kernel.
(You have already installed the kernel and modified the {\ltt{}lilo.conf};
all you need is the reboot.)
However because classes are in you want the reboot to happen at 2:00am.
Give the command you would run and the contents of any file associated with
that command.
\vskip 0.6in
You want to get a new copy of your system's default window manager file
({\ltt{}/etc/X11/xinit/xinitrc.fvwm2}) from 
{\ltt{}/net/cheetah/u4/backups/xinitrc.fvwm2}
once a week (Saturday 2:00am)
Explain how you would do this. Give the command(s) and details.
\vskip 0.8in
\ques
% Homework 2
A user wants to change their default umask (whatever that is).
What files could the user edit to do this?
\vskip 0.9in
You are using the database a lot and are tired of typing
{\ltt{}/usr/local/share/} in front of all the database commands.
What file would you need to change and what change would you need
to make?
\vskip 1.0in
You need to add a group to your local machine for the xyzzy project,
the number of this new group should be 4321.
What file do you need to modify and what line to you need to add?
\vskip 0.9in
\vfill\eject
\ques
% Homework 10
You want {\ltt{}control-y} to be the key that interrupts ({\ltt{}intr})
a program.
Give the command to do this.
\vskip 0.4in
Give the command to backup /home to a file called {\ltt{}/backups/homes.tgz}.
\vskip 0.4in
Give the command to decrypt the {\ltt{}exam.cr} file.
\vskip 0.4in
\ques
% Homework 3
The user {\ltt{}sam} has  a home directory of {\ltt{}/home/sam},
a shell of {\ltt{}/bin/bash}, a user number of {\ltt{}4321}
and a base group of {\ltt{}2222}.
Give the password and shadow entries for {\ltt{}sam}.
\vskip 0.8in
Who should own {\ltt{}/home/sam} and it's contents?
\vskip 0.4in
\ques
% Homework 4
Give a command that would list your disks and their partitions?
\vskip 0.4in
Write a script that will list all files (not directories) in {\ltt{}/etc} 
that have modification dates newer than the file {\ltt{}/timestamp}.
\vskip 1.1in
\bye
