\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2001, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook.

\ques
(4 points)
% Project 18
Your directory {\ltt{}/home/ftp/pub} has a mode ({\ltt{}chmod}) of 777.
What does this mean? What does this allow users to do (and which users)?
\vskip 2.0in
\ques
(4 points)
% Project 18
What is the difference between a static and a dynamic library.
What command would you use to determine if a program
accessed dynamic libraries.
\vskip 1.0in
\ques
(4 points)
% Project 19
Your want all mail (except for the {\ltt{}root} and {\ltt{}bob}
accounts) to be forwarded {\ltt{}jaguar.cecs.edu}.
(Hint: You macro letter is {\ltt{}H} and your and
your class letter is {\ltt{}L}.)
What file would you modify and what change would you make to that file?
\vskip 1.2in
\ques
(4 points)
% Project 20
You have a C program (called {\ltt{}getgrade}) already build and compiled.
This program will allow a user to look only at their line in the
grade sheet {\ltt{}grades.txt} for the class.
Of course, the grade sheet needs to be protected so it is not readable.
What do you need to to to make this program work.
Give the protections you need and give the exact commands to
set up those protections for both the above files.
\vskip 1.0in
\ques
(4 points)
% Project 21
You wish to allow users from {\ltt{}lynx} and {\ltt{}jaguar} to
read news using your machine as a server.
What do you need to do? (Give file(s) and modifications.)
\vskip 0.8in
\vfill\eject
\ques
(4 points)
% Project 21
You want your machine to transfer (feed) news articles to {\ltt{}cheetah}.
What do you need to do?
(Give file(s) and modifications.)
Also give the command that you (as the news administrator) could used to 
transfer the news.
\vskip 1.9in
\ques
(4 points)
% Project 22
Suppose you have www configured and running. You are to make a
modification so that {\ltt{}/etc} is not accessible
via the web, but {\ltt{}/etc/public} is accessible.
What do you need to do? (Give file(s) and modifications.)
\vskip 1.5in
% \vfill\eject
\ques
(4 points)
% Project 23
You have two machines for which you supply name service.
{\ltt{}lab1.lbcc.edu} (201.1.4.2) and 
{\ltt{}server1.lbcc.edu} (201.1.4.3).
Give the zone entries (only zone entries) of the {\ltt{}named.conf}
for your DNS server.
\vfill
\eject
\ques
(4 points)
% Project 23
Give the reverse zone file for the previous question. (Include the SOA).
\vskip 2.8in
\ques
(4 points)
% Project 24
You wish to allow user {\ltt{}bob} on {\ltt{}cheetah.cecs.csulb.edu}
to put files onto your ftp area (user {\ltt{}ftp}) on 
your machine ({\ltt{}lab99.net.cecs.csulb.edu}).
What do you do?
(Give file(s) and contents.)
\vskip 1.0in
\ques
(4 points)
% Project 24
User {\ltt{}bob} wishes to put a program (file) called 
{\ltt{}stuff.tar} from his home directory into {\ltt{}~ftp/pub}
call it {\ltt{}version2.tar} and change its permissions to
be {\ltt{}644}.
What does {\ltt{}bob} do? (Give files, contents and command.)
\vskip 1.6in
\ques
(4 points)
% Project 25
You want Windows NT users to be able to access their home directories
(if they have an account).
What special section needs to be set up and what sort
of security do you need?
(Assume the appropriate software is already installed.)
What do you need to do?
\vskip 1.3in
\vfill\eject
\ques
(4 points)
% Project 13
You want to list the accounts that are being delivered to your machine
by NIS. Give the exact command to do this.
\vskip 1.8in
\ques
(4 points)
% Project 13
What does the file {\ltt{}nsswitch.conf} allow you to do.
Include a discussion of what the {\ltt{}compat} mode does.
\vskip 1.0in
\ques
(4 points)
% Project 14
Describe how you would
export the {\ltt{}/homes} directory on your machine to all
machines on the 134.139.136.0 cable, read/write
and to machines on the 134.139.45.0 cable, read only?
(Give the file name(s) and contents.)
\vskip 1.2in
\ques
(4 points)
% Project 14
Describe how you have the
the {\ltt{}/etc} directory from {\ltt{}jaguar.cecs.csulb.edu}
automatically mounted when your machine boots.
(Give the file name(s) and contents.)
\vskip 1.2in
\ques
(4 points)
% Project 15
How would you make two printers available to users on your machine.
One printer is called {\ltt{}laser} and is on {\ltt{}cougar}
the other is called {\ltt{}apple} and is on {\ltt{}cheetah}.
The printer on {\ltt{}cheetah} should be the default.
(Give the file name(s) and contents.)
\vskip 1.0in
\vfill\eject
\ques
(4 points)
% Project 15
Describe how you would have
notice ({\ltt{}notice}) messages (or higher) from the cron daemon 
({\ltt{}cron})
go into the file {\ltt{}/var/log/cron}
and
critical ({\ltt{}crit}) (only, no higher or lower)
messages from printer system ({\ltt{}lpr}) be sent to {\ltt{}cheetah}.
(Give the file name(s) and contents.)
\vskip 1.5in
\ques
(4 points)
% Project 16
You want to load Linux from an aztec CD drive onto an SCSI harddrive.
You need a special (1.44M) floppy.
(a) Which special floppy do you need (boot or root)?
(b) You need an image to {\ltt{}dd} onto that floppy, where would you
look to find out the name of the image you need (give directory
and filename)?
\vskip 1.3in
\ques
(4 points)
% Project 17
Your third partition on your main driver {\ltt{}hda3} is
DOS and needs to be changed to linux native.
What command do you give and exactly what do you type when
running that command.
\vskip 2.7in
\ques
(4 points)
% Project 17
When installing the operating system, 
you want to install the compilers and debuggers on your machine.
Which disk set do you need?
\vskip 0.5in
\ques
(4 points)
% Project 17
You installed the smb server software but disabled it.
What command did you run to disable this software?
\vskip 0.5in
\vfill\eject
Analysis section. 

\ques
(4 points)
Suppose the following work:

{\program
 ping 134.139.136.65
 ping 134.139.45.6
 ping 128.192.4.53
\endprogram}

and the following fails:

{\program
 ping 134.139.136.85
\endprogram}

What could be misconfigured on your machine?
\vfill
\ques
(4 points)
Assume all the above pings work and when a user logs into your
machine they get a message ``{\ltt{}no home directory using /}".
What could be misconfigured on your machine?
\vfill
\ques
(4 points)
Assume the pings and the home directories work.
Suppose that all user home pages except for {\ltt{}bob} can be accessed.
What could be misconfigured on the machine?
Assuming {\ltt{}bob} doesn't have root priviledges,
what could bob have done to cause this?
\bye
