\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2004, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook. No digital or communitcations devices.
All questions 4 points.

\ques
% Project 22
Explain how you would allow http access to nothing in
{\ltt{}/home} except things under {\ltt{}/home/httpusers}.
Give the file name and contents.
\vskip 2.8in
\ques
% Project 22
On your machine, where does the user need to place html files,
and what entry from what file makes this so?
\vskip 1.0in
\ques
% Project 16
How do you disable http (temporarily) after doing an install?
\vskip 0.8in
\ques
% Project 17
For a blank harddrive,
give the sequence of {\ltt{}fdisk} commands to
set {\ltt{}hdb1} (cylinders 0-100)
to be a Linux swap partition
and {\ltt{}hdb2} (cylinders 101-1500)
to be a bootable (active) Linux native (ext2) partition.
%\vskip 3.0in
\vfill\eject
\ques
% Project 17
In what order are the following performed during inatallation:
ADDSWAP, CONFIGURE, INSTALL, SELECT catagories, SOURCE, TARGET.
\vskip 1.8in
\ques
% Project 18
You want NIS accounts to be able to ftp.
What file do you need to modify and what modification do you need to make?
\vskip 1.0in
\ques
% Project 20
Describe when you would use {\ltt{}chmod4711} on a program?
\vskip 1.5in
\ques
% Project 15
How would you make the printer {\ltt{}lj1} from
{\ltt{}psvr413.cecs.csulb.edu} available to users on your machine.
(Give the file name(s) and contents.)
\vskip 1.0in
\ques
% Project 15
You want to send all messages from {\ltt{}lpd} (facility {\ltt{}lpr})
to a file called {\ltt{}/var/log/lpd}.
How would you do this?
Give the file name, the modification you would make to that file;
and describe the command you would use to activate that modification.
\vskip 1.0in
\vfill\eject
\ques
% Project 21
You wish to set up a news group called {\ltt{}classes.476}.
What files will need to be modified
and what modifications would be made to those files
(include modifications that are done by {\ltt{}ctlinnd}).
Also, what directory will need to be created?
\vskip 2.5in
\ques
% Project 21
You want your machine to send and receive news articles from
the news server on {\ltt{}cougar}.
What files need to be modified and what modifications are done
to those files.
Also, after these modifications have been made and activated,
what file will appear (and in what directory) when you post news.
\vskip 2.0in
\ques
% Project 13
You want all user accounts distributed using NIS from cheetah
to be valid accounts on your machine.
What files do you need to change and for each file, what change do
you need to make?
\vskip 1.0in
\ques
% Project 25
What are the 3 special sections in {\ltt{}smb.conf}?
\vskip 1.0in
\vfill\eject
\ques
% Project 24
What are the things (not including the distfile) that need to be
enabled and or set up to allow {\ltt{}rdist} to work.
Give the file names and contents.
\vskip 2.0in
\ques
% Project 18
How do you find out which dynamic libraries {\ltt{}smbd} uses?
\vskip 0.5in
\ques
% Project 19
In {\ltt{}sendmail.cf}:
If you are looking for where the macro P is {\it used} what do you look for?
If you are looking for where the class Q is {\it defined} what do you look for?
\vskip 1.0in
\ques
% Project 24
You as {\ltt{}news} wish to install the contents
of {\ltt{}innd-2-2-3.tgz}
into {\ltt{}~news/bin} on {\ltt{}lab21}
(this directory is owned by the user {\ltt{}news}.
You will copy (push) the file over the network from {\ltt{}panther},
call it {\ltt{}webupdate.tgz} and extract the files from
the archive (the extraction is done on {\ltt{}lab21}).
Assuming permissions have already been set up;
a command file needs to be built on {\ltt{}panther};
give the exact contents of that file.
\vskip 2.5in
\vfill\eject
\ques
% Project 14
Describe how you would allow
the {\ltt{}/var/spool/news/articles} directory on your machine to be mounted
on {\ltt{}jaguar} read/write
and on {\ltt{}cheetah} read only?
Give the file name, and the line in that file that would be
necessary to do this; and give the command to activate this change.
\vskip 1.7in
\ques
% Project 14
Give the {\ltt{}fstab} entry that would mount
the {\ltt{}/slackware} directory from {\ltt{}jaguar.net.cecs.csulb.edu}
on the {\ltt{}/mnt} directory of your machine.
\vskip 0.8in
\ques
% Project 23
You have two machines for which you supply name service.
{\ltt{}a.quest.org} (245.122.33.1) and 
{\ltt{}b.quest.org} (245.122.33.2).
Give the entire forward zone file for the zone {\ltt{}quest.org},
including the SOA, if the DNS server for that zone
is {\ltt{}dns.quest.org} ({\ltt{}245.122.1.1}).
\vskip 3.5in
\ques
% Project 23
For the pervious question, give just the {\ltt{}PTR} entries
that would occur in the reverse zone file.
\vfill\eject
Analysis section. After the homework 17 reinstall
several things were not done correctly on {\ltt{}lab88}...

\ques
You can login to {\ltt{}lab88} using the
{\ltt{}bob} account, but not using your {\ltt{}csa476xx}.
What are the first 2 things would you check on {\ltt{}lab88}.
(Give them in order of the most likely to find the problem.)
(For each item, how you would perform the check.)
\vfill
\ques
You can ftp to {\ltt{}lab88} using the {\ltt{}bob} account,
but not using the anonymous account.
What are the first 2 things would you check.
(Give them in order of the most likely to find the problem.)
(For each item, how you would perform the check.)
\vfill
\ques
From {\ltt{}jaguar} your telnet to {\ltt{}lab88} works, but
rlogin to {\ltt{}lab88} fails.
What are the first 2 things on {\ltt{}lab88} would you check.
(Give them in order of the most likely to find the problem.)
(For each item, how you would perform the check.)
\vfill
\ques
The drives from {\ltt{}cheetah} didn't get mounted.
What are the first 2 things on {\ltt{}lab88} would you check.
(Give them in order of the most likely to find the problem.)
(For each item, how you would perform the check.)
\bye
