\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2002, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook.

\ques
(4 points)
% Project 18
How does anonymous ftp work?
\vskip 2.0in
\ques
(4 points)
% Project 18
How do you disable anonymous ftp and still
allow users to use ftp to their own accounts?
\vskip 0.8in
\ques
(4 points)
% Project 19
In sendmail configuration,
describe the difference between a macro ({\ltt{}D})
and a class ({\ltt{}C}).
\vskip 1.2in
\ques
(4 points)
% Project 20
You have a C program (called {\ltt{}getgrade}) already build and compiled.
This program will allow a user to look only at their line in the
grade sheet {\ltt{}grades.txt} for the class.
Of course, the grade sheet needs to be protected so it is not readable.
What do you need to to to make this program work.
Give the chmod commands to
set up those protections for both the above files.
\vskip 1.0in
\ques
(4 points)
% Project 21
You wish to allow users from {\ltt{}lynx} and {\ltt{}jaguar} to
read news using your machine as a server.
What do you need to do? (Give file(s) and modifications.)
\vskip 0.8in
\vfill\eject
\ques
(4 points)
% Project 21
You want your machine to receive news articles from {\ltt{}cheetah}.
What do you need to do?
(Give file(s) and modifications.)
\vskip 1.9in
\ques
(4 points)
% Project 22
Suppose you are setting up the apache httpd at a site and
their users have been keeping their web documents
in their {\ltt{}~/www} directories.
How do you configure apache so their directories will
still be avaiable on the web.
(Give file(s) and modifications.)
\vskip 1.5in
\ques
(4 points)
% Project 23
You have two machines for which you supply name service.
{\ltt{}mork.occc.edu} (154.2.3.2) and 
{\ltt{}mindy.occc.edu} (154.2.3.3).
Give the entire forward zone file for the zone {\ltt{}occc.edu},
including the SOA, if the DNS server for that zone
is {\ltt{}dns.occ.edu} ({\ltt{}154.2.3.1}).
\vfill\eject
\ques
(4 points)
% Project 23
How do you use {\ltt{}nslookup} to test if name service is working for
on particular server.
\vskip 1.8in
\ques
(4 points)
% Project 24
You wish to allow user {\ltt{}bob} on {\ltt{}cheetah.cecs.csulb.edu}
to put files onto your www area (user {\ltt{}www}) on 
your machine ({\ltt{}lab99.net.cecs.csulb.edu}).
What do you do?
(Give file(s) and contents.)
\vskip 1.0in
\ques
(4 points)
% Project 24
User {\ltt{}bob} wishes to put a program (file) called 
{\ltt{}newhomepage.tar} from his home directory into {\ltt{}~www/htdocs}
on {\ltt{}lab99} (call it {\ltt{}page.tar}) and extract the files from the tar
archive (the extraction is done on {\ltt{}lab99}).
What does {\ltt{}bob} do? (Give files, contents and command.)
\vskip 2.0in
\ques
(4 points)
% Project 25
You want Windows 95 users to be able to access a repository
that contains the starting files for their homework.
You have those files in {\ltt{}/winstuff/csource}
on your Linux machine.
What files would you need to change and what
changes would you need to make to those files.
(Assume the appropriate software is already installed.)
\vskip 1.3in
\vfill\eject
\ques
(4 points)
% Project 13
If a machine is running {\ltt{}ypserv}, where does the 
{\ltt{}ypserv} get it's password information?
\vskip 1.4in
\ques
(4 points)
% Project 13
What does the file {\ltt{}ypserv.conf} do and when
do yo need to use it?
\vskip 1.4in
\ques
(4 points)
% Project 14
Describe how you would
export the {\ltt{}/homes} directory on your machine to
jaguar read/write
and to cheetah read only?
(Give the file name(s) and contents.)
\vskip 1.2in
\ques
(4 points)
% Project 14
Give the command to mount
the {\ltt{}/slak} directory from {\ltt{}jaguar.cecs.csulb.edu}
on your machines {\ltt{}/cdrom} directory.
(Do not use {\ltt{}fstab}.)
\vskip 1.2in
\ques
(4 points)
% Project 15
How would you make the printer {\ltt{}cecs1} from
{\ltt{}cheetah} available to users on your machine.
(Give the file name(s) and contents.)
\vskip 1.0in
\vfill\eject
\ques
(4 points)
% Project 15
Describe how you would have
critical ({\ltt{}crit}) messages (or higher) from the printer daemon 
({\ltt{}lpr})
go into the file {\ltt{}/var/log/lpd}
and
send notice ({\ltt{}notice}) (only, no higher or lower)
messages from the mail system ({\ltt{}mail}) to {\ltt{}cheetah}.
(Give the file name(s) and contents.)
\vskip 1.5in
\ques
(4 points)
% Project 16
What is the {\ltt{}pkgtool}?
\vskip 1.3in
\ques
(4 points)
% Project 17
For a blank harddrive,
give the sequence of {\ltt{}fdisk} commands to
set {\ltt{}hda1} to contain cylinders 0-500
and be a Linux partition
and {\ltt{}hda2} to contain cylinders 501-600
and be a swap partition.
\vskip 3.0in
\ques
(4 points)
% Project 17
Which installation disk set contains the documentation?
\vskip 0.5in
\ques
(4 points)
% Project 17
During the install you selected a target.
What is a target and
what target did you select?
\vskip 0.5in
\vfill\eject
Analysis section. 

\ques
(4 points)
{\ltt{}linux122} in room ECS 412 can't print.
Propose a series of 3 tests (these must be commands
that you could run on {\ltt{}linux122}) and
describe what each of those tests tell you
about the problem.
would 
\vskip 0.5in
\vfill
\ques
(4 points)
When logging into {\ltt{}lab99} (in ECS 413)
as {\ltt{}cav476z5} you receive the message
``No such user".
Suppose {\ltt{}cav476z5}  can log in to {\ltt{}lab98}.
What could be misconfigured on {\ltt{}lab99}?
List exactly 3 things. (There are more, just list 3 of them.)
\vfill
\ques
(4 points)
From a web browser on {\ltt{}lab88} you attempt to access {\ltt{}www.cecs.csulb.edu}
and get the message ``Unable to contact server" (Error 404).
What things could be misconfigured on {\ltt{}lab88} that could cause this?
List exactly 3 things. (There are more, just list 3 of them.)
\bye
