\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Fall 2004, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook. No digital or communitcations devices.
All questions 4 points.

\ques
% Project 15
You want to send all messages of level {\ltt{}notice} and higher
from {\ltt{}innd} (facility {\ltt{}news})
to a file called {\ltt{}/var/log/newslog}.
How would you do this?
Give the file name, the modification you would make to that file;
and describe the command you would use to activate that modification.
\vskip 1.0in
\ques
% Project 16
What floppy disks are in the standard boot set ({\ltt{}bare.i})
and what floppy disks are in the boot set we used.
\vskip 0.8in
\ques
% Project 22
Explain how you would allow password access to the URL
{\ltt{}~ftp} on your machine.
\vskip 1.5in
\ques
% Project 22
Explain how you would deny http access to {\ltt{}/home/share}.
Give the file name and contents.
\vskip 2.3in
\vfill\eject
\ques
% Project 17
How did you disable samba (temporarily) after doing an install?
\vskip 0.6in
\ques
% Project 18
You want disable ftp access for the account {\ltt{}joe}.
What file do you need to modify and what modification do you need to make?
\vskip 1.0in
\ques
% Project 20
Give the {\ltt{}ls -l} for the {\ltt{}getscore} program
given that the {\ltt{}ls -l} for the score file is
\hfill\break
{\ltt{} -rw------- volper faculty   Scores}
\vskip 0.6in
\ques
% Project 15
How would you make the printer {\ltt{}cecs1} from
{\ltt{}cheetah.cecs.csulb.edu} available to users on your machine.
(Give the file name(s) and contents.)
\vskip 1.0in
\ques
% Project 17
For a blank harddrive,
give the sequence of {\ltt{}fdisk} commands to
set {\ltt{}hda1} (cylinders 0-1400)
to be a bootable (active) Linux native (ext2) partition
and {\ltt{}hda2} (cylinders 1401-1500)
to be a Linux swap partition.
%\vskip 3.0in
\vfill\eject
\ques
% Project 21
You wish to set up a news group called {\ltt{}classes.476}.
What files will need to be modified
and what modifications would be made to those files
(include modifications that are done by {\ltt{}ctlinnd}).
Also, what directory will need to be created?
\vskip 2.7in
\ques
% Project 21
You want users from {\ltt{}cougar} to be able to read and
post news using your news server.
What files need to be modified and what modifications are done
to those files.
\vskip 2.2in
\ques
% Project 13
You want {\ltt{}heart} to be the NIS server for your machine.
What file do you need to change and what change do
you need to make?
\vskip 1.0in
\ques
% Project 24
You as {\ltt{}news} wish to install the contents
of {\ltt{}apache-3-3-4.tgz}
into {\ltt{}/var/apache} on {\ltt{}lab89}
(this directory is owned by the user {\ltt{}apache}.
You will copy (push) the file over the network from {\ltt{}cougar},
call it {\ltt{}apacheupdate.tgz} and extract the files from
the archive (the extraction is done on {\ltt{}lab89}).
Assuming permissions have already been set up;
a command file needs to be built on {\ltt{}cougar};
give the exact contents of that file.
\vskip 1.0in
\vfill\eject
\ques
% Project 24
What are the things (not including the distfile) that need to be
enabled and or set up to allow {\ltt{}rdist} to work.
Give the file names and contents.
\vskip 1.3in
\ques
% Project 18
How would you determine what dynamic libraries {\ltt{}sendmail} is using?
\vskip 0.5in
\ques
% Project 19
In {\ltt{}sendmail.cf}:
Define a class {\ltt{}H} to contain {\ltt{}joe} and {\ltt{}bob}. 
If you were looking for where the class H is {\it used} what would you look for?
\vskip 1.5in
\ques
% Project 25
Give the {\ltt{}smb.conf} entries necessary to make
{\ltt{}/var/htdocs} available as a public share to
machines running Windows.
\vskip 1.5in
\vfill\eject
\ques
% Project 14
Describe how you would allow
the {\ltt{}/home/share} directory on your machine to be mounted
by {\ltt{}cheetah} read/write
and by {\ltt{}jaguar} read only?
Give the file name, and the line in that file that would be
necessary to do this; and give the command to activate this change.
\vskip 1.0in
\ques
% Project 14
Give the {\ltt{}fstab} entry that would mount
the {\ltt{}/var/log} directory from {\ltt{}jaguar.net.cecs.csulb.edu}
on the {\ltt{}/cdrom} directory of your machine.
\vskip 0.8in
\ques
% Project 23
You have two machines for which you supply name service.
{\ltt{}a.ohio.gov} (133.22.15.1) and 
{\ltt{}b.ohio.gov} (133.22.15.2).
Give the entire reverse zone file for the zone {\ltt{}ohio.gov},
including the SOA, if the DNS server for that zone
is {\ltt{}dns.ohio.gov} ({\ltt{}133.22.1.1}).
\vskip 4.2in
\ques
% Project 23
For the pervious question, give just the {\ltt{}A} entries
that would occur in the forward zone file.
\vfill\eject
Analysis section. Assume {\ltt{}lab88} is a machine you administer.
For each of the questions on this page
state what things would you check on {\ltt{}lab88}
and for each thing you would check state how you would perform the check.

\ques
After adding the user bob;
you can login to {\ltt{}lab88} using the
{\ltt{}bob} account, and the {\ltt{}csa476xx} but not as {\ltt{}root}.
\vfill
\ques
You have a web server running on {\ltt{}lab88}.
You notice people have WWW access to {\ltt{}~bob} but not to {\ltt{}~sue}.
\vfill
\ques
Telnet from {\ltt{}jaguar} to {\ltt{}lab88} works, but
telnet from {\ltt{}panther} doesn't.
\vfill
\ques
When you log in as {\ltt{}csa476xx} you get the message
``No home directory".
\bye
