\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2003, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook.

\ques
(4 points)
% Project 22
Explain how you would allow http access to all directories in
{\ltt{}/net/u1} except for
{\ltt{}/net/u1/hide}.
Give the file name and contents.
\vskip 2.8in
\ques
(4 points)
% Project 16
What two things is the package tool used for?
\vskip 1.0in
\ques
(4 points)
% Project 17
For a blank harddrive,
give the sequence of {\ltt{}fdisk} commands to
set {\ltt{}hdb1} to have cylinders 0-800
be a Linux swap
and {\ltt{}hda2} to have cylinders 801-1000
be a Linux native (ext2)  partition.
\vskip 3.0in
\ques
(4 points)
% Project 17
What is a disk set?
\vskip 0.8in
\vfill\eject
\ques
(4 points)
% Project 18
Explain how anonymous ftp protection works.
\vskip 1.5in
\ques
(4 points)
% Project 18
How do you find out which libraries {\ltt{}fdisk} uses?
\vskip 0.5in
\ques
(4 points)
% Project 19
In {\ltt{}sendmail.cf}:
If you are looking for where the macro Q is use what do you look for?
If you are looking for where the class T is use what do you look for?
\vskip 1.2in
\ques
(4 points)
% Project 20
The {\ltt{}sudo} command allows an ordinary to execute a root command;
provided the name of the user and the name of the command
are found in the {\ltt{}sudo.conf} file.
Describe how the {\ltt{}sudo} program and {\ltt{}sudo.conf} fill are set up?
Include the protections (mods) and ownership.
\vskip 2.7in
\ques
(4 points)
% Project 15
You want to dump all messages from {\ltt{}innd} (facility {\ltt{}news})
into a file called {\ltt{}/var/log/newslog}.
How would you do this?
(Give the file name and modification.)
\vskip 1.3in
\vfill\eject
\ques
(4 points)
% Project 21
You wish to set up a new news group called {\ltt{}comp.476}.
What directory will need to be created for this to happen
and who will need to own that directory?
\vskip 0.5in
\ques
(4 points)
% Project 21
You want your machine to send receive news articles from
the news server on {\ltt{}cheetah}.
What do you need to do?
(Give file(s) and modifications.)
\vskip 1.9in
\ques
(4 points)
% Project 23
You have two machines for which you supply name service.
{\ltt{}alpha.uci.edu} (129.195.4.2) and 
{\ltt{}beta.uci.edu} (129.195.4.3).
Give the entire forward zone file for the zone {\ltt{}uci.edu},
including the SOA, if the DNS server for that zone
is {\ltt{}dns.uci.edu} ({\ltt{}129.195.4.5}).
\vfill
\ques
(4 points)
% Project 23
What is the difference between a forward and a reverse DNS zone?
\vskip 1.2in
\eject
\ques
(4 points)
% Project 24
Explain the two means of remote user pre-authorization.
Give the file names and what sort of authorization they allow.
\vskip 1.5in
\ques
(4 points)
% Project 24
User {\ltt{}news} wishes to put install the contents
of {\ltt{}/slak8/slackware/innd-bin.tgz}
into {\ltt{}~news/bin} on {\ltt{}lab99}. Copy
it accross, call it {\ltt{}newsupdate.tgz} and extract the files from
the archive (the extraction is done on {\ltt{}lab99}).
Assuming permissions have already been set up;
a file needs to be built; give the exact contents of that file.
\vskip 2.1in
\ques
(4 points)
% Project 25
You want to make {\ltt{}/home/bob/stuff} a public read-only windows
share.
Give the contents of the {\ltt{}smb.conf} file that are necessary
to do this.
\vskip 1.8in
\vfill
\ques
(4 points)
% Project 25
On looking for the stuff share, you also notice that there are
extra shares, in particular you see a share called {\ltt{}guest}
and a share called {\ltt{}lp}.
Obviously you need to remove some stuff from the {\ltt{}smb.conf};
what sections do you need to remove to get rid of these?
\vskip 1.0in
\eject
\ques
(4 points)
% Project 13
If a machine is running a yp client, what determines where
the machine get it's password information? Give file names
and indicate which lines in those files.
\vskip 1.5in
\ques
(4 points)
% Project 13
Explain the what the options {\ltt{}files}, {\ltt{}nis} and
{\ltt{}compat} mean in the {\ltt{}nsswitch.conf} file.
Also, give an example line from that file that uses at
least two of those options.
\vskip 1.9in
\ques
(4 points)
% Project 14
Describe how you would
export the {\ltt{}/home} directory on your machine to
{\ltt{}cougar} read/write
and to {\ltt{}puma} read only?
(Give the file name(s) and contents.)
\vskip 1.7in
\ques
(4 points)
% Project 14
Give the {\ltt{}fstab} entry that would mount
the {\ltt{}/u4} directory from {\ltt{}cheetah.cecs.csulb.edu}
on the {\ltt{}/net/cheetah/u4} directory of your machine.
\vskip 0.8in
\ques
(4 points)
% Project 15
How would you make the printer {\ltt{}lp} from
{\ltt{}puma} available to users on your machine.
(Give the file name(s) and contents.)
\vskip 1.0in
\vfill\eject
Analysis section. 

\ques
(4 points)
You get a report that anonymous {\ltt{}ftp} to
{\ltt{}lab99} doesn't work.
What are the first 2 things would you check on {\ltt{}lab99}.
(Give them in order of the most likely to find the problem.)
(For each item, how you would perform the check.)
\vfill
\ques
(4 points)
A user reports they get an error
when accessing {\ltt{}http://lab99/system/docs.html}
What could be misconfigured on {\ltt{}lab99}?
What are the first 3 things would you check.
(Give them in order of the most likely to find the problem.)
(For each item, how you would perform the check.)
\vfill
\ques
(4 points)
The command {\ltt{}mount -t nfs 134.139.248.88:/home /mnt} fails with the
message ``permission denied"
What are the first 2 things on {\ltt{}lab88} would you check.
(For each item, how you would perform the check.)
\bye
