\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Fall 2000, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook.

\ques
(4 points)
% Project 13
You are instructed to set up your machine as an NIS client. (domainname yp476,
ypserver 134.139.45.66).  
Using the nsswitch method,
which files will you need to edit or create, and what do you need to change
or place in those files?
(Do NOT include files files from {\ltt{}rc.d} in your answer.)
\vskip 1.8in
\ques
(4 points)
% Project 13
You wish logins on your NIS client to use NIS.
Which files will you need need to edit, 
and what do you need to change in those files?
(Assume you are using compatibility mode.)
\vskip 1.0in
\ques
(4 points)
% Project 14
Describe how you would
export the {\ltt{}/homes} directory on your machine to all
machines on the 134.139.45.0 cable?
(Give the file name(s) and contents.)
\vskip 1.2in
\ques
(4 points)
% Project 14
Describe how you would make
the {\ltt{}/u1} directory from {\ltt{}lynx.cecs.csulb.edu}
available on your machine when you boot.
(Give the file name(s) and contents.)
\vskip 1.2in
\ques
(4 points)
% Project 15
Describe how you would make
a printer called {\ltt{}laser2} on {\ltt{}lynx} available to
users on your machine as the default printer.
(Give the file name(s) and contents.)
\vskip 1.0in
\vfill\eject
\ques
(4 points)
% Project 15
Describe how you would have
error ({\ltt{}err}) messages (or higher) from the printer software {\ltt{}lpr}
go into the file {\ltt{}/var/log/printer}
and
notice ({\ltt{}notice}) messages from ftp ({\ltt{}ftp})
be sent to {\ltt{}lynx}.
(Give the file name(s) and contents.)
\vskip 1.5in
\ques
(4 points)
% Project 16
You want to load Linux from a Zip drive onto an UltraDMA harddrive.
You need a special (1.44M) floppy.
(a) Which special floppy do you need (boot or root)?
(b) You need an image to {\ltt{}dd} onto that floppy, where would you
look to find out the name of the image you need (give directory
and filename)?
\vskip 1.0in
\ques
(4 points)
% Project 17
You wish to partition your main drive to have a Linux partition
at cylinders 1-200, a swap partition at cylinders 201-300,
and a DOS partition at cylinders 301-350.
What command do you give and exactly what do you type when
running that command.
\vskip 3.0in
\ques
(4 points)
% Project 17
When installing the operating system, 
you want to install the networking utilities on your machine.
Which disk set do you need?
\vskip 0.5in
\ques
(4 points)
% Project 17
You installed the web server software but disabled it.
What command did you run to disable this software?
\vskip 0.5in
\vfill\eject
\ques
(4 points)
% Project 18
From the standpoint of how the system handles security,
what is the difference between a regular ftp session
and an anonymous ftp session?
\vskip 2.0in
\ques
(4 points)
% Project 19
You ISP (at home) directs you to use
{\ltt{}smtp.goodnet.com} as a smart relay host for
your (Linux) machine.
What file would you modify and what change would you make to that file?
(Hint: {\ltt{}S} is used for smart.)
\vskip 1.0in
% \vfill\eject
\ques
(4 points)
% Project 20
You have a C program (called {\ltt{}submit}) already build and compiled.
This program will allow a user to place a copy of their homework
into your home directory.
What do you need to to to make this probram work.
(Give the exact command.)
\vskip 0.8in
\ques
(4 points)
% Project 20
If you try to write the above ``submit" program as a shell script
you won't be able get it to work.
Explain why.
\vskip 1.2in
\ques
(4 points)
% Project 21
You wish to allow news articles from {\ltt{}lynx} to be transfered (fed)
to your machine.
What do you need to do? (Give file(s) and modifications.)
\vskip 1.4in
\vfill\eject
\ques
(4 points)
% Project 21
You want your machine to transfer (feed) news articles to {\ltt{}lynx}.
What do you need to do?
(Give file(s) and modifications.)
\vskip 1.9in
\ques
(4 points)
% Project 22
Suppose you have www configured and running. You are to make a
modification so that {\ltt{}/home/joe} is not accessible
via the web.
What do you need to do? (Give file(s) and modifications.)
\vskip 1.5in
% \vfill\eject
\ques
(4 points)
% Project 23
You have two machines for which you supply name service.
{\ltt{}oven.home.com} (147.92.2.2) and 
{\ltt{}coffeepot.home.com} (147.92.2.3).
Give the zone entries (only zone entries) of the {\ltt{}named.conf}
for your DNS server.
\vfill
\eject
\ques
(4 points)
% Project 23
Give the forward zone file for the above question. (Include the SOA).
\vskip 2.8in
\ques
(4 points)
% Project 24
You wish to allow user {\ltt{}larry} on {\ltt{}jaguar.cecs.csulb.edu}
to put files onto your web area (user {\ltt{}www}) on 
your machine ({\ltt{}lab29.net.cecs.csulb.edu}).
What do you do?
(Give file(s) and contents.)
\vskip 1.0in
\ques
(4 points)
% Project 24
User {\ltt{}larry} wishes to put a program (file) called 
{\ltt{}hi.html} from his home directory into {\ltt{}~www/htdocs}
call it {\ltt{}index.html} and change its permissions to
be {\ltt{}644}.
What does {\ltt{}larry} do? (Give files, contents and command.)
\vskip 1.6in
\ques
(4 points)
% Project 25
You wish to allow the directory {\ltt{}~ftp/pub} to be accessed by
Windows machines as a share. (Assume Samba is installed and 
starts when you boot.)
What do you need to do?
(Give file(s) and contents.)
\vskip 1.3in
\vfill\eject
Analysis section. Assume that the instructor as a part of this exam
has partially disabled or modified the machine you administer in the lab.

\ques
(4 points)
Suppose the following work:

{\program
 ping 134.139.136.65
 ping 134.139.136.85
\endprogram}

and the following fails:

{\program
 ping 134.139.45.6
\endprogram}

What could be misconfigured on the machine?
\vfill
\ques
(4 points)
Assume you fix the above problem and the instructor disables your machine
again.

Suppose {\ltt{}root} and {\ltt{}john} can login with no problems, but when 
the {\ltt{}csv472z3} account tries to log in it says ``No such user".
What could be misconfigured on the machine?
\vfill
\ques
(4 points)
Assume you fix the above problem and the instructor disables your machine
again.
You can't access other machines when you use their names, but
you can when you use their addresses.
What could be misconfigured on the machine?
\bye
