\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2000, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook.

\ques
(4 points)
% Project 13
You are instructed to set your machine as an NIS client. (domainname cecsyp,
ypserver 134.139.46.6).  
Which files will you need to edit or create, and what do you need to change
or place in those files?
(Do NOT include files files from {\ltt{}rc.d} in your answer.)
\vskip 1.0in
\ques
(4 points)
% Project 13
You wish logins on your NIS client to use NIS.
Which files will you need need to edit, 
and what do you need to chagne in those files?
\ques
(4 points)
% Project 14
Describe how you would
export the {\ltt{}/var} directory on your machine to all
machines in {\ltt{}.net.cecs.csulb.edu}.
(Give the file name(s) and contents.)
\vskip 1.0in
\ques
(4 points)
% Project 14
Describe how you would make
the {\ltt{}/u4} directory from {\ltt{}jaguar.cecs.csulb.edu}
available on your machine when you boot.
(Give the file name(s) and contents.)
\vskip 1.0in
\ques
(4 points)
% Project 15
Describe how you would make
a printer called {\ltt{}lp} on {\ltt{}cheetah} available to
users on your machine as the default printer.
(Give the file name(s) and contents.)
\vskip 1.0in
% \vfill\eject
\ques
(4 points)
% Project 15
Describe how you would have
warining ({\ltt{}warn}) messages (or higher) from {\ltt{}news}
go into the file {\ltt{}/var/log/newslog}
and
debug ({\ltt{}debug}) messages from the mail subsystem ({\ltt{}mail})
be sent to {\ltt{}cheetah}.
(Give the file name(s) and contents.)
\vskip 1.8in
\ques
(4 points)
% Project 16
Describe the difference between a boot disk and a root disk?
\vskip 1.0in
\ques
(4 points)
% Project 17
You wish to partition your main drive to have a Linux partition
at cylinders 1-150, a swap partition at cylinders 151-200,
and a second Linux partition at cylinders 201-250.
What command do you give and exactly what do you type when
running that command.
\vskip 3.0in
\ques
(4 points)
% Project 17
When installing the operating system, 
you want to install the compilers on your machine.
Which disk set do you need?
\vskip 0.5in
\ques
(4 points)
% Project 17
You installed the samba server software but disabled it.
What command did you run to disable this software?
\vskip 0.5in
\ques
(4 points)
% Project 18
If you are using anonymous ftp, what are the appropriate
ownership and protections for things found under the {\ltt{}~ftp}
directory.
\vskip 2.5in
\ques
(4 points)
% Project 19
Suppose {\ltt{}smtp.mybusiness.com} is the mail server for your company.
On your client machines,
what file would you modify and what change would you make to that file?
\vskip 1.0in
\vfill\eject
\ques
(4 points)
% Project 20
Write a program (called {\ltt{}deposit}) that anyone can run that allows 
them to place a copy of their {\ltt{}.cshrc} file into your home directory 
(as {\ltt{}sample.cshrc}).
\vskip 3.5in
\ques
(4 points)
% Project 20
Show the exact {\ltt{}chmod} command
that you will need to use to allow the program from the previous
question to work.
\vskip 0.5in
\ques
(4 points)
% Project 21
You wish to allow news articles from cheetah to be transfered (fed)
to your machine.
What do you need to do? (Give file(s) and modifications.)
\vskip 1.2in
\ques
(4 points)
% Project 21
You wish to allow users on {\ltt{}lab85} to read and post news using
your machine.
What do you need to do?
(Give file(s) and modifications.)
\vskip 1.2in
\ques
(4 points)
% Project 22
You want your web server to run in the {\ltt{}/var/web} dirctory.
How do you set up {\ltt{}httpd.conf} to do this?
\vskip 1.0in
\vfill\eject
\ques
(4 points)
% Project 23
You have two machines for which you supply name service.
{\ltt{}sales.mybusiness.com} (145.100.1.3) and 
{\ltt{}accounts.mybusiness.com} (145.100.1.5).
Give the zone entries (only zone entries) of the {\ltt{}named.conf}
for your DNS server.
\vfill
\ques
(4 points)
% Project 23
Give the reverse zone file for the above question. (Include the SOA).
\vfill
\ques
(4 points)
% Project 24
You wish to allow user {\ltt{}joe} on {\ltt{}cheetah.cecs.csulb.edu}
to put files onto your smb server area (user {\ltt{}samba}) on 
your machine ({\ltt{}lab29.net.cecs.csulb.edu}).
What do you do?
(Give file(s) and contents.)
\vskip 0.6in
\eject
\ques
(4 points)
% Project 24
User {\ltt{}joe} wishes to put a program (file) called 
{\ltt{}newstuff} from his home directory into {\ltt{}~samba/bin}
call it {\ltt{}newstuff} and change  its permissions so
it is executable. 
What does Joe do? (Give files, contents and command.)
\vskip 3.0in
\ques
(4 points)
% Project 25
You wish to allow the directory {\ltt{}~ftp/pub} to be accessed by
Windows machines as a share. (Assume Samba is installed and 
starts when you boot.)
What do you need to do?
(Give file(s) and contents.)
\vskip 2.5in
\vfill\eject
Analysis section. Assume that the instructor as a part of this exam
has partially disabled the machine you administer in the lab.

\ques
(4 points)
Suppose the following work:

{\program
 ping cheetah.cecs.csulb.edu
 ping lab86.net.csulb.edu
\endprogram}

and the following fails:

{\program
 ping cheetah
\endprogram}

What could be misconfigured on the machine?
\vfill
\ques
(4 points)
Assume you fix the above problem and the instructor disables your machine
again.

Suppose root and {\ltt{}john} can login with no problems, but when 
the {\ltt{}csv472z3} account logs in it says ``No home directory".
What could be misconfigured on the machine?
\vfill
\ques
(4 points)
Assume you fix the above problem and the instructor disables your machine
again.

Suppose yhou can post news and the world gets it, and you can read news 
posted locally;
but news from the rest of the world isn't getting to your machine.
What could be misconfigured on the machine?
\bye
