\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Fall 2002, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook.

\ques
(4 points)
% Project 16
What is on the boot floppy and what is on root floppy?
\vskip 1.3in
\ques
(4 points)
% Project 17
For a blank harddrive,
give the sequence of {\ltt{}fdisk} commands to
set {\ltt{}hda1} to contain cylinders 0-900
and be a Linux partition
and {\ltt{}hda2} to contain cylinders 901-1200
and be a swap partition.
\vskip 3.0in
\ques
(4 points)
% Project 17
Give the five top level steps in the install process.
(I.e., what 5 selections did use from the main menu.)
\vskip 2.3in
\ques
(4 points)
% Project 17
During the install you selected a source.
What is a source and
what source did you select?
\vskip 0.5in
\vfill\eject
\ques
(4 points)
% Project 18
What does {\ltt{}chroot} do?
\vskip 1.3in
\ques
(4 points)
% Project 18
What will the {\ltt{}ldd} command tell you about
a program?
\vskip 0.8in
\ques
(4 points)
% Project 19
Suppose {\ltt{}Z} is the macro that designates an archive
log for mail and {\ltt{}Z} is a class that designates
users whose mail is not to be archived.
If you want to archive mail for users other than
{\ltt{}root}, {\ltt{}bob} and {\ltt{}sue} to the file {\ltt{}/var/mail/arch};
show the lines that will need to put intto {\ltt{}sendmail.cf}
\vskip 1.2in
\ques
(4 points)
% Project 20
A faculty memember wants to allow students to submit homework;
and have that homework deposted in the faculty member's
{\ltt{}submissions} directory.
Describe how would you set up such a capability? (Include the mods
and ownership).
\vskip 2.5in
\ques
(4 points)
% Project 21
You wish to set up a new news group.
What files and directories will be changed when
you set it up?
\vskip 1.0in
\vfill\eject
\ques
(4 points)
% Project 21
You want your machine to send news articles to {\ltt{}cheetah}.
What do you need to do?
(Give file(s) and modifications.)
\vskip 1.9in
\ques
(4 points)
% Project 22
Explain how the {\ltt{}/Directory} directive works.
Your explanation should include how multiple directives interact.
\vskip 1.5in
\ques
(4 points)
% Project 23
You have two machines for which you supply name service.
{\ltt{}mork.occc.edu} (172.3.3.2) and 
{\ltt{}mindy.occc.edu} (172.3.3.3).
Give the entire reverse zone file for the zone {\ltt{}ventura.edu},
including the SOA, if the DNS server for that zone
is {\ltt{}dns.ventura.edu} ({\ltt{}172.3.3.5}).
\vfill\eject
\ques
(4 points)
% Project 23
How would you set up {\ltt{}named} so that the forward and reverse
files are located in {\ltt{}/var/etc/named}?
\vskip 1.2in
\ques
(4 points)
% Project 24
What is the difference between the {\ltt{}.rhosts} file and
the {\ltt{}hosts.equiv} file.
\vskip 1.8in
\ques
(4 points)
% Project 24
User {\ltt{}sam} wishes to put install the contents
{\ltt{}apache.tgz} from his home directory on {\ltt{}cheetah}
into {\ltt{}~apache/bin} on {\ltt{}lab99}. Copy
it accross, call it {\ltt{}newapache.tgz}) and extract the files from
the archive (the extraction is done on {\ltt{}lab99}).
Assuming permissions have already been set up;
what does {\ltt{}sam} do? (Give files, contents and command.)
\vskip 2.0in
\ques
(4 points)
% Project 25
You want Windows 95 users to be able to access a public share
that contains the starting files for their homework.
You have those files in {\ltt{}/windows/coursestuff}
on your Linux machine.
What files would you need to change and what
changes would you need to make to those files.
(Assume the appropriate software is already installed.)
\vskip 1.3in
\vfill\eject
\ques
(4 points)
% Project 13
If a machine is running a yp client, what determines where
the machine get it's password information? Give file names
and indicate which lines in those files.
\vskip 1.2in
\ques
(4 points)
% Project 13
Give the commands you would use to determine if
account information was being delivered using yp?
\vskip 1.1in
\ques
(4 points)
% Project 14
Describe how you would
export the {\ltt{}/mnt} directory on your machine to
puma read/write
and to jaguar read only?
(Give the file name(s) and contents.)
\vskip 1.0in
\ques
(4 points)
% Project 14
Give the {\ltt{}fstab} entry that would mount
the {\ltt{}/slak} directory from {\ltt{}jaguar.cecs.csulb.edu}
on your machines {\ltt{}/cdrom} directory.
\vskip 0.8in
\ques
(4 points)
% Project 15
How would you make the printer {\ltt{}lp} from
{\ltt{}puma} available to users on your machine.
(Give the file name(s) and contents.)
\vskip 1.0in
\ques
(4 points)
% Project 15
Describe how you would have
critical ({\ltt{}notice}) messages (or higher) from the printer daemon 
({\ltt{}mail})
go into the file {\ltt{}/var/log/mail}
and
send notice ({\ltt{}crit}) (only, no higher or lower)
messages from the mail system ({\ltt{}mail}) to {\ltt{}puma}.
(Give the file name(s) and contents.)
\vskip 1.5in
\vfill\eject
Analysis section. 

\ques
(4 points)
{\ltt{}linux122} won't users log in.
When root logs in, you see the message
``{\ltt{}Can't find /net/charlotte/mail}".
What are the first 3 things would you check.
(Give them in order of the most likely to find the problem.)
(For each item, give the command you would use to do the check.)
\vskip 0.5in
\vfill
\ques
(4 points)
When logging into {\ltt{}lab99} (in ECS 413)
as {\ltt{}csv476z5} you receive the message
``Setting home to /".
What could be misconfigured on {\ltt{}lab99}?
What are the first 3 things would you check.
(Give them in order of the most likely to find the problem.)
(For each item, give the command you would use to do the check.)
\vfill
\ques
(4 points)
From {\ltt{}trn} {\ltt{}lab88} you get the message ``500 post not allowed".
Assuming {\ltt{}lab88} is a news server, what things could be misconfigured
on {\ltt{}lab88} that could cause this?
List exactly 3 things. (There are more, just list 3 of them.)
\bye
