\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Fall 2003, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook. No digital or communitcations devices.

\ques
(4 points)
% Project 22
Explain how you would allow http access to all directories in
{\ltt{}/home/*/html} but nothing else in
{\ltt{}/home}.
Give the file name and contents.
\vskip 2.8in
\ques
(4 points)
% Project 22
Give the exact command you used to start the web server
\vskip 0.5in
\ques
(4 points)
% Project 16
What is the difference between the boot and the root floppies.
\vskip 1.5in
\ques
(4 points)
% Project 17
For a blank harddrive,
give the sequence of {\ltt{}fdisk} commands to
set {\ltt{}hda1} (cylinders 0-1100)
to be a bootable (active) Linux native (ext2) partition
and {\ltt{}hda2} (cylinders 1101-1175)
to be a Linux swap partition.
%\vskip 3.0in
\vfill\eject
\ques
(4 points)
% Project 17
List 3 of the installation disk sets and give a brief description of what
is in each of those three sets.
\vskip 1.8in
\ques
(4 points)
% Project 18
Who should own {\ltt{}/home/ftp/pub}?
\vskip 0.5in
\ques
(4 points)
% Project 18
How do you find out which dynamic libraries {\ltt{}httpd} uses?
\vskip 0.5in
\ques
(4 points)
% Project 20
The {\ltt{}getgrade} command allows a student to look at their line
in the file that contains the grades, but that file is protected
from everyone except the instructor.
Assuming that {\ltt{}getgrade.c} contains the program that displays the
information for a student;
describe the steps the instructor took to install the program.
Include all commands the instructor needed to use
(start with the {\ltt{}gcc} command).
\vskip 1.0in
\ques
(4 points)
% Project 15
You want to send all messages from {\ltt{}innd} (facility {\ltt{}news})
to a file called {\ltt{}/var/news/news.all}.
How would you do this?
Give the file name, the modification you would make to that file;
and describe the command you would use to activate that modification.
\vskip 1.3in
\vfill\eject
\ques
(4 points)
% Project 21
You wish to set up a new news group called {\ltt{}local.476c}.
What files will need to be modified
and what modifications would be made to those files
(include modifications that are done by {\ltt{}ctlinnd}).
Also, what directory will need to be created?
\vskip 2.5in
\ques
(4 points)
% Project 21
You want your machine to send and receive news articles from
the news server on {\ltt{}panther}.
What files need to be modified and what modifications are done
to those files.
Also, after these modifications have been made and activated,
what file will appear (and in what directory) when you post news.
\vskip 2.0in
\ques
(4 points)
% Project 25
What is the difference between {\ltt{}security=server}
and {\ltt{}security=share}?
\vskip 1.0in
\ques
(4 points)
% Project 25
You want to share the directory {\ltt{}/home/bob/windows},
read-only, to other computers that are running Windows. 
Give the configuration file name that would need to be
changed and the contents that would need to be in that file.
\vskip 1.0in
\vfill\eject
\ques
(4 points)
% Project 24
A network facility needs to be enabled for {\ltt{}rdist} to work.
Give the name file of the file that you would need to modify to enable this
facility, give the line that would need to be in that file
and the command to enable the facility.
\vskip 2.0in
\ques
(4 points)
% Project 24
You {\ltt{}http} wish to put install the contents
of {\ltt{}httpd-2-1.tgz}
into {\ltt{}~apache/bin} on {\ltt{}lab12}
(this directory is owned by the user {\ltt{}apache}.
You will copy (push) the file over the network from {\ltt{}lab99}
it across, call it {\ltt{}webupdate.tgz} and extract the files from
the archive (the extraction is done on {\ltt{}lab12}).
Assuming permissions have already been set up;
a command file needs to be built on {\ltt{}lab12};
give the exact contents of that file.
\vskip 2.5in
\ques
(4 points)
% Project 15
How would you make the printer {\ltt{}laser1} from
{\ltt{}panther} available to users on your machine.
(Give the file name(s) and contents.)
\vskip 1.0in
\ques
(4 points)
% Project 19
In {\ltt{}sendmail.cf}:
If you are looking for where the macro X is {\it defined} what do you look for?
If you are looking for where the class Z is {\it used} what do you look for?
\vskip 1.0in
\vfill\eject
\ques
(4 points)
% Project 14
Describe how you would allow
the {\ltt{}/apache} directory on your machine to be mounted on
{\ltt{}cougar} read/write
and on {\ltt{}panther} read only?
Give the file name, and the line in that file that would be
necessary to do this; and give the command to activate this change.
\vskip 1.7in
\ques
(4 points)
% Project 14
Give the {\ltt{}fstab} entry that would mount
the {\ltt{}/patch} directory from {\ltt{}lynx.net.cecs.csulb.edu}
on the {\ltt{}/mnt} directory of your machine.
\vskip 0.8in
\ques
(4 points)
% Project 23
You have two machines for which you supply name service.
{\ltt{}one.post.org} (196.201.33.1) and 
{\ltt{}two.post.org} (196.201.33.2).
Give the entire forward zone file for the zone {\ltt{}post.org},
including the SOA, if the DNS server for that zone
is {\ltt{}cheetah.test.edu} ({\ltt{}134.140.1.1}).
\vskip 3.5in
\ques
(4 points)
% Project 23
For the pervious question, give just the {\ltt{}PTR} entries
that would occur in the reverse zone file.
\vfill\eject
Analysis section. After the homework 17 reinstall
several things were not done correctly on {\ltt{}lab88}...

\ques
(4 points)
When you login to {\ltt{}lab88} using your
{\ltt{}csc476xx} account the login works,
but you get the message:
``No home directory".
What are the first 2 things would you check on {\ltt{}lab88}.
(Give them in order of the most likely to find the problem.)
(For each item, how you would perform the check.)
\vfill
\ques
(4 points)
From {\ltt{}jaguar} your attempt to rdist to {\ltt{}lab88} fails.
What could be misconfigured on {\ltt{}lab88}?
What are the first 2 things would you check.
(Give them in order of the most likely to find the problem.)
(For each item, how you would perform the check.)
\vfill
\ques
(4 points)
From {\ltt{}jaguar} your attempt to telnet to {\ltt{}lab88} fails.
A connection to {\ltt{}lab88} is made but you get the error message
`Connection closed by foreign host."
What are the first 2 things on {\ltt{}lab88} would you check.
(Give them in order of the most likely to find the problem.)
(For each item, how you would perform the check.)
\vfill
\ques
When you run the command, ``{\ltt{}nslookup 122.112.1.1}"
on {\ltt{}lab88} you get the message ``{\ltt{}server not found}".
What are the first 2 things on {\ltt{}lab88} would you check.
(Give them in order of the most likely to find the problem.)
(For each item, how you would perform the check.)
\bye
