\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2005, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook. No digital or communitcations devices.
All questions 4 points.

\ques
% Project 15
The CECS 472 students are experimenting with syslog.
To help them you need to send all messages from the 
facility {\ltt{}local0} to a file called {\ltt{}/var/log/studentmessages}.
How would you do this?
Give the file name, the modification you would make to that file;
and describe the command you would use to activate that modification.
\vskip 1.2in
\ques
% Project 16
Describe the the package tool and what it is used for.
\vskip 1.0in
\ques
% Project 22
You want to limit http access to {\ltt{}/web/private} user
who know an account name ({\ltt{}joe}) and password ({\ltt{}mypass}).
Explain how you would do this. Give file names, contents and commands.
\vskip 1.7in
\ques
% Project 22
Give, in the correct order, the {\ltt{}http.conf} directives that would
disallow access to all of {\ltt{}/usr} except for {\ltt{}/usr/share}.
%\vskip 2.3in
\vfill\eject
\ques
% Project 17
Name two disk sets (themes) that you installed and give a
brief description of what was in them.
\vskip 1.2in
\ques
% Project 18
You want to allow anonymous ftp.
What file do you need to modify and what modification do you need to make?
What user and directory need to exist?
\vskip 1.2in
\ques
% Project 20
You wish the program {\ltt{}register} to be able to
place a student's name and id into the file {\ltt{}/accounts/list};
but you don't want the students to be able to read that file.
Describe how you would do this.
\vskip 1.8in
\ques
% Project 15
How would you make the printer {\ltt{}lp} from
{\ltt{}cougar.net.cecs.csulb.edu} available to users on your machine.
(Give the file name(s) and contents.)
\vskip 1.2in
\ques
% Project 17
Give an English description of what the following installation steps do:
{\it source}, {\it target}, {\it swap}, {\it configure}.
\vskip 2.0in
\vfill\eject
\ques
% Project 13
You want to add the groups coming in from the NIS server {\ltt{}cougar}
to those found in your local groups file.
What file do you need to change and what change do you need to make?
\vskip 1.0in
\ques
% Project 24
From {\ltt{}cougar}, you wish to install and run the file {\ltt{}httpd}
on {\ltt{}lab89}.
You will use the account {\ltt{}http} on {\ltt{}lab89} to do the install.
Give the contents of your {\ltt{}distfile}.
Don't forget, before you can run, you must {\ltt{}chmod} before you can run.
\vskip 1.4in
\ques
% Project 19
In {\ltt{}sendmail.cf}:
Define a class {\ltt{}Y} to contain {\ltt{}cougar} and {\ltt{}panther}
and a macro {\ltt{}D} to be {\ltt{}bob}.
If you were looking for where the macro D is {\it used} what would you look for?
\vskip 1.6in
\ques
% Project 25
Give the {\ltt{}smb.conf} entries necessary to make
{\ltt{}/usr/share} available as a public share to
machines running Windows.
\vskip 1.5in
\vfill\eject
\ques
% Project 19
You want mail going to {\ltt{}webmaster} to be delivered locally
and not to the smart host.
What file would you need to change and what change would you need to make.
\vskip 1.0in
\ques
% Project 18
Describe the difference between a statically linked and a dynamically
linked executable.
\vskip 1.0in
\ques
% Project 21
You wish to set up a news group called {\ltt{}local.test}.
What files will need to be modified
and what modifications would be made to those files?
(Include modifications that are done by {\ltt{}ctlinnd} if it is
used as part of this process.)
Also, what directory will need to be created?
\vskip 2.7in
\ques
% Project 21
You wish your news server to receiver news transfers from the
{\ltt{}cougar} news server.
What files need to be modified and what modifications are done to those files?
(Include modifications that are done by {\ltt{}ctlinnd} if it is used
as part of this process.)
\vskip 2.2in
\vfill\eject
\ques
% Project 14
Describe how you would allow
the {\ltt{}/home} directory on your machine to be mounted
by {\ltt{}cheetah} and {\ltt{}couger} read/write.
Give the file name, and the line in that file that would be
necessary to do this; and give the command to activate this change.
\vskip 0.9in
\ques
% Project 14
Give the {\ltt{}fstab} entry that would mount
the {\ltt{}/home} directory from {\ltt{}jaguar.net.cecs.csulb.edu}
on the {\ltt{}/mnt} directory of your machine.
\vskip 0.7in
\ques
% Project 23
You have two machines for which you supply name service.
{\ltt{}s.csulb.edu} (133.22.15.1) and 
{\ltt{}t.csulb.edu} (133.22.15.2).
Give the entire forward zone file for the zone {\ltt{}csulb.edu},
including the SOA, if the DNS server for that zone
is {\ltt{}dns.csulb.edu} ({\ltt{}133.22.1.1}).
\vskip 4.2in
\ques
% Project 23
For the pervious question, give the following parts of the {\ltt{}named.conf}
(1) the entry that refers to the forward zone file, assuming the
name of the file is {\ltt{}named.hosts}
(2) the entry that would cause named to look in the directory
{\ltt{}/local/dns} for it's configuration files.
\vfill\eject
Analysis section. Assume {\ltt{}lab88} is a machine you administer.
For each of the questions on this page
state what things would you check on {\ltt{}lab88}
and for each thing you would check state how you would perform the check.

\ques
After adding the user {\ltt{}bob};
{\ltt{}bob} cannot save his homework file.
\vfill
\ques
You cannot rlogin from {\ltt{}cheetah}.
\vfill
\ques
The user {\ltt{}sam} reports that he can't ftp his account
on {\ltt{}lab88}.
\vfill
\ques
When you log in as {\ltt{}root} you see the message
``domain not bound".
\bye
