\input header.tex
\parskip=0pt
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Fall 1996, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notes.

\ques
(8 points)
Linux installation, boot and root floppies.

When you boot, what things happen while your first floppy disk is in the
drive?
\vskip 1.5in
During the boot sequence you may select to use either a ramdisk or a rootdisk
as the second disk you load.
What is the difference between a ramdisk and a rootdisk?
\vskip 1in
What command do you use to review the messaged that were printed during boot?
\vskip 0.7in

\ques
(8 points)
Linux installation, commands.

Give an example of each of the following commands and tell what the
command (as you have shown it) will do?

fdisk:
\vskip 0.8in
mkswap:
\vskip 0.8in
swapon:
\vskip 0.8in
mke2fs:
\vfill\eject

\ques
(6 points)
Terminal configuration.

You attach an old Data Media 1521 to your serial port (COM 1).
You wish to allow root logins from this terminal and no others.
What needs to be in termcap?
\vskip 0.8in

What file do you need to adjust for the desired root login capability and
what should be in that file?
\vskip 1in

\ques
(4 points)
Processes.

What does the RSS field of the ps command tell you?
\vskip 0.8in

\ques
(8 points)
Network configuration.

Your lab machine is assigned the IP number 134.139.136.72 and a netmask
of 255.255.255.192.
What command would you give to accomplish this configuration?
(Give a command that does not require rebooting your machine.)
\vskip 0.8in

For the cable your machine is on, there is one gateway to the rest of the
internet.
The IP address of this gateway is 134.139.136.65.
What command do you give to set up your routing tables?
\vskip 0.8in

You wish to configure your machine to look up machine names using NIS
and to use DNS only when the NIS lookup fails.
What file do you modify and what do your put in that file?
\vskip 1.2in

You wish to configure your machine to use jaguar for its DNS lookups.
What file do you modify and what do your put in that file?
\vfill\eject

\ques
(6 points)
Networking utilities.

How would you find out the protocol number for the transmission control
protocol?
\vskip 0.8in

How would you find out what port number is used by the telnet service?
\vskip 0.8in

You wish to examine a telnet session to see where it is coming from,
what command do you use? (Give the exact form with correct options.)
\vskip 0.8in

\ques
(8 points)
Network File System.

You wish to make the {\ltt{}/homes} directory on your machine
({\ltt{}lion.net.cecs.csulb.edu} available to {\ltt{}lab17}.
On {\ltt{}lab17} this directory should appear as {\ltt{}/local/users}.
Give all the steps you need to take. 
Include the names of files, the contents of those files and
the exact form of all commands.
\vskip 3in

\ques
(6 points)
Network Information System.

You are trying to set up an account for sue.
You want to make sue's default group {\ltt{}majors}.
You go to the {\ltt{}/etc/groups} file and all it
contains is a single line with one letter, a {\ltt{}+}.
What do you do now to find out what number corresponds
to the desired group?
Give the exact form of all commands you would use.
\vfill\eject

\ques
(6 points)
Mail configuration.

This is a hypothetical question to see if your understand the general format.
In the year 2042, the new sendmail allows expanders. 
Usually an expander is a machine on the high-speed netowrk, so that
when you send mail to a group of people, one copy will go over the
slow cables to the expander, which will fan out copies to the list
of recipients.
You want to set up {\ltt{}mailgate.la.us} as your expander.
What file will you modify?
What sort of line would you expect to have to add (or modify) to that file?
\vskip 1in

\ques
(8 points)
Network news.

What is the purpose of the nnrp.access file?
\vskip 0.8in

What is the purpose of the newsfeeds file?
\vskip 0.8in

\ques
(6 points)
Domain Name Service.

You are bringing up your machine on the network
({\ltt{}lion.net.cecs.csulb.edu}, {\ltt{}134.139.136.72}).
Your name server is jaguar and on jaguar the file {\ltt{}named.boot}
contains the following:

{\program
primary  net.cecs.csulb.edu        named.net
primary  136.139.134.in-addr.arpa  named.137
\endprogram}

What changes do you have to make and to what files?
\vskip 2in

\ques
(6 points)
File transfer protocol.

What does the {\ltt{}chroot} system call do?
\vskip 1in

During an ftp, what piece of software would call this command?
\vskip 1in

\ques
(6 points)
WAIS.

You want to set up an index called {\ltt{}grades} on {\ltt{}lion}.
Give the the command to build the index and
the command to search that index from {\ltt{}jaguar}.
\vskip 1in

\ques
(6 points)
World Wide Web.

You want to run a web server on port 8013 and you want the www stuff
to be in the {\ltt{}/u1/cecs/www} directory.
What file do you modify and what lines do you change to do this?
(Don't bother to give the rest of the lines or files and assume
stuff has been untar'ed into the correct place).
\vskip 1in
Give the exact form of the command you use to start the web server?
\vskip 1in

\ques
(8 points)
Network management.

In ECS 416 you want to it setup so that the machine {\ltt{}unix67}
can distribute to {\ltt{}unix68} .. {\ltt{}unix78}.
What would you have to do?
(Include the names of the files, which machines those files are
on and their contents.)
\vskip 1.2in

You wish to distribute a copy of the password file from {\ltt{}unix67}
to the other machines.
What would you have to do?
(Include the names of the files, which machines those files are
on and their contents.)
Although you cannot really do it, I will accept a ".." in the
middle of the list of machines (give complete entries only for unix68 and 
unix78).
Note that the domain names in that lab end in {\ltt{}cecs.csulb.edu}.
\vskip 1in
\bye
