\input header.tex
\input cstuff.tex
\parindent=0in
\nopagenumbers
\headline{{\rm CECS 476, Fall 1996, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}
\bigskip
\parindent=0pt
1) (10 points) 
Boot/root floppies. 
\hfil\break
What is software is loaded into memory from a Linux boot floppy?
\vskip0.5in
There are two types of ``root" disks, ramdisks and root disks.
Describe the difference between the two.
\vskip0.8in
Suppose you wanted to load the ramdisk version of the root from the B
floppy drive.
What command/option is issued and where?
\vskip0.5in
2) (10 points) 
X. 
\hfil\break
What is the purpose of the XF86Config file?
\vskip0.5in
What does Superprobe do that might help you set up
the XF86Config file correctly?
\vskip0.7in
3) (10 points) 
Installing Linux. 
\hfil\break
Describe the missing steps to install Linux. 
Do not describe how to use the script.
Describe the steps that behind the script (i.e., the steps the actions
that the script does).
Step one (given for you so your don't repeat) boot Linux from the floppies.
Step two login as root.
(Missing steps to be filled in).
Step $n-2$ copy the appropriate disks sets from the source CD into the 
appropriate partitions of the hard drive.
Step $n-1$ install lilo on the new hard drive.
Step $n$ configure the new system (fstab, route tables,...)
Just fill in steps 3..$n-3$ by describing the commands you use (in the order
you would use them).
\vfill\eject
4) (10 points) 
Networking. 
\hfil\break
What is the purpose of the /etc/hosts file?
\vskip0.5in
There are two other ways/methods that fulfill the same purpose as the
hosts file, what are they?
\vskip0.5in
What is the purpose of the resolv.conf file?
\vskip0.5in
For a machine with an IP address of 134.139.136.130 and a netmask of 
255.255.255.192, give the cable number and the broadcast address.
\vskip0.8in
What command can you use to locate the hardware address of an ethernetcard?
\vskip0.5in
5) (10 points) 
Network File System. 
\hfil\break
When you use NFS the machine making the disk avaible
makes an entry in a file. 
What is the name of that file?
\vskip0.5in
Give a sample entry for that file?
\vskip0.5in
When you use NFS (Network File System) the machine using a remote disk 
makes an entry in a file. 
What is the name of that file?
\vskip0.5in
Give a sample entry for that file?
\vskip0.5in
6) (10 points) 
Network Information System.
\hfil\break
You are a NIS client and wish to use NIS to manage which users can login.
What file do you need to change?
\vskip0.5in
What entry do you need to make there?
\vskip0.5in
\vfill\eject
7) (10 points) 
Mail. 
\hfil\break
What happens mail sent from the address:
\hfill\break
{\ltt{}sam}
\hfill\break
is processed using the following two lines:

{\program
DM cecs.csulb.edu
R$+ $1 < @ $M >
\endprogram}
\vskip0.5in
If those two lines existed, what file would they be found in?
\vskip0.5in
8) (10 points) 
News. 
\hfil\break
What is the purpose of the file {\ltt{}nnrp.access}?
\vskip0.5in
What is the purpose of the file {\ltt{}newsfeeds}?
\vskip0.5in
9) (10 points) 
Ftp. 
\hfil\break
What is does the {\ltt{}chroot} command do?
\vskip0.5in
Under what circumstance does {\ltt{}ftpd} use the {\ltt{}chroot} command?
\vskip0.5in
For what reason does {\ltt{}ftpd} use the {\ltt{}chroot} command?
\vskip0.5in
10) (10 points) 
http. 
\hfil\break
You wish to place the http configuration file in {\ltt{}/etc/httpd};
give the command for starting the server (use port 80).
\vskip0.5in
You wish to keep the error and log files in the {\ltt{}/etc//httpd}
directory; show the contents of the configuration file
\bye
