\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Fall 1998, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook.

In general, if you are asked how to do something,
give file names and contents; or explicit versions of commands.

\ques
(4 points)
You wish to allow printing the the printer on unix67.cecs.csulb.edu.
Unix67 calls the printer {\ltt{}lj}.
You do not want to remove the capability to print to the jaguar printer.
What do you need to do to your machine (give file and directory names and 
contents).
\vskip 2.5in
\ques
(4 points)
You add a second drive to your system.
You wish to use the first 100 cylinders for a swap partition and the
rest (100-601) for a linux partition.
What do you need to do to correctly partition the disk. 
(Don't set up the file system of the swap, you did that on the midterm.)
\vskip 2.5in
\ques
(4 points)
What are {\ltt{}aha1740.s} and {\ltt{}fdomain.s} and how do they differ?
\vskip 1.0in
\ques
(4 points)
What is the difference between the A disk set and the N disk set.
\vfill\eject
\ques
(4 points)
When installing Linux,
what things do you do during the netconfig portion of the install
\vskip 1.0in
\ques
(4 points)
You want to clear everything out the {\ltt{}/tmp} directory at 2am
every day.
Describe the command and give the entry you make in the table.
\vskip 1.0in
\ques
(4 points)
I want to issue a mail messages 8 hours from now. The message
is in a file called {\ltt{}message.txt}
(Mail can take input from a file using the standard redirect input operator.)
What command do I issue? (Give the exact form.)
\vskip 0.7in
\ques
(4 points)
What is ``chord middle"?
\vskip 0.7in
\ques
(4 points)
How do you find out how much RAM is on your video card?
\vskip 0.7in
\ques
(4 points)
You wish to modify your system so that all return addresses
are rewritten to be {\ltt{}smtp.csulb.edu},
except for mail that is from the user {\ltt{}joe} (which should not have 
its return address rewritten);
how do you do this?
\vskip 1.8in
\ques
(4 points)
What entry do you change in the configuration file to move the
location of where the web server keeps its files?
\vfill\eject
\ques
(4 points)
How do we forward the local.326a news group to {\ltt{}tabloid.csulb.edu}?
\vskip 1.5in
\ques
How do we allow users from {\ltt{}lynx.cecs.csulb.edu} to read the
news that is stored on our machine.
\vskip 1.0in
\ques
(4 points)
What does the {\ltt{}chroot} command do?
\vskip 0.7in
\ques
(4 points)
For maximum security, 
what should be in the file {\ltt{}~ftp/etc/passwd}?
\vskip 0.9in
\ques
(4 points)
You have a lot of configuration files in the {\ltt{}/etc} directory;
how do you save them to floppy?
\vskip 0.7in
\ques
(4 points)
A reboot is considered a kernel notice. You wish information about
any reboots (in the lab) to be send to your office machine 
{\ltt{}netman.cecs.csulb.edu}. How do you do this?
\vfill\eject
\ques
(4 points)
You are only a TA (not the system administrator).
You want students to be able submit their homework to you by
depositing it in your home account's {\ltt{}submitted} directory.
How do you do this?
\vskip 2.5in
\ques
(4 points)
You wish to automount {\ltt{}/home/sue} from {\ltt{}lab76.net.cecs.csulb.edu}.
What file must be modified and what entry must be made in that file.
\vskip 1.5in
\ques
(4 points)
You wish to distribute the files {\ltt{}.cshrc} and {\ltt{}.login}
to {\ltt{}/home/sue} and {\ltt{}/home/sam}, give the contents
of the distfile.
\vskip 1.5in
\bye
