\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Fall 1999, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook.

\ques
(4 points)
% Project 13
You are instructed to set your machine as an NIS client. (domainname happy,
ypserver 134.139.136.99).  Which the files in the {\ltt{}/etc}
directory will you need to edit, and what you need do to those files?
(Do NOT include files files from {\ltt{}rc.d} in your answer.)
\vskip 1.0in
\ques
(4 points)
% Project 14
Describe how you would
export the {\ltt{}/homes} directory on your machine to all
machines on the 134.139.136.0 cable.
(Tell me the file name and contents)
\vskip 1.0in
\ques
(4 points)
% Project 14
Describe how you would make
the {\ltt{}/homes} directory from {\ltt{}lab85.net.cecs.csulb.edu}
available on your machine when you boot.
(Tell me the file name and contents)
\vskip 1.0in
\ques
(4 points)
% Project 15
Describe how you would make
a printer called {\ltt{}laserjet} on {\ltt{}lab85} available to
users on your machine as the default printer.
(Tell me the file name and contents)
\vskip 1.0in
% \vfill\eject
\ques
(4 points)
% Project 15
Describe how you would have
critical ({\ltt{}crit}) messages (or higher) from {\ltt{}cron}
go into the file {\ltt{}/var/log/cronlog}
and
emergency ({\ltt{}emerg}) messages from the printer subsystem {\ltt{}lpr}
be sent to {\ltt{}lab85}.
\vskip 1.8in
\ques
(4 points)
% Project 16
Describe how you would build a boot floppy for a machine with a
Sanyo CD-ROM and an IDE hard drive.
Give the exact command, including the name of the source file for
the image.
\vskip 1.0in
\ques
(4 points)
% Project 16
When you boot from floppies you have a choice 
between ``ramdisk" and ``root disk".
What is the difference between these two options?
\vskip 1.0in
\ques
(4 points)
% Project 17
When installing the operating system, 
you want to install networking on your machine.
Which disk set do you need?
\vskip 0.5in
\ques
(4 points)
% Project 17
You installed the web server software but disabled it.
What command did you run to disable this software?
\vskip 0.5in
\ques
(4 points)
% Project 18
Describe how anonymous ftp works.
\vskip 1.0in
\ques
(4 points)
% Project 19
If you are trying to find out what is happening with you mail,
you can use options to mail and sendmail to examine things.
Give the form of the mail and sendmail commands you would use to do this.
\vskip 1.2in
\ques
(4 points)
% Project 19
(Synthesis question, are you familiar enough with sendmail so you
know how it would implement this.)
Suppose that the sendmail documentation said that you could
set up a group called {\ltt{}P} and that any mail sent to
accounts in the group {\ltt{}P} would go directly to the printer.
Suppose you wanted mail for the accounts {\ltt{}lp} and {\ltt{}news}
to go directly to the printer.
What file would you modify and what line would you add?
\vskip 1.0in
\ques
(4 points)
% Project 20
In project 20 you used SUID to add entries to the {\ltt{}datelog} file.
Suppose the {\ltt{}clogit} program and {\ltt{}datelog} file already exist.
Give the commands would you run (exact format) to use SGID (Group)
(instead of SUID) to modify the {\ltt{}datelog} file.
\vfill\eject
\ques
(4 points)
% Project 20
Why are SUID shell scripts not allowed?
\vskip 1.0in
\ques
(4 points)
% Project 21
You wish to forward news posted on your machine to {\ltt{}lab85}.
What do you need to do? (Give file(s) and modifications.)
\vskip 1.0in
\ques
(4 points)
% Project 21
You add a newsgroup called {\ltt{}local.476c}.
What do you need to do? (Do not use {\ltt{}ctlinnd}, tell me the
steps you would need would perform, to do it by hand. 
Give file(s), directories and modifications.)
\vskip 1.5in
\ques
(4 points)
% Project 22
You want all web documents to be in {\ltt{}/var/web}.
How do you set up {\ltt{}httpd.conf} so it looks in that directory first?
\vskip 1.0in
\ques
(4 points)
% Project 22
You want all directories not inside {\ltt{}/var/web} to be inaccessible to the
web browers.
What to you put in {\ltt{}httpd.conf}.
\vfill\eject
\ques
(4 points)
% Project 23
You have two machines for which you supply name service.
{\ltt{}joe.univ.edu} (137.199.1.1) and {\ltt{}sam.univ.edu} (137.199.1.1).
Give the zone entries (only zone entries) of the {\ltt{}named.conf}
for your DNS server.
\vfill
\ques
(4 points)
% Project 23
Give the forward zone file for the above question. (Include the SOA).
\vfill
\ques
(4 points)
% Project 24
You wish to allow user {\ltt{}sam} on {\ltt{}jaguar.cecs.csulb.edu}
to put files onto your web server (user {\ltt{}www} on 
{\ltt{}www.cecs.csulb.edu}). (Assume the software to do this has
already been installed, i.e., don't show a ``tar".)
What do you do?
\vskip 0.7in\eject
\ques
(4 points)
% Project 24
Sam wishes to put a file called {\ltt{}newindex.html} from his home directory
onto {\ltt{}~www/htdocs}, call it {\ltt{}index.html} and have its
permissions be {\ltt{}6400}. What does sam do?
\vskip 3.0in
\ques
(4 points)
% Project 25
What command would you give to index all files in you {\ltt{}~ftp/pub}
directory?
\vskip 0.5in
Analysis section. Assume that the instructor as a part of this exam
has partially disabled the machine you administer in the lab.

\ques
(4 points)
Suppose the following work:

{\program
 ping 134.139.136.85
 ping 134.139.136.65
\endprogram}

and the following fails:

{\program
 ping 134.139.45.6
\endprogram}

What could be misconfigured on the machine?
\vskip 1.0in
\ques
(4 points)
Assume you fix the above problem and the instructor disables your machine
again.

Suppose root and {\ltt{}john} can login, but neither you
nor any other {\ltt{}csv...} account can.
What could be misconfigured on the machine?
\bye
