\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2005, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open book, open notebook. (All question 8 points, 96 total points possible)
\hfill\break
\ques
% Homework 3
The user {\ltt{}joe} has  a home directory of {\ltt{}/home/joe},
a shell of {\ltt{}/bin/bash}, a user number of {\ltt{}12345}
and a base group of {\ltt{}111}
Give the {\ltt{}/etc/passwd} entry for {\ltt{}joe}
\vskip 0.4in
How would you make {\ltt{}sam} own his home directory.
\vskip 0.4in
\ques
% Homework 5
Give the command to build an Linux ext2 file system on {\ltt{}/dev/hda3}.
\vskip 0.5in
Give the name of the file and the exact line that needs to be in that file to
have the file system on {\ltt{}/dev/hda3} attached to the directory trees
as {\ltt{}/var/log}.
\vskip 0.5in
What command do you use to set up the partitions on a disk?
\vskip 0.4in
\ques
% Homework 9
Give the steps to build a kernel.
\vskip 2.0in
You have a two versions of Linux installed, one on {\ltt{}/dev/hda1}
and the other on {\ltt{}/dev/hdc2}; both call their kernel {\ltt{}vmlinuz}.
Give the exact contents of your {\ltt{}lilo.conf}.
\vskip 1.8in
\vfill\eject
\ques
% Homework 10
Give the exact command to extract the {\ltt{}/xfer/gcc.tar} command,
preserving permissions.
\vskip 0.4in
How would you make control-Y be the command that terminates ({\ltt{}intr})
a running program?
\vskip 0.4in
\ques
% Homework 7
You want Alt-F7 on your Linux box to open up a 7th login window (6 isn't enough).
What file do you need to change? Give the exact command to activate this change.
\vskip 0.8in
You want to backup the {\ltt{}/home} directory to floppy at 11:30 this evening
(You won't be there then so you have to automate this.)
Describe how to do this; give exact file name, file contents and command.
\vskip 1.2in
A system administrator wants the machines in a lab to reboot {\it every} morning
at 2AM.
How is this done? Give file name, file contents and command.
\vskip 1.4in
\ques
% Homework 2
Give a sample {\ltt{}/etc/shadow} entry for a user called {\ltt{}joe} and give an
explanation of the first three fields of that entry.
\vskip 1.5in
Each user has a path. What does this path do and how is it set?
\vskip 1.0in
How are groups given names?
\vskip 0.5in
\vfill\eject
\ques
% Homework 4
Write a script that counts the number of device interfaces in {\ltt{}dev}
that contain the letters ``{\ltt{}tty}".
\vskip 0.8in
\ques
% Homework 12
Describe how to allow telnets only from {\ltt{}panther}.
\vskip 0.9in
Describe how to allow rlogins to {\ltt{}bob} from {\ltt{}joe@cheetah}.
\vskip 1.1in
Your IP number is 192.168.1.2 and netmask is 255.255.255.0;
give the exact {\ltt{}ifconfig} command you need.
\vskip 0.4in
Your default (and only) gateway is 192.168.1.1;
give the exact {\ltt{}route} command you need.
\vskip 0.4in
\ques
% Homework 8
How can you find out what kind of video card is in {\it your} machine?
\vskip 1.6in
How would you make the 1024x768 screen resolution the default
for your X11 window system?
\vskip 1.2in
\vfill\eject
\ques
% Homework 6
Give the exact commands to set up a 1MB swap file called {\ltt{}/swaps/swap1}?
\vskip 1.5in
\ques
% Homework 1
\hfill\break
Give a {\it command} that would locate the passwd command and the
manual entries for that command.
\vskip 0.4in
How would you find a command that would allow you to access the USB port?
\vskip 0.4in
In what {\it directory} would you most likely find
the following files:
\hfill\break
A) System Administration programs:
\vskip 0.2in
B) Configuration files:
\vskip 0.2in
C) Files related to booting the machine:
\vskip 0.2in
D) Information about the windows system configuration:
\vskip 0.2in
\ques
% Homework 11
Give the command you would use to find out
the hardware (MAC) address of your network card?
\vskip 0.4in
Describe the contents of the {\ltt{}resolv.conf} file.
\vskip 1.2in
A machine knows about two gateways, one to cable {\ltt{}192.168.4.0}
with a netmask of {\ltt{}255.255.255.0}, the other to the
rest of the network.
Give the entire routing table for this machine.
\vskip 2.0in
\bye
