\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Fall 2003, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open book, open notebook. (All question 8 points, 96 total points possible)

\ques
% Homework 10
Give the exact command to extract the contents of a floppy that
contains a compressed tar image.
\vskip 0.5in
You want the control-W to erase ({\ltt{}erase}) everything you have typed on
the command line.
Give the exact command to do this.
\vskip 0.5in
\ques
% Homework 8
How do you configure the X window system?
\vskip 1.0in
How would you find out what type of video card you have?
\vskip 1.0in
\ques
% Homework 9
What does ``{\ltt{}make bzImage}" do?
\vskip 1.0in
You have installed Linux on {\ltt{}/dev/hdb2} and called the
kernel {\ltt{}myzImage}. Give the lines in {\ltt{}lilo.conf} that
allow you to boot this partition.
\vskip 1.8in
\vfill\eject
\ques
% Homework 6
What is ment by ``short term load"?
\vskip 0.7in
What command would you use to find out how much memory is in use
on your system?
\vskip 0.5in
What command would you use to find out turn on swapping
on the swap partition on {\ltt{}/dev/hda3}.
\vskip 0.5in
\ques
% Homework 2
You want to run the files in {\ltt{}/usr/lib/yp} without
having to type {\ltt{}/usr/lib/yp} every time.
What file would you change and what would you change in that file?
\vskip 0.8in
How could tell if the {\ltt{}bob} account was using the shadow file
for its password?
\vskip 0.5in
How would you count the number of groups on your machine
that have been given local names?
(Give the exact command to do this.)
\vskip 0.5in
\ques
% Homework 13
What line needs to be in what file if you want to use NIS
for the list of the user accounts?
\vskip 0.5in
How would you get the NIS information for the user
csc476zz?
\vskip 0.5in
How would you specify what machine your NIS information comes from?
(Give a file, and contents.)
\vskip 0.5in
\ques
% Homework 4
Write a script that counts the number of names in the yp password map.
\vfill\eject
\ques
% Homework 12
Give the exact command to configure the network card on the machine
that {\it you} administer.
\vskip 0.5in
What command would you use to set up your machine so
it can get through the gateway to the rest of the net?
(Assume you network interface is already configured correctly.)
\vskip 0.5in
Describe how {\ltt{}.rhosts} works.
\vskip 1.0in
Explain how {\ltt{}host.allow} and {\ltt{}host.deny} work.
\vskip 1.0in
\ques
% Homework 7
You which to change from using {\ltt{}agetty} to using {\ltt{}mingetty}.
What file will you need to modify?
\vskip 0.5in
Give the cron entry to run a command file called {\ltt{}/usr/adm/weekly}
at 2:30am every Saturday morning.
\vskip 0.5in
Give the at command to run a command file called {\ltt{}cleansys}
at 11:00pm this evening.
\vskip 0.5in
\ques
% Homework 5
How do you fix inconsistencies in the ext2 file system on {\ltt{}/dev/hda3}.
(Give the exact command.)
\vskip 0.6in

Show the {\ltt{}fstab} entry that would cause
{\ltt{}/dev/hdd2} to be mounted as {\ltt{}/home} when the system boots.
\vskip 0.6in
What does the {\ltt{}fdisk} command allow you to do?
\vskip 1.2in
\vfill\eject
\ques
% Homework 1
In what directory would you look to find out if your system is configured
to support a fourth disk drive (hdd)?
\vskip 0.5in
How would you find out which directory the {\ltt{}mk2efs} command is 
located in?
\vskip 0.5in
In what directory would you look to find out when the kernel you are
running was built?
\vskip 0.5in
\ques
% Homework 11
What is found in the arp table?
\vskip 0.8in
What is found in {\ltt{}/usr/sys/linux/drivers/net}?
\vskip 0.8in
What command would you use to find out the internet number
of your machine?
\vskip 0.5in
\ques
% Homework 3
Give the steps to set up an account for {\ltt{}bob}.
\vskip 2.0in
\bye
