\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2004, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open book, open notebook. (All question 8 points, 96 total points possible)

\ques
% Homework 10
Give the exact command to backup bob's home directory
to floppy.
\vskip 0.5in
When you need to halt ({\ltt{}intr}) a run-away program
you want to use control-W (instead of control-C).
Give the exact command to do this.
\vskip 0.5in
\ques
% Homework 8
What line in {\ltt{}XF86Config} tells X what
type of mouse you have?
\vskip 0.5in
How would you find out how much memory you have on your video card?
\vskip 1.5in
\ques
% Homework 9
Give the steps to build a kernel.
\vskip 1.5in
You have a single kernel ({\ltt{}bzImage}) installed on {\ltt{}/dev/hda2}
Give the exact contents of your {\ltt{}lilo.conf}.
\vskip 1.8in
\vfill\eject
\ques
% Homework 6
Give the command to set up a swap structure in {\ltt{}/dev/hdb2}.
\vskip 0.5in
What command would you use to find out how much swap space is in use
on your system?
\vskip 0.5in
Give the {\ltt{}fstab} entry that would be associated with
{\ltt{}/dev/hdb2} being a swap partition.
\vskip 0.5in
\ques
% Homework 2
The home directory for {\ltt{}bob} is {\ltt{}/bin/csh};
what is wrong and in what file is the error?
\vskip 1.2in
You want to alias {\ltt{}x} so that it does a "{\ltt{}ps aux | grep csh}"
What file do you need to modify to establish this alias.
\vskip 0.5in
Why does {\ltt{}root} have to type {\ltt{}./cpeek} instead
of simply {\ltt{}cpeek}?
\vskip 0.5in
\ques
% Homework 1
Your {\ltt{}inetd} is having problems;
in what directory would you look for messages about those problems.
\vskip 0.5in
In what directory would you look to find which devices the kernel you are
running supports?
\vskip 0.5in
\ques
% Homework 4
Write a script that counts the number of running processes
that contain the letters {\ltt{}rpc}.
\vfill\eject
\ques
% Homework 12
You don't want people from {\ltt{}server.hacker.com} to
be able to telnet to your machine. What do you do?
(Give file and contents.)
\vskip 0.9in
Describe how {\ltt{}hosts.equiv} works.
\vskip 1.1in
Your IP number is 134.139.248.99 and netmask is 255.255.255.192;
give the exact {\ltt{}ifconfig} command you need.
\vskip 0.5in
Your default (and only) gateway is 134.139.248.103;
give the exact {\ltt{}route} command you need.
\vskip 0.5in
\ques
% Homework 5
Give the command to build a file system on {\ltt{}/dev/hdb1}.
\vskip 0.6in
Give the command to run a file system check on {\ltt{}/dev/hdb1}.
\vskip 0.6in
Give the command and the exact steps within that command to
partition{\ltt{}/dev/hdb} into cylinder 1-100 for Linux and 101-120
for swap.
\vskip 1.6in
\vfill\eject
\ques
% Homework 7
You are instructed to have your machine reboot every morning
at 1am (to clean our old CECS 472 servers);
how would you do this? (Give command, and contents/entries.)
\vskip 1.2in
Give the command to run a script called {\ltt{}backup}
20 minutes from now.
\vskip 0.5in
What file controls the behavior of the control-alt-del
keystroke?
\vskip 0.5in
\ques
How would you find out what options are available for
the {\ltt{}wc} command.
\vskip 0.5in
% Homework 11
How do you find out the official fully-qualified hostname of your machine?
(Give the exact command with options.)
\vskip 0.5in
What does your {\ltt{}/etc/resolv.conf} file do?
\vskip 1.2in
Given the following route table circle the entry
that provides access to 134.139.240.8?
\vskip 0.5in
\ques
% Homework 3
Give the steps to set up an account for {\ltt{}joe}.
As part of your description, give the exact line that you would
place in the {\ltt{}passwd} file. (Joe's user ID is 11011
and his group is 233.)
\vskip 2.0in
\bye
