\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Fall 2004, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open book, open notebook. (All question 8 points, 96 total points possible)
\hfill\break
\ques
% Homework 3
The user {\ltt{}sam} has  a home directory of {\ltt{}/home/sam},
a shell of {\ltt{}/bin/tcsh}, a user number of {\ltt{}555}
and a base group of {\ltt{}107}
Give the {\ltt{}passwd} entry for {\ltt{}sam}
\vskip 1.0in
\ques
% Homework 8
What was the mouse protocol for {\it your} machine?
\vskip 0.4in
How do you switch resolutions when in X11?
\vskip 0.5in
\ques
% Homework 9
Give the steps to build a kernel.
\vskip 2.0in
You have a single kernel ({\ltt{}vmlinuz}) installed on {\ltt{}/dev/hda1}
Give the exact contents of your {\ltt{}lilo.conf}.
\vskip 1.8in
\vfill\eject
\ques
% Homework 7
Every hour the {\ltt{}/usr/bin/w} command is used on cheetah to automatically
appends a list of who is logged 
to a file called {\ltt{}/var/log/list}.
How is this done? Give file name, file contents and command.
\vskip 1.0in
You want to recompile your Kernel at 11:30 this evening;
(after you leave so it won't slow your machine down while
you are using it.)
Describe how to do this; give exact file name, file contents and command.
\vskip 1.2in
You want your Linux box to boot up to the X-Windows login interface
(instead of a command line login).
This requires a change in the default run level to 4.
What file do you need to change?
\vskip 0.5in
\ques
% Homework 2
Group number {\ltt{}555} is to be named {\ltt{}tutor}; what
line would need to be in what file?
\vskip 1.0in
Build an {\it alias} that reports the files in {\ltt{}/etc} sorted by the
time they were changed. State what file you would place that alias
in.
\vskip 0.5in
Why does {\ltt{}root} have to type {\ltt{}./cpeek} instead
of simply {\ltt{}cpeek}?
\vskip 0.5in
\ques
% Homework 1
File System Organization.
\hfill\break
Give a {\it command} that could be used to exactly locate the
{\ltt{}ls} command.
\vskip 0.4in
In what {\it directory} would you most likely find
the following files:
\hfill\break
A) Log files:
\vskip 0.2in
B) Configuration files:
\vskip 0.2in
C) An executable (such as {\ltt{}ls}):
\vskip 0.2in
D) The interface to the SCSI disk drivers:
\vskip 0.2in
E) The file systems (dos,ext2) that are supported by the kernel:
\vskip 0.2in
\vfill\eject
\ques
% Homework 4
Write a script that counts the users in the password file
and appends that number to a file called {\ltt{}UserCounts}.
\vskip 1.0in
\ques
% Homework 12
Describe how {\ltt{}.rhosts} works.
\vskip 0.9in
Describe how {\ltt{}hosts.equiv} works.
\vskip 1.1in
Your IP number is 134.139.42.33 and netmask is 255.255.255.128;
give the exact {\ltt{}ifconfig} command you need.
\vskip 0.4in
Your default (and only) gateway is 134.139.42.1;
give the exact {\ltt{}route} command you need.
\vskip 0.4in
\ques
% Homework 5
Give the command to build an Linux ext2 file system on {\ltt{}/dev/hdb2}.
\vskip 0.6in
Give the name of the file and the exact line that needs to be in that file to
have the file system on {\ltt{}/dev/hdb2} attached to the directory trees
as {\ltt{}/disk3}.
\vskip 0.6in
How would you modify the partition table so that {\ltt{}/dev/hdb1} was
a Linux swap partition.
Give the command and the exact steps within that command.
\vskip 1.6in
\vfill\eject
\ques
% Homework 6
Give the steps to set up swapping structure on {\ltt{}/dev/hdb1}
including getting it to turn automatically at boot.
\vskip 1.5in
\ques
% Homework 11
You want only local accounts (no network {\lt{}csa..} accounts) to be
able to login to your machine.
What file do you change, what change do you make?
\vskip 0.5in
You want short hand references for names, such as
{\ltt{}lab17} instead of {\ltt{}lab17.net.cecs.csulb.edu}.
Given an English sentence, that includes the name of the
file and clearly defines which line needs to be present.
\vskip 1.2in
Give the entry in the route table that describes the cable
your machine is attached to.
\vskip 0.5in
\ques
% Homework 10
Give the exact command to backup bob's home directory
to floppy.
\vskip 0.4in
Your assistant is writting a program that needs to detect
when the user presses the home key on the Linux console
keyboard.
As the system administrator; you need to tell the programmer
what to look for.
(Hint: kh stands for cursor home key.)
You must tell your assistant {\it how}  to find out the information?
Give an English paragraph containing the instructions you would
give to your assistant.
\vskip 1.5in
\bye
