\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2000, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open book, open notebook.

\ques
(8 points)
You want to check how the kernel configured your cpu.
In what directory would you look?
\vskip 0.5in
How would you find out if your system is configured to use
the serial port or the PS/2 port for it's mouse?
(Give the shell command you would use to do this.)  
\vskip 0.5in
What command would you run to find out the directory
that the {\ltt{}xf86config} program was in.
\vskip 0.5in
\ques
(8 points)
How would you find out when the user {\ltt{}bob} last changed his password.
\vskip 0.5in
User {\ltt{}sue} complains that {\ltt{}startx} doesn't work
(command not found). 
Neither do any of the other X commands.
What do you do to the {\ltt{}sue} account to fix this?
\vskip 1.8in
\ques
(8 points)
User {\ltt{}bob} switches from being a graduate student to being 
a faculty member. You need to change his base group.
Describe how you would do this?
\vskip 0.8in
(Because the disk is full)
You need to move user {\ltt{}sue} from {\ltt{}/home/u1} to
{\ltt{}/home/u2}.
(I.e., move the home directory.)
Describe all the steps required to do this?
\vfill\eject
\ques
(8 points)
Write a script that counts the number of {\ltt{}*.gif} files
in {\ltt{}~joe/htdocs} and mails that number to {\ltt{}sam}.
\vskip 2.0in
\ques
(10 points)
Your get a second drive for your system ({\ltt{}hdb}).
Set it up as follows: first partition (cylinders 1-400) is ext2 and
will be attached to your file system as {\ltt{}/morehomes};
the second partition (cylinders 400-450) is a swap partition;
the third partition (cylinders 451-460) is a DOS partition.
Give the commands necessary to do this. 
Be sure to also give the name of the file
you need to edit a file to make the new {\ltt{}ext2} partition
and the new swap space available at boot
and describe what changes you must make to that file.
\vskip 4.0in
\ques
(8 points)
You are trying to run a big program, but you don't have enough swap space.
What commands would you run to set up and use a 16 megabyte swapfile.
(Do not reboot.)
\vfill\eject
\ques
(8 points)
You don't want the ``alt-F2"...``alt-F6" virtual terminals available
as ``logins" on your machine.
What file do you need to change.
\vskip 0.5in
Describe how you would make a backup of your entire {\ltt{}home} directory
to floppy every Monday morning at 2am.
\vskip 1.5in
\ques
(8 points)
Everytime you run X it starts up in 640x480 mode and you need to
{\ltt{}ctrl-alt-+} to get to the 1024x768 mode you want.
What file should you change and what change should you make
to get X to start in 1024x768 mode?
\vskip 1.5in
\ques
(8 points)
You first attempt at a new kernel has a minor flaw
(Suppose it's something like ``nfs file type not found" although the exact
error does not matter for this question.)
What steps do you take to build a slightly modified version of your kernel.
rebuild Linux on a {\it alpha} system (instead of on an {\it Intel}).
Where should you look for the kernel?
\vskip 1.4in
How do you make Linux have the following behavior at boot:
wait 5 seconds at the boot prompt.
if linux is chosen, boot linux ({\ltt{}hdb1}),
if win is chosen, boot windows ({\ltt{}hda1}),
if 5 seconds passes, boot windows.
Give file name, contents of that file and command to install
this boot sequence.
\vfill\eject
\ques
(8 points)
You have used ftp to get a new compiler.
The file is called {\ltt{}java_2_1.tgz}.
How would you install this new software.
\vskip 0.8in
You login to jaguar and it says ``Terminal type Linux not found".
What file would you need to upgrade?
\vskip 0.4in
You want control-y to terminate your programs (instead of control-c).
What command do you issue to do this?
\vskip 0.4in
\ques
(8 points)
How would you examine the arp table?
\vskip 0.5in
You want your DNS server to be ({\ltt{}192.168.4.15}).
in case that server is off-line you want to use the
DNS server {\ltt{}192.168.2.1}.
Give the exact contents of the {\ltt{}resolv.conf} file that will do this.
\vskip 1.2in
\ques
(10 points)
(Netmask for this question is {\ltt{}255.255.255.192}) 
\hfill
\break
Your network administrator changes your gateway to {\ltt{}192.168.1.4}
What command do you give to make this adjustment (without rebooting).
\vskip 0.5in
Your network administrator changes the IP number assigned to your
machine to {\ltt{}192.168.1.13}
What command do you give to make this adjustment (without rebooting).
\vskip 0.5in
Your network administrator directs you to shut down the remote finger
service on your machine.
What do you change and in what file?
What program do you need to ``HUP" to make this effective?
\vskip 0.5in
Your network administrator directs you to allow rlogins only
from subnet {\ltt{}192.168.0.0/255.255.0.0}.
What two files do you change and what do you put in each file?
(If you not know the exact name of the rlogin service,
you may tell me which file you can look in to find out the exact name.)
\bye
