\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Fall 2000, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open book, open notebook.

\ques
(8 points)
Give the exact command would you run to find out the block size of the Linux
partition on {\ltt{}/dev/hda3}.
\vskip 1.0in
Give the command you would use to find out how much swap space is in use.
\vskip 0.8in
\ques
(8 points)
How would you find out the UID of the user {\ltt{}bob}.
\vskip 0.5in
Given the following output of ls:
\hfill\break
{\ltt{}rwxrwx---  root printmaster   updatepaper}
\hfill\break
How would you add {\ltt{}sam} and {\ltt{}bob} to the set of users who
can run the {\ltt{}updatepaper} program?
(What change do you make and to what file?)
\vskip 1.0in
\ques
(10 points)
Write a script that counts the number of {\ltt{}agetty} programs running
and appends that number to a file called {\ltt{}agettylog}.
\vfill\eject
\ques
(8 points)
Who should own the home directory of the user {\ltt{}bob}?
\vskip 0.8in
The user {\ltt{}sue} wishes to use the {\ltt{}ksh} shell instead of 
the {\ltt{}csh} shell.
What file do you need to change?
\vskip 0.8in
\ques
(8 points)
Exactly what command would you uset to set up a Linux files system on the
{\ltt{}/dev/hdb1} partition (assuming the partition table is already
correctly configured).
\vskip 0.8in
What file would you change and what change would you make to
have the above partition automatically mounted at boot time?
\vskip 1.0in
If the Linux file system on {\ltt{}/dev/hdb1} has errors,
what is the exact command you would give to fix it?
\vskip 1.0in
\ques
(8 points)
What file would you need to change if you wanted to attach
a terminal to your serial port?
\vskip 0.5in
Describe how you would clean (remove the contents of) the {\ltt{}/tmp}
directory every night at 11pm.
\vfill\eject
\ques
(8 points)
Your tape drive is {\ltt{}/dev/st0}.
Give the exact command to backup your entire (main) disk to that tape.
\vskip 0.5in
Your telnet window has 40 lines, your telnet client forgot to
tell Linux so it thinks you have 24.
Give the command to tell linux that you have 40 columns ({\ltt{}rows})
in your telnet window.
\vskip 0.5in
\ques
(8 points)
Give the exact command you would use if you wanted to find out 
information about your video card.
\vskip 0.5in
Give the exact command you would use if you wanted to find check 
your X configuration.
\vskip 0.5in
What is a ``modeline".
\vskip 0.5in
\ques
(8 points)
Give the 3 steps (commands used) in building a kernel.
\vskip 0.8in
Exactly what is found in {\ltt{}/proc/sys/kernel/version}?
\vskip 0.8in
How would you make Linux boot the {\ltt{}/dev/hda3} partition
instead of {\ltt{}/dev/hda1}?
(Give the file, the change and the command to activate the change.)
\vfill\eject
\ques
(8 points)
You want to know what file systems your kernel supports.
In what directory would you look?
\vskip 0.5in
You are looking for the configuration file for attaching your machine
to a UPS (Uninterruptible Power Supply).
In what directory would you look?
\vskip 0.5in
What command would you run to find out the name and locations
of files associated with the {\ltt{}mail}.
\vskip 0.5in
\ques
(8 points)
How would you find out which machine is your DNS server?
\vskip 0.5in
You want your hostname look-ups to use the DNS server and
to use the local files only if the DNS server can't find the name.
Give the exact line needed in the {\ltt{}nsswitch.conf} to do this.
\vskip 0.5in
\ques
(10 points)
Your gateway is changed to {\ltt{}134.139.136.99} (assuming you are
on that cable).
What command do you need to tell your machine to use this gateway?
\vskip 0.5in
Describe how would you set up your {\ltt{}csv476xx} account to allow rlogins
to the machine you administer from {\ltt{}cheetah} without a password.
\vskip 1.5in
Give the files and exactly what needs to be in them to prevent rlogins
from all machines in the domain {\ltt{}cecs.csulb.edu} except for
{\ltt{}cheetah.cecs.csulb.edu}.
\bye
