\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2001, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open book, open notebook.

\ques
(8 points)
% Homework 6
What command would you use to configure {\ltt{}/dev/hdb2} as swap space?
\vskip 0.8in
What command would you run to find the number of block groups
in the Linux partition on {\ltt{}/dev/hdb1}.
\vskip 0.8in
\ques
(8 points)
% Homework 2
How would you find out the {\it name} of group that the user 
{\ltt{}joe} belongs to?
\vskip 1.5in
What file are the encrypted passwords kept in?
\vskip 0.5in
\ques
(10 points)
% Homework 4
Write a script that lists all the files in the current directory
that are owned by the user {\ltt{}joe}.
\vfill\eject
\ques
(8 points)
% Homework 3
What file defines where the home directory of the user {\ltt{}joe} is?
\vskip 0.8in
How would you change the floppy drive so it is owned by the 
user {\ltt{}sue}?
(Give the exact command.)
\vskip 0.8in
\ques
(8 points)
% Homework 5
What file would you change and what change would you make to
if you wanted a user to be able to mount an ATAP-2 cdrom?
(device is {\ltt{}/dev/hdc}, file system type is {\ltt{}iso9660})
\vskip 0.8in
Exactly what command would you uset to set up a Linux files system on the
{\ltt{}/dev/hda3} partition (assuming the partition table is already
correctly configured).
\vskip 0.8in
What is the condition that should be met before running {\ltt{}fsck}?
\vskip 0.8in
\ques
(8 points)
% Homework 7
What file do you need to change if you wanted to disable the
control-alt-del reboot capability?
\vskip 0.5in
Every week (1 AM. on Sunday) you want to move the {\ltt{}/var/log/messages}
file to {\ltt{}/var/log/messages.bak}
Describe how you do this?
\vfill\eject
\ques
(8 points)
% Homework 10
You wish to create a compressed tar archive file 
(called {\ltt{}homework.tgz})
of the directory {\ltt{}/home/bob/homework}.
Give the exact command to do this.
\vskip 0.5in
You want to set up your login so control-y redraws (reprints)
your command line ({\ltt{}rprnt}).
What command do you issue to do this?
\vskip 0.5in
\ques
(8 points)
% Homework 8
What file and what change would you make to have the first choice
of resoultion be 800x600 when you are running X.
\vskip 0.8in
Give the exact command you would use if you wanted to find out 
information about your video card.
\vskip 0.5in
What does {\ltt{}X -probeonly} do?
\vskip 0.8in
\ques
(8 points)
% Homework 9
You want to find out when your kernel was built,
where do you look? (Give the full file name.)
\vskip 0.8in
When did you need to run {\ltt{}make dep}?
\vskip 0.8in
How would you make Linux boot the {\ltt{}/dev/hda3} partition
instead of {\ltt{}/dev/hda1}?
(Give the file, the change and the command to activate the change.)
\vfill\eject
\ques
(8 points)
% Homework 1
You want to know your system has support for the sonycd.
In what directory would you look?
\vskip 0.4in
You are looking for the command to configure the sound card.
What steps would you take to find this command?
\vskip 1.0in
You are having a problem with the network. 
You want to check to see if there are any  error messages.
In what directory should you look?
\vskip 0.4in
\ques
(8 points)
% Homework 11
What directory would you look in to find out which
linksys network cards you had drivers for.
Give the full path name starting with the {\ltt{}/}.
\vskip 0.5in
You want to switch your DNS server to be {\ltt{}134.139.4.15},
what file do you change and what change to you make?
\vskip 0.5in
\ques
(10 points)
% Homework 12
Your IP address is changed to {\ltt{}134.139.136.99}.
Exactly what command do you run to make this change?
\vskip 1.0in
You want to allow telnet from {\ltt{}linux7.cecs.csulb.edu} to your machine
(and it is currently disallowed).
What file do you need to change and what change do you need to make?
\vskip 1.0in
You want to completely disable {\ltt{}ftp} on your machine
What file do you need to change and what change do you need to make?
\bye
