\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2003, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open book, open notebook. (All question 8 points, 104 total points possible)

\ques
% Homework 6
How would you find out the amount of CPU time the {\ltt{}inetd}
server has used?
\vskip 0.8in
Give the steps to set up a swap partition on {\ltt{}/dev/hda3}.
\vskip 1.3in
% Homework 2
You want to check when {\ltt{}bob} last changed his password.
How would you do this?
\vskip 1.0in
You want to find out what groups {\ltt{}bob} belongs to.
How would you do this?
\vskip 0.8in
\ques
% Homework 13
How would you get a list of the groups that are 
coming in over the network?
\vskip 0.8in
How would you specify what machine your NIS information comes from?
(Give a file, and contents.)
\vskip 0.5in
\ques
% Homework 4
Write a script that counts the number of {\ltt{}agetty} programs
that are currently running.
\vfill\eject
\ques
% Homework 3
Give the steps to set up an account for {\ltt{}bob}.
\vskip 2.0in
\ques
% Homework 5
How do you find out if the ext2 file system on {\ltt{}/dev/hda3} is
marked clean or dirty?
\vskip 1.0in
Show the {\ltt{}fstab} that would allow the system administrator
to mount a SCSI cdrom {\ltt{}/dev/scd0} on {\ltt{}/cdrom}.
\vskip 0.7in
Give the command to build a Unix file system on {\ltt{}/dev/hda3}.
\vskip 0.7in
\ques
% Homework 7
You want to modify your system so that only one
(instead of the six) virtual terminal is allowed (i.e., only alt-F1 exists).
What file do you need to change?
\vskip 0.5in
You want to build a new kernel at 11:30PM (after the lab closes).
Describe how you do this? (Give files, with exact contents and commands.)
\vfill\eject
\ques
% Homework 10
Give the exact command to 
make a compressed backup of the contents of all files in
{\ltt{}/etc} to a floppy disk.
\vskip 1.0in
You want the key that pauses (suspends) a program ({\ltt{}susp}) to
be control-Y instead of control-Z.
Give the exact command to make this change.
\vskip 0.5in
\ques
% Homework 8
You switch from a PS/2 mouse to a serial mouse.
What changes do you need to make in your system.
(Include any configuration files and links that you would change.)
\vskip 1.1in
How would you find out what type of video card you have?
\vskip 0.7in
\ques
% Homework 9
Give the steps to build (not install) a new kernel.
\vskip 1.8in
You install a (complete) experimental version of Linux into the 
{\ltt{}/dev/hda3} partition. You want do allow a dual boot for your
original ({\ltt{}/dev/hda1}) Linux and the experimental version.
What lines would you have to add to the {\ltt{}lilo.conf} file to do this.
\vfill\eject
\ques
% Homework 1
In what directory would you look to find the configuration file
of your advanced audio system?
\vskip 0.5in
You need examine the output of {\ltt{}inetd},
in what directory would you look?
\vskip 0.5in
You want to know if your kernel supports the reisner file system.
In what directory would you look to find this out?
\vskip 0.5in
\ques
% Homework 11
What does the file {\ltt{}3c503.c} contain?
\vskip 0.5in
Give the exact command you would use to find out
the (internet) name  of your machine.
\vskip 0.5in
How do you find out the netmask on the loopback interface?
\vskip 0.5in
\ques
% Homework 12
Give the exact command to configure the network card on the machine
that {\it you} administer.
\vskip 0.5in
What command would you use to set up your machine so
it can get through the gateway to the rest of the net?
(Assume you network interfaces are already configured correctly.)
\vskip 0.5in
Describ how {\ltt{}hosts.equiv} works.
\vskip 0.5in
\bye
