\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 2002, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open book, open notebook. (All question 8 points, 104 total points possible)

\ques
% Homework 6
What command would you run to get information about {\it{}all}
the processes that are running in the system?
\vskip 0.5in
Assuming {\ltt{}/dev/hdb2} has been configured as swap space,
what entry would you make in {\ltt{}/etc/fstab} to cause that
swap partition to be used (automatically) when your machine boots?
\vskip 0.5in
What command would you run to find out how much swap space
you have and how much you are using?
\vskip 0.5in
\ques
% Homework 2
{\ltt{}bob} wants to set up an alias, what
file does Bob need to modify?
\vskip 0.5in
You wish to move {\ltt{}bob}'s home directory,
in addition to moving the directory,
what file do you need to modify?
\vskip 0.5in
\ques
% Homework 13
You wish to add your machine to the {\ltt{}cecsyp} NIS domain
as a client.
What steps do you need to take?
(Give file names and file contents.)
\vskip 2.0in
\ques
% Homework 4
Write a script that lists all the processes 
that are owned by the user {\ltt{}bob}.
\vfill\eject
\ques
% Homework 3
The {\ltt{}.login} of {\ltt{}bob} is owned by the wrong account.
Give the exact command you can issue to fix this.
\vskip 0.5in
You want to switch {\ltt{}joe} to a group called {\ltt{}oldusers}.
Give the sequence of steps you would need to do this.
\vskip 2.0in
\ques
% Homework 5
You install a new harddrive with a partition
{\ltt{}/dev/hdb1} that you want to make into
a Linux (ext2) partition available as {\ltt{}/disk2}.
What are steps must you take.
\vskip 2.0in
If {\ltt{}/dev/cdrom} is your cdrom drive,
what entry would you make in {\ltt{}/etc/fstab} so that
it could be mounted as {\ltt{}/cdrom}?
\vskip 0.5in
\ques
% Homework 7
You want to add {\ltt{}alt-F7} as a seventh login console.
What file do you need to change?
\vskip 0.5in
You want to run the command {\ltt{}/bin/rm /tmp/*},
but you don't want to do it until 11:30 tonight.
Describe how you do this?
\vfill\eject
\ques
% Homework 10
You wish to move a copy of bob's home directory
from lab89 to lab85.
Describe how you would do this using tar?
\vskip 1.8in
There is a control key that lets you erase a word
on the command line.
How would you find out what that control key is?
(Give the exact command.)
\vskip 0.5in
\ques
% Homework 8
If you wanted to narrow your the size of your X window,
which numbers in the following line would you change?
\break
{\ltt{}ModeLine "800x600"     36     800  824  896 1024   600  601  603  625}
\vskip 0.5in
What will the command {\ltt{}ls -l /dev/mouse} report on
your machine?
\vskip 0.5in
How would you find out the clock rates for your video card?
\vskip 0.8in
\ques
% Homework 9
Give the steps to build (not install) a new kernel.
\vskip 1.8in
Name 3 things that can safely be removed from the standard
network kernel without impairing the ability of your
machine to run.
(Give the file, the change and the command to activate the change.)
\vfill\eject
\ques
% Homework 1
You want to know which types of file systems (ext2, dos,...) your system
is supporting.
In what directory would you look?
\vskip 0.4in
You are looking for the command to configure the USB port.
What steps would you take to find this command?
\vskip 1.0in
You discover the USB port uses a file called {\ltt{}usb.conf},
but they forgot to tell you where to look for it.
In what directory should you look?
(I.e., what would be your first guess?)
\vskip 0.4in
\ques
% Homework 11
Give the exact command you would use to find
out the gateway for your machine.
\vskip 0.5in
Give the exact command you would use to find out
the ethernet address of your network card.
\vskip 0.5in
What file controls whether or not DNS is used to
lookup internet numbers?
\vskip 0.5in
\ques
% Homework 12
What command would you use to set up your machine so
it can get through the gateway to the rest of the net?
(Assume you are already configured correctly to use the
local cable.)
\vskip 0.5in
You want to allow network access to your machine from any
machine on campus (134.139.x.x), but deny it to all other machines.
What files do you need to change and what entries do you need
to make in those files.
\vskip 1.8in
What does the {\ltt{}hosts.equiv} allow you to do.
\vskip 0.8in
\bye
