\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Fall 2002, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open book, open notebook. (All question 8 points, 104 total points possible)

\ques
% Homework 6
How would you find out the resident set size of {\ltt{}rpc.mountd}?
\vskip 0.5in
Give the steps to set up a 4MB swap file.
\vskip 1.5in
% Homework 2
You want to check if {\ltt{}joe} has changed his password recently.
How would you do this?
\vskip 1.2in
A file in bob's home directory belongs to the group {\ltt{}faculty}.
How would you check to see if this is appropriate.
\vskip 0.8in
\ques
% Homework 13
How would you get a list of the accounts whose password information
is coming in over the network?
\vskip 0.5in
How would you determine what machine they were coming from?
(Give a command, not a file name.)
\vskip 0.5in
\ques
% Homework 4
Write a script that counts the number of files in
the home directory of {\ltt{}bob} that are owned by the user
{\ltt{}sue}.
\vfill\eject
\ques
% Homework 3
Give the steps to set up an account for {\ltt{}bob}.
\vskip 2.0in
\ques
% Homework 5
How do you find out the time the last {\ltt{}fsck} was run on {\ltt{}/dev/hda3}?
\vskip 1.0in
Show the {\ltt{}fstab} entry for {\ltt{}/dev/hda3} that would NOT cause
an {\ltt{}fsck} to be done for that partition at boot.
\vskip 0.5in
Give the command to build a Unix files system on a floppy.
\vskip 0.5in
\ques
% Homework 7
You upgrade from {\ltt{}agetty} to {\ltt{}bgetty}
What file do you need to change?
\vskip 0.5in
You want to run the command {\ltt{}/bin/rm /tmp/*},
every morning at 1AM.
Describe how you do this?
\vfill\eject
\ques
% Homework 10
I want to backup the contents of all files on your computer
to the file {\ltt{}!djv/bak.tgz}.
Give the exact {\ltt{}cd} and {\ltt{}tar} commands to do this.
\vskip 1.0in
You want the key that kills a program ({\ltt{}intr}) to
be control-Y instead of control-C.
Give the exact command to make this change.
\vskip 0.5in
\ques
% Homework 8
In what section of the {\ltt{}XF86Config} file is
your mouse protocol defined?
\vskip 0.5in
What command would you run to test the {\ltt{}XF86Config} on your machine?
(Do not {\ltt{}startx}.)
\vskip 0.5in
How would you find out the amount of RAM on your video card?
\vskip 0.7in
\ques
% Homework 9
Give the steps to build (not install) a new kernel.
\vskip 1.8in
Name 3 things that can safely be removed from the standard
network kernel without impairing the ability of your
machine to run.
\vfill\eject
\ques
% Homework 1
In what directory  would you look to find out the speed of the
CPU on your machine?
\vskip 0.5in
The manual tells you that the capabilities of an advanced audio card
are accessed through a file called {\ltt{}pcmixer}.
In what directory would you find that file?
\vskip 0.5in
You are looking for the command to configure your GPS card.
How would find that command?
\vskip 0.5in
\ques
% Homework 11
Give the full path to the directory containing the source code for the
drivers for the network cards.
\vskip 0.5in
Give the exact command you would use to find out
the fully qualified domain name ({\ltt{}fqdn}) of your machine.
\vskip 0.5in
How do you find out the netmask on the loopback interface?
\vskip 0.5in
\ques
% Homework 12
What command would you use to set up your machine so
it can get through the gateway to the rest of the net?
(Assume you are already configured correctly to use the
local cable.)
\vskip 0.5in
Give the exact command the network card on the machine
that {\it you} administer.
\vskip 0.5in
Describ how {\ltt{}.rhosts} works.
\vskip 0.5in
\bye
