\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 1997, Final, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notes.

\ques
(15 points)
Thought question (essay): given the following two entries from a password file,
what are the consequences of the two users having the same UID.
\hfill\break
{\ltt{}joe:AaBbddsSinLsg:1001:41:Joe Doe:/home/joe:/bin/csh}
\hfill\break
{\ltt{}sam:BacurwdialKsk:1001:41:Sam Jones:/home/sam:/bin/bash}
\vfill
\ques
(10 points)
If john's home is {\ltt{}/u1/students/john}:
\hfill\break
A) Who should own the directory {\ltt{}/u1/students/john}?
\hfill\break
B) Who should own the directory {\ltt{}/u1/students}?
\vskip 1in
\ques
(10 points)
You have a new gcc compiler. Inside the directory {\ltt{}/usr/gcc}
you untar the compiler source.
The entire rest of the install will be done in that directory.
You want to allow {\ltt{}joe} to work on the new gcc compiler
but you don't want to give joe the root password.
\hfill\break
A) Describe in a short sentence how you do this.
\hfill\break
B) Show the exact command you would use.
\vskip 1.5in
\ques
(10 points)
The machine {\ltt{}jaguar} gets its name (and IP address) changed
to {\ltt{}cheetah}, due to an emergency. 
No changes are made any changes to the printer stuff.
You discover your can no longer print from your lab machine.
Give the file you need to change and the exact new contents.
(When you get to lab you can do this to your machine so you can
print your homework.)
\vskip 0.8in\eject
\ques
(10 points)
The 472 students are working on their next client server projects.
In the morning you check your machine shows an uptime of {\ltt{}2.0 2.0 2.0}.
\hfill\break
A) What do you expect to find?
\hfill\break
B) How would you look for it?
\vskip 2in
\ques
(15 points)
You want to make a tape backup (the tape is {\ltt{}/dev/nrst0}),
but you want it done at 4am when the system is relatively quite.
However, you aren't allowed into the building at 4am.
How can you do this?
Give the exact commands and/or contents of files.
\vskip 2in
\ques
(10 points)
Examine your homework 8.
X ran very slowly mostly due to not enough memory.
On the basis of the information from {\it your} homework assignment:
\hfill\break
A) How much memory would you need to run X?
\hfill\break
B) Justify your answer from the information in your homework assignment.
(That is, tell me what numbers you saw and how you used them to get
your answer in part A).
\hfill\break
C) Tell me what lab machine you did this part of your homework assignment
on. (Yes, your answers will differ somewhat depending on where you did 
the assignment.)
\vfill\eject
\ques
(20 points)
Long question: You get a second hard drive for your lab machine.
You decide to use the entire drive for the home directories of the users.
So you don't conflict with the existing home you will call this
new one {\ltt{}/home2}.
Your hardware technician has just plugged in the drive,
you have just rebooted the machine, there is is {\ltt{}hdb};
you log in as root.
Now, tell me the rest of the commands to set up the disk.
(Do not install any user homes, just set it up to be ready to do so.)
\bye
