\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Fall 1997, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook.

\ques
(15 points)
Users. The user joe reports a problem. When he logs in he gets
a message ``cannot access home directory".
There are a number of things that could have gone wrong.
Give a step-by-step description of what would you examine to trace down this 
problem.
\hfill\break
{\ltt{}joe:AaBbddsSinLsg:1001:41:Joe Doe:/u1/home/joe:/bin/csh}
\vskip 2.5in
\ques
(10 points)
At boot time, you machines freezes up.
Your friendly instructor tells you that this is caused by something in your 
fstab.
He even gives you the following print out of your fstab.
What change do you need to make to fix the freezing up problem?

{\program
/dev/hda1        /        ext2        defaults   1   1
/dev/hda2        swap     swap        defaults   1   1
/dev/hda3        /dos     msdos       defaults   1   1
/dev/fd0         /floppy  ext2        defaults   1   1
none             /proc    proc        defaults   1   1

\endprogram}
\vskip 2in
\ques
(10 points)
Printcap. You want to setup your machine so that the users have a choice
of printing to the cecs1 printer on cheetah.cecs.csulb.edu or the lp0
printer on vec401psvr.cecs.csulb.edu.
Give the printcap file necessary to do this.
\vfill\eject
\ques
(10 points)
You want to save {\ltt{}/home/john} directory to the tape you just put into
the {\ltt{}/dev/rst0} tape drive.
Show the exact commands you would use.
\vskip 2.0in
\ques
(10 points)
The 472 students are working on their latest network project.
Unfortunately they seem to be clogging the system by forgetting
to shutdown their test runs.
To free the system up, you decide you need to kill these processes.
You will be looking for programs called {\ltt{}mutd} that are
not owned by root and are not attached to a terminal.
You will build a command file to do this.
Show the contents of that file.
\vskip 2.5in
\ques
(10 points)
You decide that you need to run the above command file once an hour.
Tell me exactly how you do this, including the contents of any files
and the exact commands you type.
\vfill\eject
\ques
(10 points)
Your instructor gets a couple new machines.
He designates them {\ltt{}134.139.122.3} and {\ltt{}134.139.122.4} and
attaches them to a second interface of the lab88
machine ({\ltt{}134.139.136.88}) (He borrowed the interface which is numbered
{\ltt{}134.139.122.1}, but this number is only important in the next question.)
He asks you to set up the machine you administer so it can send packets to
these new machines.
What do you do?
Give the exact commands.
\vskip 2.5in
\ques
(15 points)
Unfortunately your instructor forgot to configure the interface on lab88.
He gives you the root password and tells you, ``Please get that working,
by the way, it's {\ltt{}eth1}," 
After loggin into lab88 as root, what do you do?
Give the exact commands.
\vskip 2in
\ques
(10 points)
You take charge of a new linux machine.
You are not sure what hardware the machine has.
What do you do? (Opening the case is not an acceptable answer.)
Give the exact command, and tell us what you would look for.
\bye
