\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Fall 1998, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook.

\ques
(8 points)
Add a user: Account name {\ltt{}joe}, primary group {\ltt{}other},
home directory {\ltt{}/u1/homes/joe}.
Describe the steps you need to take to add this user.
Do not use any scripts.
\vskip 3.5in
\ques
(5 points)
You have many Windows NT users, they keep trying to use control-alt-del
to logout. You decide the best solution is to allow them to logout with
this command. Exactly how would you do this?
\vskip 1.2in
\ques
(5 points)
User {\ltt{}sam} wants to know how much disk he is using.
How do you find out? (Give the exact command).
\vskip 0.9in
\ques
(5 points)
You have a bunch of disks, each containing home directories,
{\ltt{}/u1/homes}, {\ltt{}/u2/homes}, ... .
You wish to place a new users ({\ltt{}sue}) home directory on
the disk with the most space.
How do you find the disk with the most space?
\vfill\eject
\ques
(8 points)
Your machine has new (2 Gigabyte) hard drive with 2000 cylinders. 
You are to make two partion on this drive for user home directories
{\ltt{}/homes1} and {\ltt{}/homes2}.
Describe the sequence of commands you would use to partition the drive.
\vskip 3.0in
\ques
(4 points)
Assuming you have successfully partitioned the above drive; give the
commands that you would use to set up file systems in the partitions.
\vskip 1.0in
\ques
(5 points)
You want these drives to mount automatically at boot time.
What file do you change? And what lines to you add to that file?
\vskip 1.2in
\ques
(5 points)
After several months, you have a problem with the file system in the first
partition ({\ltt{}/homes1}). What command do you run to fix that file system?
\vfill\eject
\ques
(8 points)
It's half way through the semester. Your server is very sluggish.
It is running programs at a much slower speed than it should.
What commands would you use to locate the problem.
What would you look for when you ran those commands.
\vskip 2.5in
\ques
(8 points)
You've just downloaded the source for your new Linux 2.0.35 kernel
into {\ltt{}/usr/src/linux}.
It has your long awaited fixes.
You have successfully built the kernel ({\ltt{}make config}, {\ltt{}make dep},
{\ltt{}make zImage}). Now you are ready to try it out.
What do you do to try this new kernel?
\vskip 2.0in
\ques
(4 points)
You are networking a machine. 
Your machine's internet number is {\ltt{}134.139.136.92}.
Give the command to configure the {\ltt{}eth0} interface.
\vskip 0.5in
\ques
(5 points)
On you machine, you default gateway is {\ltt{}134.139.136.99}.
Give the command to configure the default route.
\vfill\eject
\ques
(5 points)
Your DNS server is {\ltt{}134.139.47.130}.
How do you configure DNS to work? Give the name of the file and its contents
\vskip 1.5in
\ques
(5 points)
You want to diable the {\ltt{}ftp} service on your machine.
What do you do? (Give file name and action.)
\vskip 0.8in
\ques
(5 points)
You don't want to allow users from {\ltt{}grimy.net} to telnet into your
machine.
What do you do? (Give file name and contents.)
\vskip 0.9in
\ques
(5 points)
You want to make your {\ltt{}/home2} directory available over the network
to all machines in {\ltt{}cecs}.
What do you do? (Give file name and contents.)
\vskip 0.9in
\ques
(5 points)
You want to use the {\ltt{}/homes3} directory from {\ltt{}lynx.cecs.csulb.edu}.
You create the mount point with the command {\ltt{}mkdir /net/homes3}.
What else do you do? (Give file name and contents.)
\vskip 0.9in
\ques
(5 points)
You add a second machine to your subnet called
{\ltt{}hi2.net99.cecs.csulb.edu} (you already had a 
{\ltt{}hi.net99.cecs.csulb.edu}).
On your DNS server, give the name of the file that needs to be changed 
and the line your would add to that file.
\vfill\eject
\bye
