\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 1999, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook.

\ques
(8 points)
In what directory would you look for the configuration file for the server
that monitors your Uninterruptable Power Supply and 
tells you when the power has gone off?
\vskip 0.5in
In what directory would you look for a program usually used by the system
administrator?
\vskip 0.5in
In what directory would you look if you wanted to examine what PCI devices
the kernel was currently talking to.
\vskip 0.5in
\ques
(8 points)
What is found in the file {\ltt/etc/shadow}?
\vskip 0.5in
You are tired of typing {\ltt{}ps -aux} all the time, you want to be able
to type {\ltt{}pf} instead (because it's shorter). 
What do you have to do to make this happen? (Specify file and changes)
\vskip 1.8in
\ques
(8 points)
Add a user: Account name {\ltt{}george}, primary group {\ltt{}cecsa},
home directory {\ltt{}/homes/george}.
Describe the steps you need to take to add this user.
Do not use any scripts.
\vfill\eject
\ques
(8 points)
Write a script that counts the number of {\ltt{}httpd} programs
running and records that number in a file called {\ltt{}httpd.log}
\vskip 2.8in
\ques
(10 points)
Your second drive does not even have a partition table on it.
Set it up as follows: first partition (cylinders 1-500) is ext2 and
will be attached to your file system as {\ltt{}/morehomes};
the second partition (cylinders 500-564) is a swap partition.
Give the commands necessary to do this. If you need to edit a file,
tell me what changes you would make to that file.
\vskip 3.8in
\ques
(8 points)
(After 2 months) You have a problem because the file system on your
{\ltt{}/morehomes} directory (set up above) has become corrupt.
What commands do you use to fix that file system? (Do not reboot.)
\vfill\eject
\ques
(8 points)
How do you change the system so that when a user types control-alt-del
the message ``This is a Unix machine" is printed. Give the change
and the command needed activate that change.
\vskip 1.0in
You want to clean out the {\ltt{}/tmp} directory every morning at 2am
using the {\ltt{}rm -r /tmp/*} command. How would you do this?
\vskip 2.5in
\ques
(8 points)
You want the default (first) display (under X11) to be at 800x600,
and the secondary display to be 1152x764.
What file would you change, what section in that file and what
would the new line look like?
\vskip 1.0in
\ques
(8 points)
What sequence of commands (3 commands) would be used to build a new kernel.
\vskip 0.4in
You want to be able to test your new kernel, but still be able to
boot the old one (just in case).
What file do you need to change, what do you need to add and
what command do you need to run?
\vfill\eject
\ques
(8 points)
You want to back up everything in your {\ltt{}/morehomes} directory to
your Digital Linear Tape ({\ltt{}/dev/nst1}). What commands do you give?
\vskip 0.8in
Your new keyboard has a little key with a flag on it. You want to be
able to use that key in the editor to jump to the lower right of the
screen. What file would you need to modify?
\vskip 0.4in
You want to set up your login so that control-e erases a word ({\ltt{}werase}).
What command do you issue to do this?
\vskip 0.4in
\ques
(8 points)
You just bought a new 3Com915C network card. On the floppy you got with
it you found a directory called {\ltt{}Linux} and in that directory
a file called {\ltt{}3c915.c}. Where do you put that file?
\vskip 0.5in
You want {\ltt{}astro} ({\ltt{}134.139.4.15}) to be the DNS server for your
machine. What file do you change and what change do you make?
\vskip 1.0in
\ques
(10 points)
You want to set up basic networking on a machine:
IP number {\ltt{}192.168.32.4},
netmask {\ltt{}255.255.255.240}, 
gateway {\ltt{}192.168.32.1}.
Give the sequence of commands to do this.

\bye
