\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Fall 1999, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook.

\ques
(8 points)
You want to know if your system has been setup so that it can
access the SCSI tape drive;
In what directory would you look?
\vskip 0.5in
In what directory would you look if you wanted to know what addresses
your kernel had assigned to the various devices?
\vskip 0.5in
What command would you run if you wanted to find out the directory
that the {\ltt{}xf86config} program was in.
\vskip 0.5in
\ques
(8 points)
How would you find out the Unique ID (UID) number for the user bob?
\vskip 0.5in
You are working alot with the {\ltt{}yp} programs and you are tired of 
having to type the full path name of these programs, 
such as {\ltt{}/usr/lib/yp/ypxfr}.
What do you have to do to be able to use just the name of the command
and not the whole path? (Specify file and changes)
\vskip 1.8in
\ques
(8 points)
User {\ltt{}joe} is unhappy with using {\ltt{}csh} as his shell and wants
to use {\ltt{}bash} as his shell instead.
Describe how you would do this? (not using scripts)
\vskip 0.8in
User {\ltt{}smith} has changed their name to {\ltt{}jones} and needs
to change their login name.
Describe how you would do this?
(Do not move the home directory.)
\vfill\eject
\ques
(8 points)
Write a script that counts the number of processes that {\ltt{}joe}
is running and mails that number to {\ltt{}sam}.
\vskip 2.8in
\ques
(10 points)
Your get a third drive for your system.
Set it up as follows: first partition (cylinders 1-950) is ext2 and
will be attached to your file system as {\ltt{}/u2};
the second partition (cylinders 951-1021) is a swap partition.
Give the commands necessary to do this. Be sure the name of the file
you need to edit a file to make this new disk available at boot
up and tell me what changes you must make to that file.
\vskip 3.8in
\ques
(8 points)
You are trying to run a big program, but you don't have enough swap space.
What commands would you run to set up and use a 16 megabyte swapfile.
(Do not reboot.)
\vfill\eject
\ques
(8 points)
After you have changed the configuration file for {\ltt{}init},
how do you get the {\ltt{}init} process to read the new configuration.
\vskip 0.5in
How you you set up you Linux box to replace your alarm clock?
Do this by having it play the file {\ltt{}wakeup.wav} at 6am
(on weekdays only).
To simplify this assignment, assume you play a wav file by
sending it ({\ltt{}cat} is fine) to the {\ltt{}audio} device.
\vskip 2.5in
\ques
(8 points)
You upgrade from a serial mouse to a PS/2 mouse.
Exactly what in your Linux system need to be changed 
and what changes do you make?
\vskip 1.0in
\ques
(8 points)
You rebuild Linux on a {\it Sparc} system (instead of on an {\it Intel}).
Where should you look for the kernel?
\vskip 0.4in
How do you make Linux have the following behavior at boot:
wait until you have chosen whether to boot Linux from the second
hard drive or Windows from the primary hard drive?
(Assume there is only one partition on each drive.)
Give file name, contents of that file and command.
\vfill\eject
\ques
(8 points)
You have used ftp to get a new version of the X window system.
The file is called {\ltt{}xf86_4_0.tgz}.
How would you install this new software. (Just install, do not configure.)
\vskip 0.8in
Your new keyboard has a little key with a flag on it. You want to be
able to use that key in the editor to jump to the lower right of the
screen. What file would you need to modify?
\vskip 0.4in
Control-z is too similar to Shift-z so you want to change the command
that suspends a process ({\ltt{}susp}) to control-p.
What command do you issue to do this?
\vskip 0.4in
\ques
(8 points)
What is the purpose of the arp table?
\vskip 0.5in
You want your DNS server to be ({\ltt{}192.168.4.15}), and you want to
beable to leave of the {\ltt{}.mycom.com} and {\ltt{}.its.mycom.com}
suffixes when you do network operations.
Give the exact contents of the {\ltt{}resolv.conf} file that will do this.
\vskip 1.2in
\ques
(10 points)
(Netmask for this question is {\ltt{}255.255.255.192}) 
\hfill
\break
You need to change the IP number on your machine from
IP number {\ltt{}134.139.136.110},
to IP number {\ltt{}134.139.136.111}.
Give the exact command you can use to do this with out rebooting.
\vskip 0.5in
Give the exact command you can use to set it's gateway to  
{\ltt{}134.139.136.65}.
\vskip 0.5in
You set up a new machine and you want to
remove ftp services (completely).
What do you change and in what file?
\vskip 0.5in
On subnet {\ltt{}134.139.43.0/255.255.255.0} (ECS 414),
you want to set up a machine so that you can telnet
to it from other machines on the same subnet,
but from no where else.
What two files do you change and what do you put in each file?
\bye
