\input header.tex
\parindent=0in
\nopagenumbers
\newcount\quesno
\quesno=1
\def\ques{\number\quesno) \advance\quesno by 1}
\def\aspace{\vskip 1.5in}
\headline{{\rm CECS 476, Spring 1998, Midterm, Dennis Volper\hfill \ifnum\pageno=1
Name:\infoline{2.5in}\else Page \number\pageno\fi}}

Open Book, open notebook.

\ques
(7 points)
You are dealing with a program which has a configuration file
called {\ltt{}smb.conf}.
Unfortunately you don't yet have the documentation on-line so you
don't know where to look for this file.
Which directory would you check first.
\vskip 0.7in
\ques
(8 points)
You are the system administrator for {\ltt{}heart}.
Students are at your door saying that their friends are getting
the message ``file system full".
Obviously one of the 10 partitions containing the student home directories
is full, because yet another student has goofed up their 175 homework and
put an infinite loop in a program that creates a disk file (attempting
to create an infinite file).
You just have to find the file and remove it.
You are already logged in as root. 
What commands do you issue to locate the problem.
\vskip 2in
\ques
(8 points)
Your machine has new hard drive. 
You are to use a partion on this drive for the user home directories
({\ltt{}/homes2}).
Assuming the drive has already been partitioned, give the
commands that you would use to set up {\ltt{}/dev/hdb1} as {\ltt{}/homes2}.
\vskip 2.8in
\ques
(8 points)
On this new hard drive, you are also to set up {\ltt{}/dev/hdb2} as
a swap partition.
Give the commands to do this.
\vfill\eject
\ques
(7 points)
When a student tries to reboot using the control-alt-del, you
want to print the message ``Sorry, not allowed".
Describe what file needs to be changed and give the change.
\vskip 1.5in
\ques
(8 points)
You want to increase security by allowing root to login directly
only on the alt-F6 console (and nothing else).
Describe what file needs to be changed and give new contents of that file.
\vskip 2.0in
\ques
(8 points)
Describe the steps that occur when a user is added. 
(Describe means in English words, don't give the commands.)
\vskip 3.5in
\ques
(8 points)
You've just downloaded the source for your new Linux 2.0.34 kernel
into {\ltt{}/root/src.tgz}.
Oops, its' a tar archive and needs to be unarchived into
{\ltt{}/usr/src}.
How do you do this? (Give the commands.)
\vfill\eject
\ques
(8 points)
You want to allow your users to print to the laser printer in 411
which is attached to {\ltt{}psvr411.cecs.csulb.edu} and is
called by that machine {\ltt{}lp0}.
What file do you modify and what do you add to that file?
\vskip 1.5in
\ques
(7 points)
You want to know about the video setup on your machine.
What commands do you run?
\vskip 1.5in
\ques
(8 points)
Describe what the {\ltt{}SUID} bit does.
\vskip 2.0in
\ques
(7 points)
You want to build a new kernel. You've just (in a previous question)
installed the source in {\ltt{}/usr/src/linux}.
You will need to run three commands, what are those three commands?
\vfill\eject
\ques
(8 points)
You've just installed an new version of Linux, including the kernel
({\ltt{}vmlinuz}), and everything else from {\ltt{}/} down on 
{\ltt{}/dev/hdc1}. (That means you will want {\ltt{}hdc1} to be your root 
directory when you boot this new version.)
Your old version of linux is still on {\ltt{}/dev/hda1} (unchanged).
You want to be able to test the new system. 
You will want Linux to pause 5 seconds at the {\ltt{}Boot:} prompt
to let you select {\ltt{}linux} (old verion) or {\ltt{}linnew} (new version).
Give the exact contents of your {\ltt{}lilo.conf}.

\bye
