\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Homework 14 \hfill Fall 2006}}
\footline{Dennis Volper \hfill 16 October 2006 (Week 8 Lecture 1)\hfill 
Due: 18 October 2006 (Week 8 Lab 2)}
\parindent 0pt

This project is about NFS (Network File System).

1) What does jaguar export and to what machines.
For this question, give a description of the machines to which
jaguar exports.

2) cheetah mounts a directory from another machine.
Give the fstab entry for this mount.

3) The machine you administer mounts two directories from cheetah.
Give the fstab entries on your machine that causes these mounts.

4) Cheetah is running the automounter.
Look at cheetah. 
Report: what NFS directories does cheetah actually have mounted 
(use {\ltt{}df}).
(Note as our discussion of the automounter pointed out, the answer will
depending on which of these directories has been accessed recently.
The automounter is started by the {\ltt{}rc.local} script;
examine that script.
Report: exactly how is the automounter called and
what do the parameters in this call mean.
Examine the automount configuration.
Report: what machines that cheetah is willing to automount NFS volumes from?
(Its a long list, you can give a brief descriptive summary.)
If your machine is in the list report the exact contents of the
line that pertains to your machine, and a sentence saying what that
line means.
(If your machine is not in the list, inform the instructor so he can put it
there.)

5) Configure your machine so that it attaches the directory
{\ltt{}/hdb/disk1/slackware} from jaguar on your local directory tree
as {\ltt{}/mnt}.
Jaguar is already configured to make this directory available to your
machine, you do not need to modify jaguar.
Your {\ltt{}/mnt} directory should already exist.

Report: In the mount you see a bunch of directories with one letter names,
report those letters.

{\bf Report:} the file you changed on your local machine and give the line
you added to it.

6) Configure your machine so that it makes the directory
{\ltt{}/etc} available to cheetah.
Cheetah will access this directory as {\ltt{}/net/lab/labxx} where {\ltt{}labxx}
is the name the machine you are assigned to administer.
Cheetah is already configured to mount your {\ltt{}etc} directory,
you do not need to make any modifications to cheetah.
Because your {\ltt{}exports} was empty when you last booted;
you will also need to start {\ltt{}rpc.nfsd} and {\ltt{}rpc.mountd}.

Testing: Log into cheetah and run {\ltt{}ls /net/lab/labxx}.
Because cheetah is running the automounter
this {\ltt{}ls} will cause your directory to be mounted.
Now run {\ltt{}df}.

{\bf Report:} the files you changed on your local machine and give the lines 
you added to them.
Also report the part of the disk free report from cheetah that applies to 
the {\ltt{}/etc} from your machine.

Yes, this is due, in lab, after the midterm.
\bye
