\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Homework 18 \hfill Fall 2005}}
\footline{Dennis Volper \hfill 2 November 2005 (Week 10 Lecture 2)\hfill 
Due: 7 November 2005 (Week 11, Lab 1)}
\parindent 0pt

This project is about ftp.

1) Log into jaguar.
Ftp to your local machine.
Use the username anonymous.
Get the dummy test file.
(If you don't have a dummy test file under {\ltt{}~ftp}, make one up.)

Report: On login. What does it say when you login.

2) On you local machine, check your {\ltt{}ftpusers}
and {\ltt{}proftpd.conf} files to make sure that
both network (NIS/yp) accounts and anonymous ftp
are allowed.
Also, modify the anonymous account so it
will put up a greeting message when at the start of
an anonmyous ftp.

Test: go back to jaguar, ftp to anonymous on your machine
and make sure it all works.

Note: we did not add any files to your ftp area, so when
you test, there will be nothing there to get; just make sure
you get to login and see the message.

Report: what changes did you make (give file names).

3) Go back to jaguar.
Ftp to your local machine.
Use the username bob.
Get the {\ltt{}demo} file.
(If you didn't remember to make a demo file when you created
bob, login as bob and create a text file called demo.)

4) Change the settings on ftp so that {\ltt{}bob} may not use ftp.
All other ftp capabilities should still be allowed.

Note: several other users are usually not allowed to use ftp, including {\ltt{}root}, {\ltt{}uucp}
{\ltt{}news}; do not change these permissions.

Test: make sure that {\ltt{}bob} cannot use ftp into your machine and your
account can.

Report: Exactly what change you made and to what
file/directory you made that change.

5) Dynamically and statically loaded libraryies.
Compare the {\ltt{}clogitA} and {\ltt{}clogitB} commands found in {\ltt{}~djv}.
Examine the size of the two commands
and use {\ltt{}ldd} to look at the dynamically loaded libraries.

Report: the difference between the two commands (sizes and dynamic libraries).
\bye
