\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Homework 8 \hfill Fall 2005}}
\footline{Dennis Volper \hfill 26 September 2005 (Week 5 Lecture 1)\hfill 
Due: 28 September 2005 (Week 5 Lab 2)}
\parindent 0pt

This assignment covers the X Window system.

On your machine examine the x configuration file found in {\ltt{}/etc/X11}.
\hfill\break
1) How many different mouse protocols available?
List two of the protocols that apply to Mouseman products.
\hfill\break
2) What device does your config specify for the mouse?

Examine the device file system:
\hfill\break
3) what device does {\ltt{}/dev/mouse} link to?

On your system probe your X11 setup (use a command, don't use
the files).
Report:
\hfill\break
4) The exact command you ran.
\hfill\break
5) The version of the X11 system on your machine and its release date.
\hfill\break
6) The ``Vendor" of your video card.
\hfill\break
7) The "Total memory:" that was found on your card.
\hfill\break
8) What ``product" of that vendor was your card.
\hfill\break
9) How many video modes were searched for a match.

Re-do your X11 configuration file.
You know your video card (from above).
Assume your monitor can do a standard SVGA (800x600), 30-69K horizontal,
47-90 vertical.
You need to get at least 2 working resolutions,
you should be able to get 3.

Try starting X and stepping through some modes. Pick your
highest resolution and use {\ltt{}xvidtune} on it.

\hfill\break
10) Report the eleven numbers from the tuning program.
Warning, if your setup is not fully correct,
this program gets a floating-point error.

\bye
