\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Homework 1 \hfill Fall 2004}}
\footline{Dennis Volper \hfill 30 August 2004 (Week 1 Lecture 1)\hfill 
Due: 1 September 2004 (Week 1 Lab 2)}
%first day assignment, unless monday is a holiday
\parindent 0pt

Purpose:
To familiarize you with the systems you will be using.

Submission: You will submit a printout.
This document and all submissions in this course will have a header
containing the following information:

Your name, your account number, and the name of the machine on which you
did the homework.

Manual usage:

How many users are listed in the password file of cheetah?
(Fortunately there is one user per line.)
Hint: use {\ltt{}man -k} to find a command that prints the number
of lines in a file.

1) Report: the number of entries in the password file and
the command you used to find out.

File system organization:

Examine: the configuration file that controls the {\ltt{}inetd} system service
on your Linux system.

2) Report: What is the name exact name of this file
and in what directory did you find this file.

Locate: the program that will tell the disk space usage
on your Linux system.

3) Report: What is the name name of that program 
and in what directory (where) is the program found.

Report the answer to each of the following questions

4) In what directory do you find the {\ltt{}shutdown} command?

5) Your {\ltt{}/etc/X11} directory should contain templates for
the configuration file for the {\ltt{}X} window system.
What are the name of these files?
(Hint: the file names start with XF86.)

6) In the {\ltt{}/dev} directory, what is full name of the entry that starts
with {\it sony}? (Hint, use ls with a wild card).

Examine the {\ltt{}/proc} file system.
Your machine is probably running 10--20 processes.
\hfill\break
7) Use the {\ltt{}ls} command, and give the numbers of the last 6
of those processes listed. (This will vary with time.)

Examine the log files on {\ltt{}jaguar}:
\hfill\break
8) Give the names of the last 3 log files that have changed and 
the dates at which they changed
\hfill\break
9) Give the last 3 lines found in the {\ltt{}messages} log file.

10) Log into {\ltt{}cheetah} and run the {\ltt{}register} program
(so I know who is using
which acocunt). Use your student ID number, the one that matches
the number that I will find on my enrollment sheet.
(No submission on this one.)

\bye
