\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Homework 18 \hfill Spring 2004}}
\footline{Dennis Volper \hfill 12 April 2004 (Week 11 Lecture 1)\hfill 
Due: 14 April 2004 (Week 11, Lab 2)}
% usually 10-2 but we had 2 MW holidays this semester
\parindent 0pt

This project is about ftp.

1) On you local machine, check your {\ltt{}ftpusers}
and {\ltt{}proftp.conf} files to make sure that
both network (NIS/yp) accounts and anonymous ftp
are allowed.

Report: what changes (if any) did you have to make to these
files.

2) Log into jaguar.
Ftp to your local machine.
Use the username anonymous.
Get the dummy test file.

Report: On login. What does it say when you login.

3) Go back to jaguar.
Ftp to your local machine.
Use the username bob.
Get the {\ltt{}demo} file.
(If you didn't remember to make a demo file when you created
bob, login as bob and create a text file called demo.)

4) Compare the {\ltt{}ls} command that everyone else uses with the
one for anonymous ftp.
Examine the size of the two ls command
and use {\ltt{}ldd} to look at the dynamically loaded libraries.

Report: the difference between the two commands (sizes and dynamic libraries).

5) The current setup of ftp is a little less secure than it
could be.
Some change would make it more secure.
Make at least one such change.
Then check your changes by logging log into jaguar a second time
and use anonymous ftp to get the dummy test file again.

Report: Exactly what change you made and to what
file/directory you made that change.
If you changed ownership or protection, report the new owner or mode.
\bye
