\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Homework 6 \hfill Spring 2004}}
\footline{Dennis Volper \hfill 11 February 2004 (Week 3 Lecture 2)\hfill 
Due: 18 February 2004 (Week 4 Lab 2)}
\parindent 0pt

This part of the assignment is designed to familiarize you with the
commands involving Unix processes.

Submission: You will submit a written document.

For Cheetah: 1) how long has it been since it has
been rebooted, 2) how many users are logged in, 3) how busy is the machine
(short, medium and long term load).

For Cheetah: 4) What percentage of the cpu is the operating system
spending in each of user mode, system mode and idle?
5) How much memory is in use and
how much is idle?
6) What 3 processes have consumed the most total CPU since
they were started?

For the machine you administer answer the following:
7) How many processes called {\ltt{}agetty} are running?
8) There are several commands running that include the letters {\ltt{}rpc},
list all those commands.
9) What is the resident set size and total (virtual memory or VM) size of the
lpd process.

%One of the users on your system has created a run-away process.
%Use your system administrator privilege to
%get rid of the process the process.
%(-10 points if you reboot the machine)
%
%Submit: 9) The exact commands you used to examine the processes;
%who owned the process, what was it called and what was its
%process id number;
%and the exact command you used to get rid of the run-away process.
%
%Note: If your machine was rebooted recently, it will have wiped
%out the run-away process, and you will have to let me know so
%I can start one.

This part of the assignment is designed to familiarize you with the
commands involving virtual memory and swapping.

10) As it is set up,
does your machine use a swap partition or a swap file? 
Report which it is.
Report the full name of the swap partition or file.

11) Report the following in kilobytes:

a) the amount of memory available (minus the kernel),
\break
b) the amount of memory in use,
\break
c) the amount of memory used for buffers,
\break
d) the amount of swap space available,
\break
e) the amount of swap space in use,

(Any dumps of command output will be given a zero.)

On the lab machine you are assigned to administer:

Set up a 4 MB swap file, call it {\ltt{}/swapfile}.
Turn on swapping for that file.

12) Report the exact commands you used to do this.

13) Report the amount of swap space available and the amount in use.

Turn off swapping and remove your file.

Note for subsequent questions:
If you did the {\ltt{}fdisk} as directed in the previous home work,
the swap partion you created should be {\ltt{}/dev/hdc1}; this is your
``second" swap partition.
The swap partition I created is {\ltt{}/dev/hda2} and is already in use.

First, set up the swap structure in your second swap partition.
Second, modify your {\ltt{}fstab} so that swapping in that partition
is turned on automatically at boot.
(Use the {\ltt{}swapon -a} command to make sure you've got everything
setup correctly, else the next step will lock up!!!)
Now that you've tested to make sure things work, reboot
(This is to make sure the ``automatically at boot" is working.)
This new swap partition is permanent, do not remove it.

14) Report the amount of swap space available and the amount in use.
(This should be different from your previous report of swap space, by
approximately the size of your new swap partition!)

\bye
