\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Homework 8 \hfill Fall 2004}}
\footline{Dennis Volper \hfill 26 September 2004 (Week 5 Lecture 1)\hfill 
Due: 28 September 2004 (Week 5 Lab 2)}
\parindent 0pt

This assignment covers the X Window system.

On your machine examine the x configuration file found in {\ltt{}/etc/X11}.
\hfill\break
1) What are the different mouse protocols available?
\hfill\break
2) What device does your config specify for the mouse?

Examine the device file system:
\hfill\break
3) what device does {\ltt{}/dev/mouse} link to?

On your system probe your X11 setup (use a command, don't use
the files).
Report:
\hfill\break
4) The exact command you ran.
\hfill\break
5) The version of the X11 system on your machine and its release date.
\hfill\break
6) The ``Vendor" of your video card.
\hfill\break
7) The "Total memory:" that was found on your card.
\hfill\break
8) What ``product" of that vendor was your card.
\hfill\break
9) How many video modes were searched for a match.

Re-do your X11 configuration file.
You know your video card (from above).
Assume your monitor can do a standard SVGA (800x600), 30-50K horizontal,
40-90 vertical.
See if you can get at least two working resolutions.

Try starting X and stepping through some modes. Pick your
best mode and try using {\ltt{}xvidtune} on it.

\hfill\break
10) Report the eleven numbers from the tuning program.
Warning, if your setup is not fully correct,
this program gets a floating-point error.

\bye
