\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476 \hfill Homework 15 \hfill Fall 2004}}
\footline{Dennis Volper \hfill 25 October 2004 (Week 9 Lecture 1)\hfill 
Due: 27 October 2004 (Week 9 Lab 2)}
\parindent 0pt

{\bf Syslog--}

Set up your machine so that it logs {\it  all} mail activity 
on your machine to a file
called {\ltt{}/var/log/maillog}.
Send from your machine and make sure the log records this.

1) Report: the line you put into the syslog.conf that did this.

Set up your machine so that it logs {\it all mail} activity 
on your machine to 
{\ltt{}jaguar.net.cecs.csulb.edu}.
(Please don't swamp jaguar by logging everything.)

Send mail from your machine and make sure the log records this works.
Note: On {\ltt{}jaguar}, you will need to examine the {\ltt{}syslog.conf}
to see what file that {\ltt{}jaguar} puts this log information into.
The name of the log file on jaguar is deliberately slightly different from
the name of the logfile I've asked you to use on your machine.

2) Report: the line you put into the syslog.conf that did this.

Clean up: Remove the {\ltt{}jaguar} entry from your {\ltt{}syslog.conf}.


{\bf Printers---}

{\bf printcap:}
Add a line to your printcap so that your machine can
print to the printer on jaguar.
This printer attached to {\ltt{}jaguar.net.cecs.csulb.edu} is
as {\ltt{}jaguar} and as {\ltt{}lp}.
Make the printer on {\ltt{}jaguar} the default printer for the system 
({\ltt{}lp}).

3) Report: the line that you added to the printcap. 
Do not submit the entire printcap.

\bye
