\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Homework 18 \hfill Fall 2004}}
\footline{Dennis Volper \hfill 3 November 2004 (Week 10 Lecture 2)\hfill 
Due: 8 November 2004 (Week 11, Lab 1)}
% usually 10-2 but we had 2 MW holidays this semester
\parindent 0pt

This project is about ftp.

1) On you local machine, check your {\ltt{}ftpusers}
and {\ltt{}proftpd.conf} files to make sure that
both network (NIS/yp) accounts and anonymous ftp
are allowed.

Report: what changes (if any) did you have to make to these
files.

2) Log into jaguar.
Ftp to your local machine.
Use the username anonymous.
Get the dummy test file.

Report: On login. What does it say when you login.

3) Go back to jaguar.
Ftp to your local machine.
Use the username bob.
Get the {\ltt{}demo} file.
(If you didn't remember to make a demo file when you created
bob, login as bob and create a text file called demo.)

4) Compare the {\ltt{}clogitA} and {\ltt{}clogitB} commands found in
{\ltt{}~djv}.
Examine the size of the two commands
and use {\ltt{}ldd} to look at the dynamically loaded libraries.

Report: the difference between the two commands (sizes and dynamic libraries).

5) Change the settings on ftp so that {\ltt{}bob} may not use ftp.
All other ftp capabilities should still be allowed.

Note: several other users are usually not allowed to use ftp, including {\ltt{}root}, {\ltt{}uucp}
{\ltt{}news}; do not change these permissions.

Test: make sure that {\ltt{}bob} cannot use ftp into your machine and your
account can.

Report: Exactly what change you made and to what
file/directory you made that change.
\bye
