\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Homework 1 \hfill Spring 2006}}
\footline{Dennis Volper \hfill 25 January 2006 (Week 1 Lecture 2)\hfill 
Due: 30 January 2006 (Week 2 Lab 1)}
%first day assignment, unless monday is a holiday
\parindent 0pt

Purpose:
To familiarize you with the systems you will be using.

Submission: You will submit a printout.
This document and all submissions in this course will have a header
containing the following information:

Your name, your login name, and the name of the machine on which you
did the homework.

All the questions will also serve to drill you on the organization
of the Linux file system.
The first three questions are also a drill on using the online manual.

How many users are listed in the password file of cheetah?
(Fortunately there is one user per line.)
Hint: use {\ltt{}man -k} to find a command that prints the number
of lines in a file.

1) Report: the number of entries in the password file and
the command you used to find out.

File system organization:

Examine: the configuration file that controls the {\ltt{}inetd} system service
on your Linux system.

2) Report: 
What is the name exact name of this file,
in what directory did you find this file,
and what commands did you use to do this.

Locate: the program that will tell the disk space usage
on your Linux system.

3) Report: What is the name name of that program,
in what directory (where) is the program found
and what commands did you use to do this.

The next 5 questions are designed to make you use various
commands with specific options.
The answers themselves are of minor interest, the drill here is
on use of various Unix commands.
These commands will be frequently used by you in later assignments.

Report the answer to each of the following questions and the
commands you used to find that answer.

4) Your {\ltt{}/etc/X11} directory should contain templates for
the configuration file for the {\ltt{}X} window system,
what are the name of these files?
(Hint: the file names start with xorg.)

5) In the {\ltt{}/dev} directory, there is an the entry that starts
with {\it sony}. What is the full name of that entry.
(Hint, use ls with a wild card).

6) Examine the {\ltt{}/proc} file system.
What is the cpu MHz of your machine.
Hint: this is information about the cpu and can be obtained using the
cat command on the correct pseudo-file.

Examine the log files on {\ltt{}jaguar}:
\hfill\break
7) Give the names of the last 3 log files that have changed and 
the dates at which they changed.
\hfill\break
8) Give the last 3 lines found in the {\ltt{}messages} log file.

This following is not really a question, it is an action that
willl attach your name and account to my gradesheet.

9) Log into {\ltt{}cheetah} and run the {\ltt{}register} program,
follow the intructions that program gives you.
(No submission on this one.)

\bye
