\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Homework 8 \hfill Fall 2007}}
\footline{Dennis Volper \hfill 1 October 2007 (Week 5 Lecture 1)\hfill 
Due: 3 October 2007 (Week 5 Lab 2)}
\parindent 0pt

This assignment covers the X Window system.

Examine the manual entry for the configuration file ({\ltt{}xorg.conf}.
\hfill\break
1) What configuration option diables the action of the control-alt-backspace
combination.

On your machine examine the x configuration file found in {\ltt{}/etc/X11}.
The manual entry for {\ltt{}xorg.conf} will also be helpful.
\hfill\break
2) How many different mouse protocol optionss available?
\hfill\break
3) What is the protocol option currently specified for the mouse?

Examine the device file system:
\hfill\break
4) what device does {\ltt{}/dev/mouse} link to?

On your system probe your X11 setup (use a command, don't use
the files).
Report:
\hfill\break
5) The exact command you ran.
\hfill\break
6) The version of the X11 system on your machine and its release date.
\hfill\break
7) The ``Vendor" of your video card.
\hfill\break
8) What ``Product" of that vendor was your card.
\hfill\break
9) The "Total Mem:" (video memory) is being used.
\hfill\break
10) How many video modes ({\ltt{}Mode:}) were searched.
Hint: searching (grep) and line counting may be really helpful here.

Re-do your X11 configuration file.
You know your video card (from above).
Assume your monitor can do 1024x768, 30-69K horizontal,
40-90 vertical.
You need to get at least 2 working resolutions,
you should be able to get 3.
Your mouse uses the  PS/2 protocol.
If this protocol doesn't work, we may have a couple mice in the
room that use the Mouseman plus PS/2 protocol
(I haven't checked all the mice).
Use 24 bits as the default color depth.

Start X and step all your video modes. For each of your your
resolutions use {\ltt{}xvidtune} to show the information about that
resolution.

\hfill\break
11) Report what resolutions you have available.

\bye
