\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Assignment 9 \hfill Spring 2014}}
\footline{Nathan Pickrell \hfill 18 February 2014 (Week 5 Lecture 1)\hfill 
Due: 20 February 2014 (Week 5 Lab 2)}
\parindent 0pt

This assignment covers the X Window system.

Examine the manual entry for the configuration file ({\ltt{}xorg.conf}).
\hfill\break
1) What configuration option diables the action of the control-alt-backspace
combination.

In {\ltt{}/etc/X11}:

Examine the {\ltt{}xorg.conf-vesa}  configuration file.
The manual entry for {\ltt{}xorg.conf} will also be helpful.
\hfill\break
2a) How many different mouse protocol options available?
\hfill\break
2b) If this file were to be used, what protocol option would be used for the
mouse?

Examine the initializations for {\ltt{}xinit}.
\hfill\break
2c) How is the default window manager set (use {\ltt{}ls})?
\hfill\break
Verify this by starting X as {\ltt{}bob}.

In the log directory:

Examine the {\ltt{}Xorg.0.log} file 
(It was created when you started X in question 2.)
\hfill\break
3a) What mouse input device was found?
\hfill\break
3b) What is the best Modeline supported by the video chipset (DCC)?
\hfill\break
3c) What is the best Modeline supported by the monitor (VGA1)?


Examine the device file system (use {\ltt{}ls}):

4) What device does {\ltt{}/dev/mouse} link to?

In the {\ltt{}djv} account:

Examine the {\ltt{}.xinitrc}:
\hfill\break
5a) What window manager is used by this account?
\hfill\break
5b) How many windows are display when this account starts X?

Examine the {\ltt{}.twmrc}:
\hfill\break
A button has been set up that raises a window (to be on
top of the other windows).
\hfill\break
5c) Report the button and the line that does it?

On your system as administrator:

Modify the default {\ltt{}fvwm} settings to automatically
start two 80x24 xterm windows in the upper left and lower right
of the screen. Also modify the settings so the background is
solid yellow.
\hfill\break
6a) Report the name of the file and the modifications you made
to that file?

Modify the default window manager to be {\ltt{}twm}.
\hfill\break
Verify this works by starting X as {\ltt{}bob}.
\hfill\break
6b) How did you do this?
\hfill\break
Modify the default back to {\ltt{}fvwm}.
\hfill\break
Verify you did this this by again starting X as {\ltt{}bob}.

On your system (the user login doesn't matter):

Run the {\ltt{}xvidtune} program.
\hfill\break
7a) What are the horizontal and vertical display resolutions?
({\ltt{}HDisplay}, {\ltt{}VDisplay})
\hfill\break
7b) What is the vertical synchonization rate?


On your system as {\ltt{}sue}:

Modify sue's account so it
(a) uses {\ltt{}twm} as the window manager instead of the default manager
(b) automatically starts an xterm in the upper left
and
(c) sets the background to solid red.
\hfill\break
Verify by starting X as {\ltt{}sue}.
\hfill\break
8) Report the name of the file you created and the contents of
that file.

\bye
