\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476 \hfill Assignment 15 \hfill Spring 2010}}
\footline{Dennis Volper \hfill 16 March 2010 (Week 8 Lecture 1)\hfill 
Due: 18 March 2010 (Week 8 Lab 2)}
\parindent 0pt

{\bf Syslog--}

Set up your machine so that it logs {\it  all} mail activity 
on your machine to a file called {\ltt{}/var/log/mymaillog}.
Note: this is a change in the name of the log file.
Send mail from your machine and make sure the new log file records this.

1) Report: the line you put into the syslog.conf that did this.

Set up your machine so that it logs {\it all mail} activity 
on your machine to 
{\ltt{}jaguar.net.cecs.csulb.edu}.
(Please don't swamp jaguar by logging everything.)

Send mail from your machine and make sure the log records this works.
Note: On {\ltt{}jaguar}, you will need to examine the {\ltt{}syslog.conf}
to see what file that {\ltt{}jaguar} puts this log information into.
The name of the log file on jaguar is slightly different from
the name of the logfile I've asked you to use on your machine.

2) Report: the line you put into the syslog.conf that did this.

Clean up: Remove the {\ltt{}jaguar} entry from your {\ltt{}syslog.conf}.

{\bf Printers---}

Install the printer system. The compressed tar archive file can
be found as {\ltt{}~djv/lpr.tgz}.
To install (a) {\ltt{}cd /}, (b) extract the contents of the tar archive,
(c) run the install script ({\ltt{}source install/doinst.sh})

%Remove everything from your print spool ({\ltt{}lprm}).
%Use {\ltt{}lpq} to make sure it's empty.

Your machine uses the lpd print server.
Add a line to your printcap so that your machine can
print to the printer on jaguar.
This printer attached to {\ltt{}jaguar.net.cecs.csulb.edu} is
as {\ltt{}jaguar} and as {\ltt{}lp}.
Make the printer on {\ltt{}jaguar} the default printer for the system 
({\ltt{}lp}).
Make sure you can print

3) Report: the line that you added to the printcap. 
Do not submit the entire printcap.

%Your machine uses the cups print server.
%Use the configuration commands to enable printing on your machine.
%Your machine should, as a default printer, print to the printer
%named {\ltt{}jaguar} on the machine named 
%{\ltt{}jaguar.net.cecs.csulb.edu}.
%(Make sure you can print.)
%4) Report: Describe what each of the fields in the panther's
%printcap entry mean.


\bye
