\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Project 25 \hfill Srping 2002}}
\footline{Dennis Volper \hfill 6 May 2002 (Week 14 Lecture 1)\hfill 
Due: 8 May 2002 (Week 14, Lab 2)}
\parindent 0pt

This project is about SAMBA.

1) Create a directory {\ltt{}/home/share} on your machine and
create a couple text files in it. Call them {\ltt{}sam.txt} and 
{\ltt{}joe.txt}.

2) Modify the samba configuration file so that your security is by
share and you share the {\ltt{}/home/share} directory as public
read only. Call this share {\ltt{}[myshare]}. (Yes, you'll need
to do a few other housekeeping items.)

3) Set up the rc files ({\ltt{}rc.samba}) to enable the samba services.
(Check the first inet assignment if you don't know how to do this.
You did the disable if you followed the instructions during the install
project.) Reboot. (Check to make sure the two samba daemons are running.)

4) Test your configuration: Go to the NT machine in the lab.
Login as guest (it should be logged in already). Click on network 
neighborhood. If your machine shows up and when you click on
your machine's icon the share should appear, if your
machine doesn't show up, use the ``find computer" option on the pull-down
and find {\ltt{}lab}{\it{}xx} where {\it xx} is the number of your machine.
(The NT machine is configure so it doesn't need the {\ltt{}net.cecs.csulb.edu}
suffix.

Submit: a copy of your smb.conf with the comments removed.

Demonstration: When you hand your submission to me, you must use the NT machine
to demonstrate that your share works.
\bye
