\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Project 8 \hfill Spring 2002}}
\footline{Dennis Volper \hfill 20 February 2002 (Week 4 Lecture 2)\hfill 
Due: 25 February 2002 (Week 5, Lab 1)}
\parindent 0pt

This assignment covers the X Window system.

On your machine examine the x configuration file.
Report 1) the number of modelines you found.
Report 2) What device are you using for the mouse.
Examine that device (this means examine {\ltt{}/dev}) 
and report 3) exactly what is that device is
(A look at the manual entry for mouse will help here.)

Check the configuration of your X system (using a command, not using
the files).
Report 4) the number of valid modes that the command found
and what clock rates (mode clock) is used for each of them,
5) the exact command you ran to find that out,
6) the version of the X11 system on your machine and its release date.
When you run this check the command reports something things are 
deleted (i.e., discarded) from the configuration file,
what were those things.

Check your video hardware.
Report: 7) what type of videocard is in the machine (include the
number) and
8) how much memory is on that card,
9) the exact command you ran to find that out.

Re-do your X11 configuration file.
You know your video card (from above).
Assume your monitor can do a standard SVGA (800x600), 30-50K horizontal,
40-90 vertical.

Try starting X and stepping through some modes. Pick your
best mode and tune it.

Report: 10) the exact numbers from the tuning program.

Note: If you have trouble with the name of your videocard, you may need
to "reboot" and see what the video BIOS displays.
\bye
