\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Project 19 \hfill Spring 2002}}
\footline{Dennis Volper \hfill  15 April 2002 (Week 11 Lecture 1)\hfill 
Due: 17 April 2002 (Week 11, Lab 2)}
\parindent 0pt

This project is about configuring mail.

1) Send mail from your lab machine to your csv account on {\ltt{}cheetah}
using the verbose options ({\ltt{}-v}.
You will notice the conversation between the two machines.

Report: the lines of that conversation.

2) On your lab machine send mail from your csv account to bob (on the
local machine) using the verbose option.

Report: the lines of that mail delivery.

You will notice a substantial difference between the lines reported
when the mail goes to another machine and when it is local.

3) Suppose you wanted all mail from your lab machine to be delivered 
to cheetah.
What changes would you make to {\ltt{}sendmail.cf} to accomplish this?
Make the change, then send mail from bob to your (csv) account
using the verbose option.
The conversation should be similar to that in (1).

Report: the change you made to {\ltt{}sendmail.cf}

3) Suppose you wish mail coming from your machine to appear as though it
came from cheetah.
You can do this by making a change to the {\ltt{}DM} macro.
Somewhere this change causes a change to be made in the return address.

Report: The ruleset that the rewrite of the address is in (S what).
The rule in that ruleset causes the rewrite (report the entire line).

Don't forget to restore the config to its original contents.
\bye
