\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Project 3 \hfill Spring 2002}}
\footline{Dennis Volper \hfill 4 February 2002 (Week 2 Lecture 1)\hfill 
Due: 6 February 2002 (Week 2, Lab 2)}
\parindent 0pt

Purpose: This assignment is to familiarize you with setting up users and logins.

System Admin: When you submit assignment 2, you should ask for (and get)
a system administrators account.
You will be assigned to a certain machine and will be given an
"administrator number" 1--2.
This number will correspond to which part of the homework you must do.
Do just the part corresponding to your number.
If you intend to work with a partner, submit assignment 2 at the
same time and ask that your administrator accounts be on the same
machine.
But you should (on this assignment) each do your project separately
and submit separate written documents.

Submission: You will submit a written document.
Put you name, account, machine and system administrators number on your 
document.
The document will contain the exact version of each command you did.
If you did an edit, tell me exactly what change you made to the file. 
You will leave the user login setup on your computer.

On the lab machine, you are assigned to administer set up {\it one}
and only one, of the following users.
Do not use a script, do all the steps individually, by hand.

{\bf Administrator 1}:

Name {\ltt{}bob}
\break
Password: access31
\break
UID: {\ltt{}13101}
\break
Default group: {\ltt{}cecsu}
\break
Home directory: {\ltt{}/home/bob}

{\bf Administrator 2}:

Name {\ltt{}sue}
\break
Password: access32
\break
UID: {\ltt{}13102}
\break
Default group: {\ltt{}cecsg}
\break
Home directory: {\ltt{}/home/sue}

For {\it all} administrators:

Shell: {\ltt{}/bin/csh}
\break
Home directory contents, 3 files:
{\ltt{}.cshrc}, {\ltt{}.login} and {\ltt{}demo}.
\break
The {\ltt{}.cshrc} and {\ltt{}.login} files should be identical to those in
the home directory of the {\ltt{}djv} account.
You should create the {\ltt{}demo} file using an editor
and it should contain one line of text saying,
``Hi there, welcome to CECS".
The file ownership and group access of all files and directories
should be correctly set.
\bye
