\input macros
\rightskip=0pt plus 1fill
\input cstuff
\headline{{\bf CECS 476\hfill Homework 1 \hfill Spring 2005}}
\footline{Dennis Volper \hfill 24 January 2005 (Week 1 Lecture 1)\hfill 
Due: 26 January 2005 (Week 1 Lab 2)}
%first day assignment, unless monday is a holiday
\parindent 0pt

Purpose:
To familiarize you with the systems you will be using.

Submission: You will submit a printout.
This document and all submissions in this course will have a header
containing the following information:

Your name, your login name, and the name of the machine on which you
did the homework.

Manual usage:

How many users are listed in the password file of cheetah?
(Fortunately there is one user per line.)
Hint: use {\ltt{}man -k} to find a command that prints the number
of lines in a file.

1) Report: the number of entries in the password file and
the command you used to find out.

File system organization:

Examine: the configuration file that controls the {\ltt{}inetd} system service
on your Linux system.

2) Report: What is the name exact name of this file
and in what directory did you find this file.

Locate: the program that will tell the disk space usage
on your Linux system.

3) Report: What is the name name of that program 
and in what directory (where) is the program found.

Report the answer to each of the following questions

4) Your {\ltt{}/etc/X11} directory should contain templates for
the configuration file for the {\ltt{}X} window system.
What are the name of these files?
(Hint: the file names start with XF86.)

5) In the {\ltt{}/dev} directory, what is full name of the entry that starts
with {\it sony}? (Hint, use ls with a wild card).

Examine the {\ltt{}/proc} file system.
What is the cpu MHz of your machine.
Hint: this is information about the cpu and can be obtained using the
cat command on the correct pseudo-file.
\hfill\break
6) Use the {\ltt{}ls} command, and give the numbers of the last 6
of those processes listed. (This will vary with time.)

Examine the log files on {\ltt{}jaguar}:
\hfill\break
7) Give the names of the last 3 log files that have changed and 
the dates at which they changed
\hfill\break
8) Give the last 3 lines found in the {\ltt{}messages} log file.

%10) Log into {\ltt{}cheetah} and run the {\ltt{}register} program
%(so I know who is using
%which account). Use your student ID number, the one that matches
%the number that I will find on my enrollment sheet.
%(No submission on this one.)

\bye
