\input macros
\input cstuff
\headline{{\bf CECS 472\hfill Project 7 \hfill Spring 2002}}
\footline{Dennis Volper \hfill 15 April 2002 (Week 11 Lecture 1)\hfill
Due: 24 April 2002 (Week 12 Lecture 2)}
\parindent 0pt

Purpose: To gain an in-depth understanding of
CORBA.

You will build a CORBA client and server.

Your server will provide a class with three methods (procedures).
Your client will allow the user to call any of these procedures.

Overview: You are re-writing a (client/server) program as
a CORBA network application.
You will be given the original working C++ program.

{\it The Colocated Program} 

You will build a colocated version of the CORBA program.
CORBA is installed only on jaguar and cheetah so you will need to telnet one
of these to do this assignment.

{\it The Train Service}

Implement the methods found in the C++ version of the train program
({\ltt{}train.cc}) as remote (CORBA) objects.
You will find a copy of the {\ltt{}train.cc} program in
{\ltt{}~volper/classes/472/programs/corba}.
It is a single file, but has three parts within the file
the class, the principal procedure and the main program.
Break it into three files before starting the CORBA assignment.

Submit the following files (use the names specified):
\hfill\break
{\ltt{}train_services.idl}: (the idl file), 
\hfill\break
{\ltt{}train_services_i.cc}: (see {\ltt{}echo_i.cc} and {\ltt{}vector_ops_i.cc})
\hfill\break
{\ltt{}run_train.cc}: (see the {\ltt{}hello} procedure in {\ltt{}greeting.cc}),
\hfill\break
{\ltt{}train_colocate.cc}: (the main program, see the {\ltt{}eg1.cc} 
file from the echo example).

Do not submit the files automatically generated by the idl compiler.

Help: various aliases and paths need to be set up. To do this,
you should {\ltt{}source corba.sh}. This file is found in the
same directory as {\ltt{}train.cc} (make a local copy for convenience).
Note the alias {\ltt{}gxx} has the correct (and complicated) invocation
of the g++ compiler to correctly compile the Corba version of the train.

{\it The Stringified Reference Program} 

You will also build a stringified version of the CORBA program.

You should do this right, that is, the {\ltt{}train_services_i.cc},
{\ltt{}run_train.cc} and the {\ltt{}train_services.idl} should be the 
same as before.
Submit the {\ltt{}train_clt.cc} and {\ltt{}train_impl.cc} files.

\bye
